### 2018-11-16 asc.tex
Initial commit

\documentclass[12pt]{article}

%\usepackage[utf8]{inputenc}
%\usepackage[english]{babel}

%
% COLORS
%
\usepackage[dvipsnames, table]{xcolor}{\rm }

%
% LINKS AND REFERENCES
%
\usepackage{hyperref}
\hypersetup{
	colorlinks,
	linkcolor={Red!90!black},
	citecolor={Red!90!black},
	urlcolor={Red}
}

\usepackage{geometry}

\usepackage[parfill]{parskip} % https://tex.stackexchange.com/a/16703/135296

% sub figures / grids of pictures
\usepackage{subcaption}
\usepackage{graphicx}
\graphicspath{{img/}} % includegraphics path
\newcommand{\includegraphicsw}[2][1.]{\includegraphics[width=#1\linewidth]{#2}}
\newcommand{\svginput}[1]{\input{img/#1}} % pdf_tex path
\newcommand{\svginputw}[2][\linewidth]{\def\svgwidth{#1}\input{img/#2}} % pdf_tex path
% pdf
\usepackage{pdfpages}
% tables
\usepackage{multirow}
\usepackage{hhline}
\usepackage{colortbl}
\usepackage{wrapfig}
% \coloneqq
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{amsthm} % proofs
% bold for everything
\usepackage{bm}
%\usepackage{showlabels}
% lowercase mathcal font
%\usepackage{dutchcal}

% braces for subeqns and boxes
\usepackage{empheq}
% http://mirror.hmc.edu/ctan/macros/latex/contrib/mathtools/empheq.pdf
\newcommand*\widefbox[1]{\fbox{\hspace{1em}#1\hspace{1em}}}

% math commands for convinience
\DeclareMathOperator{\argmin}{arg\,min}
\DeclareMathOperator{\Span}{span}
% bold vectors
\newcommand{\vect}[1]{\boldsymbol{\mathbf{#1}}}

\newcommand{\bcell}{T}
\newcommand{\bmesh}{{\vect{\mathcal T}}}
\newcommand{\mcell}{\tau}
\newcommand{\mmesh}{{\vect{\mathcal \tau}}}
\newcommand{\bfaces}[1][]{{\vect{\mathcal F}_{\text{#1}}}}
\newcommand{\mfaces}[1][]{{\vect{ f}_{\text{#1}}}}

\newcommand{\LTwo}{{\mathbb L^2}}
\newcommand{\lTwo}{{\ell^2}}
\newcommand{\HDiv}{{\mathbb H_\text{div}}}
\newcommand{\Rn}[1]{{\mathbb R^{#1}}}
\newcommand{\Pn}[1]{{\mathbb P^{#1}}}
\newcommand{\LTwoSpace}[1][\Omega]{{\mathbb L^2\left({#1}\right)}}
\newcommand{\lTwoSpace}[1][\Omega]{{\ell^2\left({#1}\right)}}
\newcommand{\HDivSpace}[1][\Omega]{{\mathbb H_\text{div}\left({#1}\right)}}
\newcommand{\PnSpace}[2]{{\mathbb P^{#1}\left({#2}\right)}}

\newcommand{\errlTwo}[1]{e^{\lTwo}_{#1}}
\newcommand{\errInf}[1]{e^{\infty}_{#1}}
\newcommand{\MO}[1]{{\color{blue}MO: #1}}
\newcommand{\DS}[1]{{\color{blue}DS: #1}}
\newcommand{\Sasha}[1]{\colorbox{Cyan}{\textbf{Sasha}:} #1}

% differentials
\newcommand*\diff{\mathop{}\!\mathrm{d}}
\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}

\DeclareMathOperator{\Ker}{Ker}

% listings
%\usepackage{listings}
%\lstset{
%	basicstyle=\linespread{.95}\footnotesize\ttfamily\color{black},
%	keywordstyle=\color{green!40!black},
%	emphstyle=\bfseries\color{green!40!black},
%	commentstyle=\itshape\color{purple!40!black},
%	identifierstyle=\color{blue!30!black},
%	showstringspaces=false,
%	stringstyle=\color{orange},
%	numbers=left,
%	tabsize=2,
%	breaklines=true,
%	breakatwhitespace=true,
%	language=C++
%}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}

	\newgeometry{
		left=3cm, right=2.5cm, top=1.5cm, bottom=1.5cm,
		includefoot, heightrounded
	}

\begin{document}

\title{A higher order approximate static condensation method for multi-material problems}
\author{
Alexander Zhiliakov\thanks{Department of Mathematics, University of Houston, Houston, Texas 77204 (alex@math.uh.edu).}
\and Daniil Svyatskiy\thanks{Los Alamos National Laboratory, Los Alamos,
New Mexico, USA (dasvyat@lanl.gov).}
\and
Maxim Olshanskii\thanks{Department of Mathematics, University of Houston, Houston, Texas 77204 (molshan@math.uh.edu); Partially supported by NSF through grant  DMS-1717516.}
}

\maketitle

\let\oldtabular\tabular
\renewcommand{\tabular}[1][1.5]{\def\arraystretch{#1}\oldtabular}

\begin{abstract}
The paper studies an approximate static condensation method for the diffusion problem with discontinuous diffusion coefficients. The method allows for a general polygonal mesh which is unfitted to the material interfaces. Moreover, the interfaces can be discontinuous across the mesh edges as typical for numerical reconstructions using the volume or moments of fluid methods.  We apply a mimetic finite difference method to solve local diffusion problems and use $P_1$ (mortar) edge elements to couple local problems into the global system. The condensation process and the properties of the resulting algebraic system are discussed. It is demonstrated that the method is second order accurate on smooth solutions and performs well for problems with high contrast in diffusion coefficients. Experiments also show the robustness with respect to position of the interface against the underlying mesh.
\end{abstract}

%\Sasha{Note that \texttt{usepackage\{dutchcal\}} seems to be not working with miktex (I need this package for a bold mathcal font). I use texlive and it works just ok. I left it commented so it compiles more or less everywhere. You may see some funny symbols from time to time  while reading if you leave it commented.}

\section{Introduction}
 Multi-phase and multi-material processes are ubiquitous in nature and engineering.
 Mathematical models of such processes are often formulated in terms of systems of partial differential equations with discontinuous coefficients and interface conditions on time-dependent internal boundaries.
 Due to their high complexity, these models   resist analytical treatment, and hence numerical simulations became an indispensable tool for solving the models and gaining insights into underlying phenomena.

 Past decades evidenced an 	explosive growth in developing of efficient computational techniques for problems with evolving interfaces, which involve interaction between many materials or different phases of matter. This includes immersed boundary method \cite{peskin2002immersed}, level-set method \cite{sethian1999level}, and unfitted finite element methods \cite{belytschko2009review,burman2015cutfem}, to name several popular numerical approaches.
 The present study is motivated by the successful applications of the volume of fluid (VOF)~\cite{hirt1981volume} and the moment of fluids (MOF) methods~\cite{ahn2009adaptive} for the numerical  reconstruction of time-dependent interfaces. Both  methods do not require a mesh aligned with the  interfaces and reconstruct them from the information about the volumes of materials in each cell.
 % implicitly with the help of a characteristic function
% and construct allow for general polygonal computational meshes not fitted to the position of the interface.
 The superior conservation properties of the  VOF and MOF approaches, however, commonly come at a price of recovering piecewise smooth interface approximation that is  discontinuous across the faces of the underlying computational mesh.

In this report, we devise  a higher order method for the numerical solution of the diffusion problem with discontinuous  coefficients on a general polyhedral mesh, which does not respect the position of multi-material interfaces.  The method builds upon the approximate static condensation (ASC) algorithm first  proposed in ~\cite{kikinzon2017approximate}; it admits high-contrast diffusion coefficients and discontinuous reconstruction of the interfaces as typical for the volume/moment of fluid method. The ASC approach uses the formulation of the interface diffusion problem as a system of local inter-cell problems  coupled through the concentration values and fluxes on the cell faces. This face concentration serves as the new primal unknown and it is further approximated by piecewise  polynomial functions defined on all faces of the global (unfitted polygonal) mesh. The original paper ~\cite{kikinzon2017approximate} considered $P_0$ (piecewise constant) approximation to the face concentration, while the present study introduces higher order polynomials for this purpose.
Although the latter potentially leads to more accurate results  (and in some cases we shall see that it provides convergent results, when the $P_0$ version fails), it also raises some questions about stability and robustness, which we address in the present report.

The approximate static condensation approach leaves much freedom in the choice of the discretization method for the local diffusion problems.  Posed in each polygonal cell, these problems are given by  diffusion equations with  discontinuous coefficients. The method benefits from the observation that   for any fixed cell $T$,  material interfaces, which possibly intersect with $T$,  induce a \emph{consistent polygonal subdivision} (local mesh) of $T$. Opposite to the global mesh, the local one is \emph{fitted} to interfaces, i.e. each micro polyhedral element is shared only by one material. Following~\cite{kikinzon2017approximate}, we apply the mimetic finite difference (MFD) method from~\cite{lipnikov2014mimetic} to approximate the local diffusion problems on this fine fitted mesh.
After eliminating inter-cell degrees of freedom, one obtains a system of linear algebraic equations for the face concentration degrees of freedom. The fluxes and inter-element degrees of freedom are recovered by simple postprocessing. In the report, we study the performance of the method in terms of accuracy, robustness with respect to the interfaces position,  and algebraic stability.

The remainder of the paper is organized as follows. In section~\ref{sec:model} we formulate the model diffusion problem with discontinuous diffusion tensor, introduce the basic mesh and discuss a reformulation of the model as a system of coupled local problems. Section~\ref{sec:ASC} presents the method and discusses certain  properties of the resulting  system of algebraic equations. Finally, section~\ref{sec:num} collects results of numerical experiments. These results include accuracy tests, numerical comparison with the method from  \cite{kikinzon2017approximate} and with a homogenization method as an alternative approach.

\section{Model problem and macro-mesh decomposition} \label{sec:model}
In a polygonal bounded domain $\Omega \subset \Rn{2}$  we consider the following diffusion problem in the mixed form
	\begin{equation}\label{dual}
		\left\{\begin{split}
			\vect K^{-1}\,\vect u &+ \nabla\,p\,&= 0&\quad\text{in } \Omega , \\
			\nabla\cdot\vect u    &+ c\,p       &= f&\quad\text{in } \Omega,
		\end{split}\right.
\end{equation}
with boundary data
		\begin{equation}
			p = g_D \quad\text{on } \partial\Omega_D,\qquad %\label{dual:bc:dirichlet} \\
			\vect u \cdot {\vect n} = g_N \quad\text{on } \partial\Omega_N. \label{dual:bc:neumann}
		\end{equation}
Here $p$ is a concentration and $\vect u$ is the diffusive flux, $\vect K$ is the positive definite  symmetric diffusivity tensor, which we assume constant within each material subdomain, $c\ge0$ is the reaction coefficient, $\vect n$ is the outward normal vector to $\partial\Omega$, $g_D$ and $g_N$ are Dirichlet and Neumann boundary data, respectively. In the context of fluid flows in porous media, \eqref{dual}--\eqref{dual:bc:neumann} is also known as the Darcy problem. In this case, $p$ has the meaning of pressure, $\vect u$ is fluid velocity and $\vect K$ is the permeability tensor.

	\begin{figure}[h]
		\centering
		\caption{The figure illustrates global unstructured polyhedral mesh (left); Physical interfaces for three materials and cut cells, i.e. multi-material cells (central); The piecewise-planar discontinuous reconstruction of the interfaces by the moment of fluid method (right). Everything is shown for two refinement level of the base mesh. \label{fig:problem_geometry}}
		\begin{subfigure}{.33\linewidth}
			\centering
			\includegraphicsw{ring_base_voronoi.png}
			\caption{Base Mesh}
			\label{fig:problem_geometry:base_mesh}
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.33\linewidth}
			\centering
			\includegraphicsw{ring_mmcs_voronoi.png}
			\caption{MMCs}
			\label{fig:problem_geometry:mmcs}
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.33\linewidth}
			\centering
			\includegraphicsw{ring_mini_voronoi.png}
			\caption{MOF reconstruction}
			\label{fig:problem_geometry:mof}
		\end{subfigure}
		\begin{subfigure}{.33\linewidth}
			\centering
			\includegraphicsw{ring_base_voronoi_refined.png}
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.33\linewidth}
			\centering
			\includegraphicsw{ring_mmcs_voronoi_refined.png}
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.33\linewidth}
			\centering
			\includegraphicsw{ring_mini_voronoi_refined.png}
		\end{subfigure}
	\end{figure}

We assume the triangulation  $\bmesh$ of $\Omega$ consisting of general polyhedral elements as illustrated in Figure~\ref{fig:problem_geometry} (left). This triangulation constitutes our macro-mesh. The material interfaces, i.e. surfaces where $\vect K$ may experience discontinuities, may cut through the macro-mesh in an arbitrary way; see Figure~\ref{fig:problem_geometry} (center). The polygonal cells ${\bcell \in \bmesh}$ cut by the interfaces are further called Multi-Material Cells (MMC). In practice,  we are given a reconstructed interface by a volume-of-fluid or moment-of-fluid method. This reconstructed interface may be discontinuous across faces of MMC, but locally within each ${\bcell \in \bmesh}$ it is a collection of planar surfaces; see Figure~\ref{fig:problem_geometry} (right).

Denote by $\bfaces$ the collection of all faces of the macro-mesh $\bmesh$. We shall distinct between the subset of internal and external faces,  $\bfaces = \bfaces[int] \cup \bfaces[ext]$\footnote{For the sake of  notation, we shall use  ~$\bfaces$ to denote both the set of elements and the corresponding domain formed by their union~$\cup_{F\in \bfaces} \bar{F}$; same for $\bfaces[int]$, $\bfaces[ext]$ and other collections of mesh elements introduced later in the text. The meaning should be clear from a context}.
Introducing the new unknown $\lambda\in H^{\frac12}(\bfaces)$, we reformulate \eqref{dual}--\eqref{dual:bc:neumann} as a system of local problems coupled through the boundary data
and flux continuity condition:
 	\begin{eqnarray}\label{dual_mini}
		%\begin{empheq}[left = \empheqlbrace]{alignat=2}
\left\{
\begin{split}
			\vect K^{-1}\,\vect u &+ \nabla\,p\,    &= 0       &\quad\text{in } \bcell, \\
			\nabla\cdot\vect u    &+ c\,p           &= f       &\quad\text{in } \bcell, \\
			                      &\phantom{+cc\,}p &= \lambda &\quad\text{on } \partial\bcell, %\label{dual_mini:trace}
		%\end{empheq}
\end{split}
\right.&
\qquad \forall~\bcell\in\bmesh,\\
        \left[\vect u\cdot\hat{\vect n}\right]=0\quad\text{on } F& \qquad \forall~F\in\bfaces[int]  \label{flux_cond}
	\end{eqnarray}
Here $\hat{\vect n}$ denotes a normal vector to the face $F\in\bfaces[int]$ and $\left[\vect u\cdot\hat{\vect n}\right]$ is the jump of the normal flux across $F$. On the outer boundary $\partial\Omega$ we assume \eqref{dual:bc:neumann}.

Note that~$\lambda$ defines Dirichlet boundary data for local diffusion problems. Once~$\lambda$ is known, one can solve \eqref{dual_mini} for $\vect u$ and $p$ inside each element independently, and hence recover the solution of the original problem~\eqref{dual}. The idea behind the ASC method is to introduce a piecewise polynomial space to approximate $\lambda$, and  define discretizations of subproblems from \eqref{dual_mini}. This local subproblems are further explicitly resolved to eliminate internal degrees of freedom and to form a system of algebraic equations for $\lambda$.

Before we go into details of the method, we note that $\lambda$ can also  be observed as the Lagrange multiplier corresponding to the normal flux condition~\eqref{flux_cond}. The problem \eqref{dual_mini}--\eqref{flux_cond} can be formulated in the weak form: Find  $\vect u  \in \bigotimes\limits_{\bcell\in\bmesh}\HDivSpace[\bcell]$, $ p\in\LTwoSpace[\Omega]$, $\lambda\in H^{\frac12}(\bfaces[int])$ such that $\vect u\cdot{\vect n}=g_N$ on $\partial\Omega_N$ and
	%\begin{empheq}[box=\widefbox]{equation}
\begin{equation}\label{weak_form}
		\begin{split}
				\int_{\Omega} \vect K^{-1}\,\vect u\cdot\vect v \diff \vect x - \sum_{\bcell\in\bmesh}\int_\bcell p\,\nabla\cdot\vect v \diff \vect x +\int_{\bfaces[int]} \lambda\,\left[\vect v\cdot\hat{\vect n}\right] \diff \vect l &- \int_{\bfaces[int]}\left[\vect u\cdot\hat{\vect n}\right]\mu\diff \vect l, \\
				+\sum_{\bcell\in\bmesh}\int_\bcell \nabla\cdot\vect u\,q \diff \vect x + \int_\Omega c\,p\,q \diff \vect x &= \int_\Omega f\,q \diff \vect x-\int_{\partial\Omega_D}\vect v\cdot{\vect n}g_D\diff \vect l
		\end{split}
	\end{equation}
for all $\vect v  \in \bigotimes\limits_{\bcell\in\bmesh}\HDivSpace[\bcell]$, $ q\in\LTwoSpace[\Omega]$, $\mu\in H^{\frac12}(\bfaces[int])$.

	\section{Approximate Static Condensation Method} \label{sec:ASC}

	In this section we describe  approximate static condensation method of order $n$ ( ASC($n$)\,), for solving the multi-material heterogeneous diffusion problem~\eqref{dual}.

        Consider an arbitrary but fixed cell $T\in\bmesh$. We now introduce the discretization of the local diffusion problem \eqref{dual_mini} in $T$.
        To this end, we consider the local mesh $\mmesh(T)$ of $T$, which is reffered as mini-mesh. While the original triangulation $\bmesh$ is referred as macro-mesh.
\begin{wrapfigure}{r}{0.4\textwidth}
\vspace{-10pt}
  \begin{center}
    \includegraphics[width=0.3\textwidth]{./ring_mini_voronoi_cell.png}%{./Pictures/mainscreen1.png}
    \caption{Local polyhedral mesh for a three-material cell $T\in\bmesh$.\label{fig:mmesh}}
  \end{center}
  \vspace{-15pt}
  \vspace{1pt}
\end{wrapfigure}
If $T$ contains only one phase or material, then we obviously have $\mmesh(T) = \{\bcell\}$. Otherwise for the cell shared by several phases, $\mmesh(T)$ consists of polygonal elements, forming a tessellation of $T$, such that any ${\tau \in \mmesh(T)}$ contains only one phase/material; see Figure~\ref{fig:mmesh}. We denote by $\mfaces(T)$ the set of all faces in $\mmesh(T)$, which collects both   internal and boundary (external) faces with respect to $T$,  $\mfaces(T) = \mfaces[int](T) \cup \mfaces[ext](T)$. Thus for the example of local mesh drafted in Figure~\ref{fig:mmesh}, we have three elements in $\mmesh(T)$, two internal faces from $\mfaces[int](T)$ and eleven external faces from $\mfaces[ext](T)$. It is clear that this local mesh is fitted to the material interfaces.

We shall discretize \eqref{dual_mini} in $T$ in terms of average fluxes assigned to each face from $\mfaces(T)$,
we denote the corresponding vector by ${\vect u}_\mmesh\in\mathbb{R}^{n_f}$, $n_f=2\,(\#\mfaces(T))$,  and concentration values assigned to each cell  ${\tau \in \mmesh(T)}$, we denote the corresponding vector by ${\vect p}_\mmesh\in\mathbb{R}^{n_p}$, $n_p=\#\mmesh(T)$. The given data is the source term vector ${\vect f}_\mmesh\in \mathbb{R}^{n_p}$ and the concentration values $\lambda$ on the boundary of $T$.
To approximate this boundary data \emph{for the local problem}, we introduce the vector
${\vect \lambda}_\mmesh\in\mathbb{R}^{n_\lambda}$, $n_\lambda=\#\mfaces[ext](T)$,
where we assign one averaged concentration value for each $f\in\mfaces[ext](T)$, so that ${\vect \lambda}_\mmesh$ can be seen as a piecewise-constant approximation of $\lambda$ with respect to the subdivision of $\partial T$ into the faces of the local mesh $\mmesh$.

%On the faces of macro mesh $\bmesh$ this

Given the above definition of the degrees of freedom on the local mesh we apply the mimetic finite difference (MFD) method from~\cite{lipnikov2014mimetic}. The method leads to the following system of equations with the matrix having the block structure:
	\begin{equation}\label{local}
		\begin{pmatrix}
			\vect M_\mmesh & \vect B^T_\mmesh \\
			-\vect B_\mmesh & \vect \Sigma_\mmesh
		\end{pmatrix}
		\begin{pmatrix}
			{\vect u}_\mmesh \\
			{\vect p}_\mmesh
		\end{pmatrix}
		=
		\begin{pmatrix}
			\vect E_\mmesh\,\vect C_\mmesh\,{\vect \lambda}_\mmesh \\
			{\vect f}_\mmesh
		\end{pmatrix}.
	\end{equation}
Here $\vect M_\mmesh,~\vect\Sigma_\mmesh$, $\vect B^T_\mmesh$, $-\vect B_\mmesh$ are vector-mass, mass, gradient and divergence matrices, respectively.
$C_\mmesh$ is a diagonal scaling matrix. i.e. the mass matrix for ${\vect \lambda}_\mmesh$ unknowns;
$\vect E_\mmesh \in \mathbb{R}^{n_{\lambda}\times n_f} $ is a rectangular matrix with 0 and 1 entries which sparsifies a vector from  $\mathbb{R}^{n_{\lambda}}$
to a vector from  $\mathbb{R}^{n_{f}}$.
For the details on MFD and accurate definition of the matrices we refer to \cite{lipnikov2014mimetic,MFDbook}.
Here we need the property that  $\vect B_\mmesh$ has a full row rank, and $\vect M_\mmesh = \vect M^T_\mmesh$ is positive definite.

Since the continuity of flux condition \eqref{flux_cond} and boundary conditions are enforced on all the \emph{external} edges of $T$, we need to distinct the vector ${\vect u}^\text{ext}_\mmesh$ of fluxes on $\mfaces[ext](T)$, which is just a trivial restriction of ${\vect u}_\mmesh$ on the edges  from $\mfaces[ext](T)$,
	\begin{equation}\label{system_mini}
		{\vect u}^\text{ext}_\mmesh \coloneqq \vect E_\mmesh^T\,{\vect u}_\mmesh
	\end{equation}
where $E_\mmesh^T$ is the restriction matrix with entries equal $0$ or $1$.

We now eliminate ${\vect u}_\mmesh$ from \eqref{local} and express ${\vect p}_\mmesh$ in terms of~${\vect \lambda}_\mmesh$ (\textit{static condensation}); recovering fluxes (backward substitution) and using~\eqref{system_mini} we get
	\begin{equation}\label{mini_flux_dofs}
		{\vect u}^\text{ext}_\mmesh = \vect A_\mmesh\,\vect C_\mmesh\,{\vect \lambda}_\mmesh - {\vect a}_\mmesh,
	\end{equation}
with
	\begin{align} \label{defA}
		\vect A_\mmesh &= \vect E^T_\mmesh \left( \vect M^{-1}_\mmesh + \vect M^{-1}_\mmesh\,\vect B^T_\mmesh \left( \vect \Sigma_\mmesh + \vect B_\mmesh\,\vect M^{-1}_\mmesh\,\vect B^{T}_\mmesh\right)^{-1} \vect B_\mmesh\,\vect M^{-1}_\mmesh \right) \vect E_\mmesh, \\
		{\vect a}_\mmesh &= \vect E^{T}_\mmesh\,\vect M^{-1}_\mmesh\,\vect B^T_\mmesh \left( \vect \Sigma_\mmesh + \vect B_\mmesh\,\vect M^{-1}_\mmesh\,\vect B^{T}_\mmesh\right)^{-1} {\vect f}_\mmesh.
	\end{align}
Note that matrices ~$\vect A_\mmesh$ and vector~${\vect a}_\mmesh$ are computed locally for each $T\in\bmesh$.
\smallskip
%	Matrix~$\vect A_\mmesh$ and vector~${\vect a}_\mmesh$ can be easily computed if the number of mini\,cells is relatively small. Otherwise, one may prefer to use a mixed-hybrid formulation instead of~$\eqref{weak_form}$ (see section~\ref{MH}).

Next, we should use the continuity of flux condition \eqref{flux_cond} and boundary conditions to obtain a complete system for ${\vect u}^\text{ext}_\mmesh$ and ${\vect \lambda}_\mmesh$. However, we cannot do this in a straightforward way, since the discontinuity of material interfaces across the macro-mesh faces may lead to a mismatch of discrete fluxes from two sides of $F\in\bfaces[int]$, including different space dimensions.
Therefore, we shall enforce the flux continuity condition in the spirit of the mortar finite element method~\cite{mortar} using the space of function defined on $\bfaces[int]$, which are polynomials of degree at most $n$ on every $F\in\bfaces[int]$, an analog of the Lagrange multiplier space in the mortar method:
\[
\Lambda=\left\{\lambda\in L^2(F)\,:\, \lambda\in P_n~\text{for any}~F\in\bfaces[int]\right\}.
\]

%	Let $F \coloneqq {\bcell^+} \cap {\bcell^-}$, $F \in \bfaces[int]$, be a face shared by base\,cells~$\bcell^+$ and~${\bcell^- \in \bmesh}$ with mini\,meshes~$\mmesh^\pm$ and mini\,faces~$\mfaces^\pm$, respectively. We denote by~$\mfaces^\pm_F \subset \mfaces^\pm_{\text{ext}}$ mini\,faces that belong to the face~$F$. In general measures of mini\,faces of~$\mfaces^\pm_F$ corresponding to one material may be different, and, moreover, it may be the case that $\#\,\mfaces^+_F \ne \#\,\mfaces^-_F$ (see figure~\ref{fig:e_plus_e_minus}). That is, one may have different trace DOFs~\eqref{dual_mini:trace} from~$\mmesh^+$ and~$\mmesh^-$.
%%	Let us set~$\nu_{F_{\bcell^\pm}} \coloneqq \#\,\mfaces^\pm_F$
%	We set~$\nu_F \coloneqq \max\,\{ \#\,\mfaces^+_F,\,\#\,\mfaces^-_F \}$.
%	
%	\begin{figure}[h]
%		\centering
%		\caption{MMCs: $3 = \#\,\mfaces^+_F \ne \#\,\mfaces^-_F = 2$, $\nu_F = 3$}
%		\label{fig:e_plus_e_minus}
%		\svginputw[.7\linewidth]{e_plus_e_minus.pdf_tex}
%	\end{figure}

When the Lagrange multiplier space $\Lambda$ couples local MFD solutions, it is convenient to define
degrees of freedom for $\lambda\in\Lambda$ in terms of its~$(n+1)$ moments $\lambda^{(i)}_F$ on every internal face $F\in\bfaces[int]$:
	\begin{equation}\label{asc_dofs}
		\lambda^{(i)}_F=\frac{\int_F  \lambda\,s_i \diff l}{|F|}, \quad i = 0, \dots, n.
	\end{equation}
	Here~$\{s\}_{i=0,\dots,n}$ is the set of $L^2(F)$-orthogonal polynomials of degree~$n$.

 For $F \in \bfaces[int]$ shared by two polygonal cells~$\bcell^\pm\in \bmesh$  denote by~$\mfaces^\pm_F \subset \mfaces_{\text{ext}}(T^\pm)$ the subsets of mini-faces that belong to the macro-face~$F$ from each side.  Let~$\nu_F \coloneqq \max\,\{ \#\,\mfaces^+_F,\,\#\,\mfaces^-_F \}$.  	
With each face $F \in \bfaces_\bcell$ we associate~$\min\,\{ n+1, \nu_F \}$ degrees of freedom~\eqref{asc_dofs} in the $\Lambda$ space. The local and global number of DOFs are
	\[
		n_\bcell = \sum_{F \in \bfaces_\bcell} \min\,\{ n+1, \nu_F \} \quad\text{and}\quad
		n_\bmesh = \sum_{F \in \bfaces} \min\,\{ n+1, \nu_F \},
	\]
 respectively.

Further denote by~${{\vect \lambda}_\bcell \in \Rn{n_\bcell}}$ a vector of DOFs for elements of $\Lambda$ associated with all macro-faces spanning the boundary of~$\bcell$. We need a correspondence between elements of $\Lambda$ and local edge elements $\lambda_\mmesh$ used as boundary data in local problem \eqref{local}.
This corresponding is given by the interpolation matrix $ \vect R_\mmesh$,
	\begin{equation}\label{asc_lambda}
		{\vect \lambda}_\mmesh = \vect R_\mmesh\,{\vect \lambda}_\bcell,
	\end{equation}
where ${\vect \lambda}_\mmesh$ is effectively a piecewise constant approximation of ${\vect \lambda}_\bcell$ on $\mfaces_{\text{ext}}(T)$.
Using this in \eqref{mini_flux_dofs}, we get
	\begin{equation}\label{asc_flux_lambda}
		{\vect u}^\text{ext}_\mmesh = \vect A_\mmesh\,\vect C_\mmesh\,\vect R_\mmesh\,{\vect \lambda}_\bcell + {\vect a}_\mmesh.
	\end{equation}
	%The interpolating matrix~$\vect R_\mmesh$ is completely defined by~$n$ and boundary mini\,faces~$\mfaces[ext]$ of~$\mmesh$.
If we find the mortar vector ~${\vect \lambda}_\bcell$, we recover the local approximation to the edge concentration, i.e. ${\vect \lambda}_\mmesh$, from~\eqref{asc_lambda}.
Further we solve numerically local subproblems in~\eqref{dual_mini} applying the mimetic FD method. This completes the solution algorithm for \eqref{dual}.

	The dimension of the $\Lambda$ space is~$n_\bmesh$, i.e. $(n+1)$ or less unknowns for each face~${F \in \bfaces}$.
        To obtain the system of $n_\bmesh$ equations, we enforce the weak continuity of the moments of  fluxes  on each internal macro-face
	\begin{equation}\label{flux_cont}
		\int_F \vect u|_{\bcell^+}\cdot\hat{\vect n}\,s_i \diff l = \int_F \vect u|_{\bcell^-}\cdot\hat{\vect n}\,s_i \diff l, \quad i = 0, \dots, n, \quad \text{for each } F \in \bfaces[int],
	\end{equation}
with $\vect u|_{\bcell^+}(x)={\vect u}^\text{ext}_\mmesh(f)|f|$, if $x\in f$ for $f\in \mfaces[ext](\bcell^+)$, and ${\vect u}^\text{ext}_\mmesh(f)$ is the local flux assigned to $f$. Similar definition applies to $\vect u|_{\bcell^-}$. 	
This and ~\eqref{asc_flux_lambda} result in the linear algebraic system
	\begin{equation}\label{asc_system}
		\vect S_\bmesh\,{\vect \lambda}_\bmesh = {\vect b}_\bmesh,
	\end{equation}
with	$\vect S_\bmesh \in \Rn{n_\bmesh \times n_\bmesh}, {\vect \lambda}_\bmesh, {\vect b}_\bmesh \in \Rn{n_\bmesh}$.
Neumann boundary condition in~\eqref{dual:bc:neumann} is handle in the similar way, and Dirichlet boundary data in~\eqref{dual:bc:neumann} is enforced strongly in~\eqref{asc_system}.

	Matrix~$\vect S_\bmesh$ is sparse and its sparsity pattern does not depend on mini-meshes. Some useful properties of this matrix will be discussed in the next section.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Matrix properties}

In this section we discuss the assembly procedure of the global matrix from \eqref{asc_system} and show that $\vect S_\bmesh$ is symmetric positive definite. We concentrate on ASC(1), which we implement and validate  in the next section. We shall make necessary remarks about ASC(0) as it is largely obtain by obvious simplifications of ASC(1).

\begin{figure}[h]
		\centering		
		\begin{subfigure}{.45\linewidth}
			\centering
			\svginputw{e_plus_1.pdf_tex}
			\caption{$\nu_F = 1$}%,
			\label{fig:asc_dofs:asc1:pc}
		\end{subfigure}%
		\qquad\quad
		\begin{subfigure}{.45\linewidth}
			\centering
			\svginputw{e_plus_2.pdf_tex}
			\caption{$\nu_F = 2$}		
		\end{subfigure}
\caption{$\lambda_{ij}(\mmesh)$ are local d.o.f. used in MFD for $\lambda$ from \eqref{dual_mini}, $\lambda_{i}(T)$, $\lambda'_{i}(T)$ are global d.o.f. used to describe mortar space $\Lambda$.
Left: Face $F$ is single-material and uses one global d.o.f.; Right: Face $F$ is multi-material and uses two global d.o.f.\label{fig:asc_dofs:asc1:mmc}}
	\end{figure}

The method uses local piecewise constant  and global piecewise $P_1$ (for ASC(1)\,) approximation of the concentration on $\bfaces$. Local piecewise constant approximations $\lambda_\mmesh$, however, use finer local subdivisions and so $\lambda_\mmesh$ does not belong to the restriction of the global space $\Lambda$ on the boundary of a given cell $T$. For the method, we define a mapping given by the matrix $\vect R_\mmesh$ to map global to local degrees of freedom and $\vect R_\mmesh^T$ from local   to global. For the well-posedness of the method, we need $\vect R_\mmesh$ to have a full rank.

We  define $\vect R_\mmesh$ locally for any fixed $T\in\bmesh$. Let us enumerate all faces of the given $T$ by index $j$. For example, $j=1,\dots,4$ for the polygonal cell in Figure~\ref{fig:asc_dofs:asc1:mmc}. For each $j$, index $i$ enumerates mini-faces from $\mfaces[ext](T)$ belonging to the macro-face $j$. For example, $i\in\{1,2,3\}$ for $j=1$ and $i\in\{1\}$ for $j=4$ for the same example in Figure~\ref{fig:asc_dofs:asc1:mmc}.
Further,  denote by $\lambda_{j\,i}(\mmesh)$ the local d.o.f. assigned  to the $i$-th mini-face~ belonging to the $j$-th macro-face~, and by $\lambda_{j}(T)$, $\lambda_{j}'(T)$ to moments defining an element from $\Lambda$ on the $j$-th macro-face (see Figure~\ref{fig:asc_dofs:asc1:mmc})) so that
we have for $\lambda\in\Lambda$,
	\begin{equation}\label{lambda_intermsof_moments}
		{\lambda}\big({\vect r}(t)\big) = \lambda_{j}'(T)|F|\,t + \left( \lambda_{j}(T) - \frac{\lambda_{j}'(T)\,|F|}{2} \right),\qquad  F\in\bfaces[int],
	\end{equation}
where $t\in(0,1)$ and ${\vect r}\::\:\left(0,1\right) \rightarrow F$ is the affine parametrization of $F$, which has index $j$ among macro-faces of $T$.

Integrating \eqref{lambda_intermsof_moments} over all mini-faces $f\in \mfaces(T)\cap F$ ($f$ has local index $i$ among mini-faces belonging to $F$) and re-scaling, we get
	\begin{equation}\label{asc1_interp}
		\lambda_{j\,i}(\mmesh) =
		\begin{cases}
			\lambda_{j}(\bcell) +  s_{j\,i}\,\lambda'_{j}(\bcell), & \text{if}~F~\text{is a multi-material face}, \\
			\lambda_{j}(\bcell),                                    & \text{otherwise},
		\end{cases}
	\end{equation}
	where $s_{j\,i} $ is a signed distance between centroids of~$f$  and~$F$. For the corresponding vectors of unknowns  ${\vect \lambda}_\mmesh = \{ \lambda_{j\,i}(\mmesh) \}$ and ${\vect \lambda}_\bcell = \{ \lambda_{i}(\bcell) \}$ this defines
the matrix $\vect R_\mmesh$ through
\[
{\vect \lambda}_\mmesh=\vect R_\mmesh {\vect \lambda}_\bcell.
\]
For the example in Figure~\ref{fig:asc_dofs:asc1:mmc}\,(left), $\vect R_\mmesh$ is given by
\begin{equation*}\footnotesize
	\vect R_\mmesh
		=
		 \begin{pmatrix}
			1 &  s_{1\,1} & 0 & 0 & 0 & 0 & 0 \\
			1 &  s_{1\,2} & 0 & 0 & 0 & 0 & 0 \\
			1 &  s_{1\,3} & 0 & 0 & 0 & 0 & 0 \\
			0 & 0 & 1 &  s_{2\,1} & 0 & 0 & 0 \\
			0 & 0 & 1 &  s_{2\,2} & 0 & 0 & 0 \\
			0 & 0 & 1 &  s_{2\,3} & 0 & 0 & 0 \\
			0 & 0 & 0 & 0 & 1 &  s_{3\,1} & 0 \\
			0 & 0 & 0 & 0 & 1 &  s_{3\,2} & 0 \\
			0 & 0 & 0 & 0 & 0 & 0 & 1
		\end{pmatrix}.		
	\end{equation*}
For ASC(0) the matrix $\vect R_\mmesh$  is as above with rows containing $s_{ij}$-s eliminated.
%Since the fourth base\,face $F \in \bfaces_\bcell$ has only one material, a trace on~$F$ from the cell~$\bcell$ is approximated by a constant. However, if in the adjacent cell we have several materials on $F$\footnotemark{}, we will use the value of~$\lambda'_{\bcell\,4}$ to improve the approximation of the fine traces on~$F$ in the adjacent cell.

Now, when the mappings between local and global approximations of $\lambda$ are defined, we are ready to proceed with the assembly of the global matrix $\vect S_\bmesh$. 	The flux continuity over the face $F$ condition ~\eqref{flux_cont} yields
	\begin{equation*}
\left\{
\begin{split}
		\sum_{f\in \mfaces(T^+)\cap F} u^{\text{ext}}_{\mmesh^+}(f)\,|f| &+ \sum_{f\in \mfaces(T^-)\cap F} u^{\text{ext}}_{\mmesh^-}(f)\,|f| &= 0 \\
		\sum_{f\in \mfaces(T^+)\cap F} u^{\text{ext}}_{\mmesh^+}(f)\,\int_{f} s_1 \diff{l} &+ \sum_{f\in \mfaces(T^-)\cap F} u^{\text{ext}}_{\mmesh^-}(f)\,\int_{f} s_1 \diff{l} &= 0
\end{split}
\right.
%\quad\Leftrightarrow \\
%		\sum_{i \in I_{\mfaces^+_F}} u^{\text{ext}}_{\mmesh^+\,i}\,\Delta s^+_i\,|\mfaces^+_{F\,i}| &+ \sum_{i \in I_{\mfaces^-_F}} u^{\text{ext}}_{\mmesh^-\,i}\,\Delta s^-_i\,|\mfaces^-_{F\,i}| = 0,
	\end{equation*}
	or in the matrix form
	\begin{equation}\label{eq:aux1}
		\left( \vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,{\vect u}^{\text{ext}}_{\mmesh^+} \right)_i + \left( \vect R^T_{\mmesh^-}\,\vect C_{\mmesh^-}\,{\vect u}^{\text{ext}}_{\mmesh^-} \right)_j = 0,
	\end{equation}
where $i$ and $j$ are the local indexes of the face $F$ in the cells $T^+$ and $T^-$, respectively.
If $F$ from $T^+$ belong to the Neumann part of the boundary, then we have
	\begin{align*}
		\left( \vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,{\vect u}^{\text{ext}}_{\mmesh^+} \right)_i &= \left( \vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,{\vect g}_{N\,\mmesh^+} \right)_i, \quad
		{\vect g}_{N\,\mmesh^+} &\coloneqq \left\{ \int_f g_N\,s_k \diff{l}\,/\,|f| \right\}_{f \in \mfaces[ext,\,\textit{N}]}, \quad k = 0, 1.
	\end{align*}

Substituting~\eqref{asc_flux_lambda} into \eqref{eq:aux1} we get the local equation for~${\vect \lambda}_\bcell$
	\begin{align}\label{local_system}
		\begin{split}
			\Big( \underbrace{\left( \vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,\vect A_{\mmesh^+}\,\vect C_{\mmesh^+}\,\vect R_{\mmesh^+} \right)}_{\vect S_{\bcell^+} \coloneqq} {\vect \lambda}_{\bcell^+} \Big)_i
			&+
			\Big( \underbrace{\left( \vect R^T_{\mmesh^-}\,\vect C_{\mmesh^-}\,\vect A_{\mmesh^-}\,\vect C_{\mmesh^-}\,\vect R_{\mmesh^-} \right)}_{\vect S_{\bcell^-} \coloneqq} {\vect \lambda}_{\bcell^-} \Big)_j = \\
			\big( \underbrace{\vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,{\vect a}_{\mmesh^+}}_{{\vect b}_{\bcell^+}} \big)_i
			&+
			\big( \underbrace{\vect R^T_{\mmesh^-}\,\vect C_{\mmesh^-}\,{\vect a}_{\mmesh^-}}_{{\vect b}_{\bcell^-}} \big)_j.
		\end{split}
	\end{align}
As standard in finite element methods, one assembles the global system~\eqref{asc_system} from the local matrices and local right-hand side vectors.  Thus we may formally write
	\begin{align}\label{global_system_assembly}
		%\begin{split}
			\vect S_\bmesh = \sum_{\bcell \in \bmesh} \vect N^T_\bcell\,\vect S_\bcell\,\vect N_\bcell, \quad
			{\vect b}_\bmesh = \sum_{\bcell \in \bmesh} \vect N^T_\bcell\,{\vect b}_\bcell.
		%\end{split}
	\end{align}
where $N_\bcell$ defines global to local mapping for the cell $T$.

From~\eqref{local_system} it is clear that~$\vect S_\bmesh$ is sparse: Global  $\lambda_{\bmesh\,i}$ interacts only with d.o.f. associated with faces of macro elements that share $i$th base\,face. For example, if $F\in\bfaces[ext]$ is shared by two quadrilaterals and has global index $i$, then $i$th row of~$\vect S_\bmesh$ will have~7 nonzero elements. %; if $i$th base\,face is a face shared by a quadrilateral and a triangle, $i$th row of~$\vect S_\bmesh$ will have~6 nonzero elements and so forth.

	Now we show that the global matrix~$\vect S_\bmesh$ in~\eqref{asc_system} is symmetric and positive definite. We give the arguments for ASC(1). Same arguments hold for  ASC(0) after obvious simplifications.
	%\begin{theorem}\label{thm:asc0}
%		$\Ker\vect R_\mmesh = \{ {\vect 0} \}$ for ASC(0)
%	\end{theorem}
%	\begin{proof}
%		From~\eqref{asc0_interp} we have that for any cell~$\bcell$\,/\,its mini\,mesh~$\mmesh$ the interpolating matrix may be written as
%		\begin{equation*}
%			\vect R_\mmesh =
%			\begin{pmatrix}
%				{\vect e}_1 & & & \\
%				& {\vect e}_2 & & \\
%				& & \ddots & \\
%				& & & {\vect e}_m
%			\end{pmatrix},
%		\end{equation*}
%		where~$m \coloneqq$ number of base\,faces spanning~$\bcell$ and ${\vect e}_k \coloneqq$ column vector of all ones; its length is the number of mini\,faces of the base\,face~$k$. Clearly, columns of~$\vect R_\mmesh$ are linearly independent.
%		
%	\end{proof}

	\begin{lemma}\label{thm:asc1}
		%If~$\bfaces_\bcell \cap \bfaces[\textnormal{mixed}] = \varnothing$, then~
		$\Ker\vect R_\mmesh = \{ {\vect 0} \}$ for ASC(1)
	\end{lemma}
	\begin{proof}
		From~\eqref{asc1_interp} we have that for any cell~$\bcell$ and its mini-mesh~$\mmesh(T)$
		%that has no mixed base\,faces, ${\bfaces_\bcell \cap \bfaces[mixed] = \varnothing}$,
		the interpolating matrix may be written as
		\begin{equation}\label{r_wo_mixed}\footnotesize
			\vect R_\mmesh =
			\begin{pmatrix}
				\vect S_1 & & & \\
				& \vect S_2 & & \\
				& & \ddots & \\
				& & & \vect S_m
			\end{pmatrix},
		\end{equation}
		where~$m \coloneqq$ number of base\,faces spanning~$\bcell$ and
		\begin{equation*}
			\vect S_k \coloneqq
			\begin{cases}
				\begin{pmatrix}
					1 &  s_{k\,1} \\
					\vdots & \vdots \\
					1 &  s_{k\,m_k} \\
				\end{pmatrix}, & \text{if }k\text{th face is multi-material face}, \\
				1, & \text{otherwise},
			\end{cases}
		\end{equation*}
		$1 < m_k$ is the number of mini-faces of the~$k$th macro-face, $ s_{k\,i}$ is the signed distance between centroids of~$i$th mini-face and~$k$th base\,face. If~$\bcell$ contains only one material, then $\vect R_\mmesh = \vect I$ and hence $\Ker\vect R_\mmesh = \{ {\vect 0} \}$, so we assume that there is at least one multi-material  face.

		Clearly, matrix~$\vect R_\mmesh$ has a non\,--\,trivial kernel iff
		\begin{equation*}
			 s_{k\,i} =  s_{k\,j}, \quad i, j = 1, 2, \dots, m_k
		\end{equation*}
		for some~$k$. Take some $\vect S \equiv \vect S_k$ corresponding to a multi-material face~$F \in \bfaces_\bcell$ with~${l \coloneqq m_k}$ materials,
		\begin{equation*}
			\vect S = \begin{pmatrix}
				1 &  s_1 \\
				\vdots & \vdots \\
				1 &  s_l \\
			\end{pmatrix}.
		\end{equation*}
		It is sufficient to show that~$ s_1 \ne  s_2$. Let $f_1$ and $f_2$ be corresponding mini-faces. We have
		\[
			 s_1 = \frac{1}{2}\left( |f_1| - |F| \right), \quad
			 s_2 = |f_1| + \frac{1}{2}\left( |f_2| - |F| \right)
		\]
		and
		\begin{equation*}
			 s_1 =  s_2 \quad\Leftrightarrow\quad |f_1| + |f_2| = 0.
		\end{equation*}
		Hence $ s_1 \ne  s_2$, and~$\Ker\vect R_\mmesh = \{ {\vect 0} \}$ follows.

	\end{proof}

	\begin{theorem} Matrix $\vect S_\bmesh$ is symmetric. If $c \ne 0$ or $|\partial\Omega_D|>0 $, then  $\vect S_\bmesh$ is positive definite.
	\end{theorem}

\begin{proof}
		From the identity \eqref{defA} it immediately follows that $\vect A_{\mmesh}$ is symmetric and non-negative definite.  Thus, the symmetry of $\vect S_\bmesh$ follows from the definition in \eqref{local_system}--\eqref{global_system_assembly}.
It is easy to see that $\vect A_{\mmesh}$ is positive definite for all~$\bcell$, where $c \ne 0$. Hence if $c \ne 0$ in $\Omega$ , then \eqref{local_system}--\eqref{global_system_assembly} and the full ranks of $\vect R$-s and $\vect C$-s imply
the positive definiteness of $\vect S_\bmesh$.
Now we show the positive definiteness of $\vect S_\bmesh$ if $|\partial\Omega_D|>0 $. Consider  any given $\bcell\in\bmesh$.
Matrix  $\vect A_{\mmesh}$ defines the discrete Dirichlet-to-Neumann map for $\partial\bcell$.
If $\partial\bcell\cap\partial\Omega_D$, then $\mbox{ker}(\vect A_{\mmesh})=0$. Otherwise $\mbox{dim}(\mbox{ker}(\vect A_{\mmesh}))=1$ and $\vect A_{\mmesh}\vect C_{\mmesh}\lambda_\mmesh=0$ implies that $\lambda_\mmesh$ is constant on $\partial\bcell$. Consider some $\lambda$ from the mortar space $\Lambda$ and corresponding vector of moments  $\vect \lambda_\bmesh$. Using connectivity of the mesh one easily finds that $\vect R_\mmesh \lambda_\bmesh$ can be constant on every $T\in\bmesh$ only if $\lambda$ is constant. Due to the assumption $|\partial\Omega_D|>0 $ this implies $\lambda=0$.
% Thus we have
%		\begin{equation*}
%			\big(\vect S_\bcell\,{\vect x},\,{\vect x}\big) =
%			\big(\vect R^T_\mmesh \left( \vect C_{\mmesh}\,\vect A_{\mmesh}\,\vect C_{\mmesh} \right) \vect R_\mmesh\,{\vect x},\,{\vect x} \big) =
%			\big(\vect A_{\mmesh}\,\vect C_{\mmesh}\,\vect R_\mmesh\,{\vect x},\,\vect C_{\mmesh}\,\vect R_\mmesh\,{\vect x} \big) \ge 0
%		\end{equation*}
%		for all~$\bcell \in \bmesh$ and
%		\begin{equation*}
%			\big(\vect S_\bcell\,{\vect x},\,{\vect x} \big) > 0
%		\end{equation*}
%		for some~$\bcell \in \bmesh$ since~$\Ker\vect R_\mmesh = \{ {\vect 0} \}$. So
Hence for any $0\neq\lambda_\bmesh\in \mathbb{R}^{n_\bmesh}$ we have
		\begin{align*}
			\left(\vect S_\bmesh\,\lambda_\bmesh,\,\lambda_\bmesh\right) &\stackrel{\eqref{global_system_assembly}}{=}
			\Big( \big( \sum_{\bcell \in \bmesh} \vect N^T_\bcell\,\vect S_\bcell\,\vect N_\bcell \big){\lambda_\bmesh},\,{\lambda_\bmesh} \Big) =
			\sum_{\bcell \in \bmesh} \big( \vect S_\bcell\,\vect N_\bcell\,{\lambda_\bmesh},\,\underbrace{\vect N_\bcell\,{\lambda_\bmesh}}_{{\vect x} \coloneqq} \big)\\
& =
			\sum_{\bcell \in \bmesh} \big(\vect S_\bcell\,{\vect x},\,{\vect x} \big) > 0.
		\end{align*}
The last inequality holds, since the exists $\bcell$ such that $\vect x=N_\bcell\,{\lambda_\bmesh}$ is not in the kernel for $\lambda_\bmesh\neq0$.
	\end{proof}

        \input{num_sec.tex}

 \subsection*{Acknowledgements} Alexander Zhiliakov acknowledges the internship opportunity in Methods and Algorithms group of the Los Alamos National Laboratory.
\bibliographystyle{plain}
\bibliography{bibl}

\end{document}

### 2018-11-16 num_sec.tex
Initial commit

\section{Numerical Results}\label{sec:num}

We define \textit{discrete} $\LTwo$\,--\,norm of $v \in \mathbb V_h \subset \LTwoSpace$
\begin{equation}\label{l2}
  \| v \|_{\lTwoSpace} \coloneqq \| P_h\,v \|_{\LTwoSpace},
\end{equation}
where $P_h \coloneqq$ $\LTwo$\,--\,projection operator on the space of piecewise constant
functions on each mesh element~$\bcell \in \bmesh_h$ (or on each~$\mcell \in \mmesh_h$
if $\bcell$ is a  multi-material cell).

The the discretization error $e_h = p - p_h$ is defined as:

\begin{equation*}
  \errlTwo{} =  \|e_h  \|_{\lTwoSpace} = \| P_h\,p - P_h\,p_h \|_{\LTwoSpace} = \| P_h\,p - p_h \|_{\LTwoSpace}
\end{equation*}
\noindent since~$P_h$ is linear and~$p_h \in \mathbb V_h$.  Then the discrete norm of the discretization error is computed as follows:
$$
\errlTwo{} = \left[\sum\limits_{\bcell \in \bmesh_h}\sum\limits_{\mcell\in\mmesh_h(\bcell)} \left(\frac{1}{|\mcell|}\int_{\mcell} p \,{\rm dx} - p_{\mcell}\right)^2|\mcell|\right]^2,
$$
where $|\mcell|$ is
the area of cell $\mcell$.

\subsection{Linear solution}

	\begin{figure}[h]
		\centering
		\begin{subfigure}{.41\linewidth}
			\centering
			\includegraphicsw{err2_asc0.png}
			\caption{$\vect K_1 \equiv \vect K_2 \equiv \vect I$}
			\label{fig:fake:2}
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.41\linewidth}
			\centering
			\includegraphicsw{err3_asc0.png}
			\caption{$\vect K_1 \equiv \vect K_2 \equiv \vect K_3 \equiv \vect I$}
			\label{fig:fake:3}
		\end{subfigure}
		\caption{Material distribution for pseudo-multi-material problem 2-materials(left), 3-materials(right) \label{fig:fake}}		
	\end{figure}

The first set of tests is designed to check the property of the method to accurately recover the solution that is the polynomial of degree~1. Let us consider the diffusion problem~\eqref{dual} with~$c \equiv f \equiv 0$,
$\partial\Omega_D = \partial\Omega$. The computational domain $\Omega=[0,1]^2$
is divided into several subdomains by nonintersecting straight lines.
In these settings the interface reconstruction algorithm MOF reconstructs
the interfaces exactly. To test the {\it linearity preservation} property,
 we set up a pseudo-multi-material problem with the diffusion tensor being the
 same in all subdomains, $\vect K_i = \vect I$ .
 The exact solution a linear function. The geometry of two cases under consideration is shown in Figure~
\ref{fig:fake}.

	We denote
        %the exact pressure solution by~$p$ and
        the solution computed  with the ASC($n$) method by~$p_{h,\,n}$, $n = 0, 1$.

        For ASC(0) we have~$\errlTwo{0} = 6.38 \times 10^{-2}$ and $6.41 \times 10^{-2}$ for the configurations shown in Figures~\ref{fig:fake:2} and~\ref{fig:fake:3}, respectively.
        That is, ASC(0) is not able to recover $P_1$ solutions exactly.

	Since ASC(1) approximates interface traces with $P_1$ functions
        it recovers edge-based degrees of freedom exactly in the sense of mean values. This results in exact reconstruction
        of cell-based unknowns and {\it linearity preservation} property for both examples, i.e.,
	\begin{equation*}
		\errlTwo{1} = \left\| p - p_{h,\,1} \right\|_{\lTwoSpace} = 0.
	\end{equation*}

	%% As we saw in previous section,
        In general, one may not expect concentration and flux convergence to be better than second order with respect to~$\lTwo$\,--\,error for ASC($1$).  However, taking the example above into account, one may expect that convergence of ASC(1) with respect to~$\lTwo$-norm is superior
        to  convergence properties of ASC(0).

        \subsection{Piecewise $P_1$ solution}

        In this set of tests, we consider the diffusion problem~\eqref{dual} with~$c = f = 0$, $\partial\Omega_D = \partial\Omega$,
        and two different materials in the domain.
        $\vect K = k\,\vect I$, $k = 1$ in the left part of the domain and $k = 0.1$ in the right (see Figure~\ref{fig:pwlin:mat}).
        The exact solution is piecewise linear such that the normal flux is continuous across the interface (see Figure~\ref{fig:pwlin:p}).

	\begin{figure}[h!]
		\centering
		\label{fig:pwlin}
		\begin{subfigure}{.44\linewidth}
			\centering
			\includegraphicsw{skew_ref.png}
			\caption{Reference solution~$p$}
			\label{fig:pwlin:p}
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.4\linewidth}
			\centering
			\includegraphicsw{skew_geometry_square.png}
			\caption{Materials: $k_1 = 1$, $k_2 = 0.1$}
			\label{fig:pwlin:mat}
		\end{subfigure}
		\caption{Piecewise linear reference solution}
	\end{figure}

	For this example we use a sequence of square base\,meshes~$\bmesh_i$, $i = 1, 2, 3, 4$; $h_i \coloneqq$ max diameter of the cell. We denote by
	\begin{equation*}
		\rho_{n,\,i} \coloneqq \frac{\log \errlTwo{n,\,i} / \errlTwo{n,\,i+1}}{\log h_i / h_{i+1}}
	\end{equation*}
the reduction rate order of ASC($n$) in ~$\lTwo$\,-\,norm between $i$ and $i+1$ refinement step. We also compute the $\ell^{\infty}$-norm of the error
	\begin{equation*}
		\errInf{n,\,i} \coloneqq \left\| p - p_{h_i,\,n} \right\|_\infty
	\end{equation*}
	for ASC($n$).

	\begin{table}[h!]\small
		\centering
		\caption{Piecewise linear example: convergence \label{fig:conv:pwlin}}
			\begin{tabular}[1.5]{| c | c || c | c || c |}
				\hline
				\multirow{5}{*}{\rotatebox{90}{ASC(0)}} & $h$ & $\errlTwo{0}$ & $\rho$ & $\errInf{0}$ \\
				\cline{2-5}
				& $3.5\times10^{-1}$ & $7.3\times10^{-1}$ & & 4.8 \\
				\cline{2-5}
				& $8.8\times10^{-2}$ & $1.6\times10^{-1}$ & 1.1 & 1.2 \\
				\cline{2-5}
				& $2.2\times10^{-2}$ & $3.7\times10^{-2}$ & 1.1 & $3.4\times10^{-1}$ \\
				\cline{2-5}
				& $5.5\times10^{-3}$ & $8.9\times10^{-3}$ & 1.0 & $7.9\times10^{-2}$ \\
				\hline
				\hline
				\multirow{5}{*}{\rotatebox{90}{ASC(1)}} & $h$ & $\errlTwo{1}$ & $\rho$ & $\errInf{1}$ \\
				\cline{2-5}
				& $3.5\times10^{-1}$ & $2.5\times10^{-2}$ & & $1.6\times10^{-1}$ \\
				\cline{2-5}
				& $8.8\times10^{-2}$ & $1.9\times10^{-3}$ & 1.84 & $6.3\times10^{-2}$ \\
				\cline{2-5}
				& $2.2\times10^{-2}$ & $1.6\times10^{-4}$ & 1.79 & $9.8\times10^{-3}$ \\
				\cline{2-5}
				& $5.5\times10^{-3}$ & $1.3\times10^{-5}$ & 1.80 & $4.0\times10^{-3}$ \\
				\hline
			\end{tabular}
	\end{table}

	Numerical results are shown in Table~\ref{fig:conv:pwlin}. We observe that ASC(0) converges linearly with respect to $\lTwo$-norm, and ASC(1) has the convergence rate close to quadratic with respect to the $\lTwo$-norm.

	\subsection{Piecewise $P_2$ solutions}

	\subsubsection{Two Materials}\label{sec:twomat}

	\begin{figure}[h]
		\begin{subfigure}{.45\linewidth}
			\centering
			\includegraphicsw{circle_ref_mesh.png}
			\caption{Reference solution~$p$}
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.45\linewidth}
			\centering
			\includegraphicsw{circle_ref_slice.png}
			\caption{$p(x,\frac{1}{2})$}
		\end{subfigure}
		\caption{Piecewise quadratic reference solution, 2 materials\label{fig:pwquad2}}
	\end{figure}

	Let us consider the diffusion problem~\eqref{dual} with~$c = 0$,
        $\partial\Omega_D = \partial\Omega$. The computational domain is divided into
        subdomains: $\Omega_1 = \{ {\bf x} : \|{\bf x} - {\bf x}_0\|< 0.25,~
        {\bf x}_0 = (0.5,0.5)\}$ and  $\Omega_2 = [0,1]^2 / \Omega_1$.
        The diffusion tensor is set  $\vect K_i = k_i\,\vect I$ in $\Omega_i$,
        $k_1 = 0.001$ and $k_2=1$. The exact solution is piecewise quadratic such
        that the normal flux is continuous across the interface (see Figure~\ref{fig:pwquad2}).
        For this problem, we compared convergence properties of the  ASC(0) and ASC(1) methods
        on a sequence of Voronoi meshes.

	\begin{table}[h!]\small
		\centering
		\caption{Piecewise quadratic example, two materials: convergence \label{tab:conv:pwquad2}}
		\begin{tabular}[1.5]{| c | c || c | c || c |}
		  \hline
		  \multirow{7}{*}{\rotatebox{90}{ASC(0)}} & $h$ & $\errlTwo{0}$ & ${\rho}$ & $\errInf{0}$ \\
		  \cline{2-5}
		  & $3.0\times10^{-1}$ & $2.4\times10^{-3}$ & & $6.3\times10^{-1}$ \\
		  \cline{2-5}
		  & $1.5\times10^{-1}$ & $6.5\times10^{-4}$ & 2.0 & $7.0\times10^{-3}$ \\
		  \cline{2-5}
		  & $8.1\times10^{-2}$ & $2.6\times10^{-4}$ & 1.4 & $3.2\times10^{-3}$ \\
		  \cline{2-5}
		  & $4.2\times10^{-2}$ & $1.4\times10^{-4}$ & 0.9 & $2.3\times10^{-3}$ \\
		  \cline{2-5}
		  & $2.1\times10^{-2}$ & $3.7\times10^{-5}$ & 1.9 & $1.1\times10^{-3}$ \\
		  \cline{2-5}
		  & $1.0\times10^{-2}$ & $2.7\times10^{-5}$ & 0.4 & $8.6\times10^{-4}$ \\
		  \hline
		  \hline
		  \multirow{7}{*}{\rotatebox{90}{ASC(1)}} & $h$ & $\errlTwo{1}$ & ${\rho}$ & $\errInf{1}$ \\
		  \cline{2-5}
		  & $3.0\times10^{-1}$ & $2.4\times10^{-3}$ & & $2.1\times10^{-3}$ \\
		  \cline{2-5}
		  & {$1.5\times10^{-1}$} & $7.0\times10^{-4}$ & 1.9 & {$1.3\times10^{-2}$} \\
		  \cline{2-5}
		  & $8.1\times10^{-2}$ & $2.3\times10^{-4}$ & 1.8 & $6.8\times10^{-4}$ \\
		  \cline{2-5}
		  & $4.2\times10^{-2}$ & $6.8\times10^{-5}$ & 1.8 & $3.2\times10^{-4}$ \\
		  \cline{2-5}
		  & $2.1\times10^{-2}$ & $2.0\times10^{-5}$ & 1.8 & $1.1\times10^{-4}$ \\
		  \cline{2-5}
		  & $1.0\times10^{-2}$ & $5.4\times10^{-6}$ & 1.9 & $3.3\times10^{-5}$ \\
		  \hline
		\end{tabular}
	\end{table}

	The norms of the errors are shown in Table~\ref{tab:conv:pwquad2}.        	
 ASC(1) demonstrates  convergence with the  rate in the $\lTwo$-norm close to quadratic.  ASC(0) convergence rate  fluctuates significantly.

        We also observe a bump in the max norm error for ASC(1) on the second mesh level,
        $h = 1.5\times10^{-1}$. To have some insight, we show the corresponding mesh in the Figure~\ref{fig:conv:pwquad2:inf:mesh}.
        One may note that the interface reconstruction produces significant discontinuity of
        interfaces: A small volume of the external material, i.e. the one occupying $\Omega_2$ domain, appears
        inside the disk, domain $\Omega_1$. Due to constant trace approximation, ASC(0)
        is not sensitive to such  irregularity. It turns out that for  ASC(1) the $\ell^\infty$ norm of the error is affected by  the appearance of such small isolated cut cells. At the same time, this  %as expected,
        does not affect the $\lTwo$-convergence of ASC(1).

        \begin{figure}
		\centering
		\label{fig:conv:pwquad2:inf}
		\begin{subfigure}{.29\linewidth}
			\centering
			\includegraphicsw{circle_voronoi_2_mat.png}
			\caption{Materials}
			\label{fig:conv:pwquad2:inf:mesh}
		\end{subfigure}%
\hskip1ex
		\begin{subfigure}{.33\linewidth}
			\centering
			\includegraphicsw{circle_voronoi_2_asc0.png}
			\caption{ASC(0), $p_h$}
		\end{subfigure}%
\hskip1ex
		\begin{subfigure}{.33\linewidth}
			\centering
			\includegraphicsw{circle_voronoi_2_asc1.png}
			\caption{ASC(1), $p_h$}			
		\end{subfigure}%
\caption{Piecewise quadratic example, two materials: $h = 1.5\times10^{-1}$. This figure illustrates the appearance of small isolated material volumes during numerical reconstruction of material interfaces. This may affect the $\ell^\infty$ error norm of the ASC(1).}
	\end{figure}

%	\clearpage

	\subsubsection{Three Materials}\label{sec:threemat}

	\begin{figure}[h]
		\centering
		\begin{subfigure}{.45\linewidth}
			\centering
			\includegraphicsw{ring_ref_mesh.png}
			\caption{Reference solution~$p$}
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.45\linewidth}
			\centering
			\includegraphicsw{ring_ref_slice.png}
			\caption{$p(x,\frac{1}{2})$}
		\end{subfigure}
\caption{Piecewise quadratic reference solution, three materials \label{fig:pwquad3}}
	\end{figure}

	In the next group of numerical tests, we consider the same  diffusion problem~\eqref{dual}
        with~$c = 0$, $\partial\Omega_D = \partial\Omega$. The computational domain is now
        divided into three subdomains: $\Omega_1 = \{{\bf x} : \|{\bf x} - {\bf x}_0\| < 0.2$,
        $\Omega_2 = \{{\bf x} : 0.2 \le \|{\bf x} - {\bf x}_0\| < 0.25$, and
        $\Omega_3 = [0,1]^2 / (\Omega_1\cup\Omega_2)$. The diffusion tensor is set to be
        $\vect K_i = k_i\,\vect I$, $k_{1} = k_{3} = 1$, $k_2 = 0.001$.
        The geometry represents a ring with $k_2=0.001$ inside the ring and $k_{1} = k_{3} = 1$ outside
        the ring. The exact solution is piecewise quadratic such that the normal flux is
        continuous across the interface; see Figure~\ref{fig:pwquad3}.
        We use a sequence of triangular meshes to study convergence for this example. In this set of tests, we also consider the numerical method based on homogenization techniques for the comparison. The homogenization method we use is from \cite{dawes2013solving}. The homogenized values of the diffusion tensor are computed on the base cells $\bcell$ and then plugged into the MFD discretization applied on the  base mesh $\bmesh_h$; see \cite{kikinzon2017approximate} for implementation details of this method.

        	\begin{table}[h]
	  \centering
	  \caption{Piecewise quadratic example, three materials: error norms and convergence rates\label{fig:conv:pwquad3}}
	  \footnotesize
	  \begin{tabular}[1.1]{| c | c || c | c || c |}
	    \hline
	    \multirow{7}{*}{\rotatebox{90}{ASC(0)}} & $h$ & $\errlTwo{0}$ & $\rho$ & $\errInf{0}$ \\
	    \cline{2-5}
	    & $3.0\times10^{-1}$ & 4.5 & & 17 \\
	    \cline{2-5}
	    & $2.5\times10^{-1}$ & 4.5 & & 17 \\
	    \cline{2-5}
	    & $1.3\times10^{-1}$ & 4.0 & & 17 \\
	    \cline{2-5}
	    & $8.3\times10^{-2}$ & 4.4 & & 17 \\
	    \cline{2-5}
	    & {$6.7\times10^{-2}$} & $7.1\times10^{-1}$ & & 4.9 \\
	    \cline{2-5}
	    & $4.3\times10^{-2}$ & $4.5\times10^{-1}$ & 1.2 & 5.0 \\
	    \hline
	    \hline
	    \multirow{7}{*}{\rotatebox{90}{ASC(1)}} & $h$ & $\errlTwo{0}$ & $\rho$ & $\errInf{0}$ \\
	    \cline{2-5}
	    & $3.0\times10^{-1}$ & $4.5\times10^{-1}$ & & 3.5 \\
	    \cline{2-5}
	    & $2.5\times10^{-1}$ & $2.6\times10^{-1}$ & 3 & 2.7 \\
	    \cline{2-5}
	    & $1.3\times10^{-1}$ & $9.2\times10^{-2}$ & 1.5 & $6.2\times10^{-1}$ \\
	    \cline{2-5}
	    & $8.3\times10^{-2}$ & $4.8\times10^{-2}$ & 1.6 & $8.3\times10^{-1}$ \\
	    \cline{2-5}
	    & $6.7\times10^{-2}$ & $2.8\times10^{-2}$ & 2.5 & $2.3\times10^{-1}$ \\
	    \cline{2-5}
	    & $4.3\times10^{-2}$ & $1.0\times10^{-2}$ & 2.3 & $6.3\times10^{-2}$ \\
	    \hline
	  \end{tabular}	
	  \centering
	  \begin{tabular}[1.1]{c | c | c || c | c || c |}
	    \cline{2-6}
	    \multirow{14}{*}{\rotatebox{90}{Homogenization}} & \multirow{7}{*}{\rotatebox{90}{Arithmetic}} & $h$ & $\errlTwo{\text{AH}}$ & $\rho$ & $\errInf{\text{AH}}$ \\
	    \cline{3-6}
	    & & $3.0\times10^{-1}$ & 4.9 & & 17 \\
	    \cline{3-6}
	    & & $2.5\times10^{-1}$ & 5.0 & & 17 \\
	    \cline{3-6}
	    & & $1.3\times10^{-1}$ & 4.9 & & 17 \\
	    \cline{3-6}
	    & & $8.3\times10^{-2}$ & 4.7 & & 17 \\
	    \cline{3-6}
	    & & {$6.7\times10^{-2}$} & 4.4 & & 16 \\
	    \cline{3-6}
	    & & $4.3\times10^{-2}$ & $9.7\times10^{-1}$ & 3.5 & 5.7 \\
	    \hhline{~=====}
	    & \multirow{7}{*}{\rotatebox{90}{Harmonic}} & $h$ & $\errlTwo{\text{HH}}$ & $\rho$ & $\errInf{\text{HH}}$ \\
	    \cline{3-6}
	    & & $3.0\times10^{-1}$ & 2.3 & & 15 \\
	    \cline{3-6}
	    & & $2.5\times10^{-1}$ & 1.7 & 1.6 & 16 \\
	    \cline{3-6}
	    & & $1.3\times10^{-1}$ & $7.3\times10^{-1}$ & 1.2 & 12 \\
	    \cline{3-6}
	    & & $8.3\times10^{-2}$ & $4.8\times10^{-1}$ & 1.0 & 12 \\
	    \cline{3-6}
	    & & $6.7\times10^{-2}$ & $3.4\times10^{-1}$ & 1.6 & 9.4 \\
	    \cline{3-6}
	    & & $4.3\times10^{-2}$ & $1.6\times10^{-1}$ & 1.7 & 8.2 \\
	    \cline{2-6}
	  \end{tabular}

	\end{table}

	Numerical results are shown in Table~\ref{fig:conv:pwquad3}.
        We compare ASC(0), ASC(1), arithmetic, and harmonic homogenization.
        Note that up to mesh level~$h = 8.3\times10^{-2}$ base\,
        faces with three materials are present, and starting from %
        {$h = 6.7\times10^{-2}$} the meshes are fine
        enough so that only   macro-faces sharing one or two materials occur.

	We see that ASC(0) starts to converge linearly with respect to $\lTwo$-error
        once~$h < 6.7\times10^{-2}$. ASC(1) demonstrates a robust behaviour and shows the convergence
        rate close to quadratic with respect to $\lTwo$-error as in previous examples,
        and performs better than homogenization approaches.

\subsection{Algebraic robustness}
%
%	One may expect that the conditioning of the ASC($n$) system~\eqref{asc_system} gets worse as one increases~$n$. In fact, we have the following result.\\
%	\begin{theorem}\label{thm:eig}
%		Let~$\mu_{\text{min}}^n > 0$ be the minimal eigenvalue of the system matrix~$\vect S_\bmesh$ in~\eqref{asc_system} of the ASC($n$) method. Then we have
%		\begin{equation}\label{mineig}
%			\mu_{\text{min}}^1 < \mu_{\text{min}}^0.
%		\end{equation}
%	\end{theorem}
%	\begin{proof}
%		\Sasha{We have it. To be added.}
%	\end{proof}
%
%	\Sasha{We also believe that the max eig value stays the same (based on num experiments), i.e. $\mu_{\text{max}}^1 \approx \mu_{\text{max}}^0$ or even $\mu_{\text{max}}^1 = \mu_{\text{max}}^0$}. I think it would be nice to prove it here, so we can show that the cond number is governed by the smallest eig value alone.
%

	In this section, we study the dependence of the condition number of matrix $S_\bmesh$ on the position of the material interface against the background mesh.
 For this purpose, we solve the diffusion problem~\eqref{dual} in the unit square with $\partial\Omega = \partial\Omega_D$, $\vect K = k\,\vect I$, $k = 1$ on the left part and $k = 0.1$ on the right. We keep the mesh fixed, and change the position of the interface so that the minimal length of mini-faces~$w$ gets smaller, $w = 10^{-1}, 10^{-2}, \dots, 10^{-5}$ (see Figure~\ref{fig:w}).

	\begin{figure}[h]
		\centering
		\caption{Distribution of materials leads to  different values of the minimal length of mini-faces $w$ \label{fig:w}}
		\begin{subfigure}{.33\linewidth}
			\centering
			\includegraphicsw{skew1.png}
			\caption{$w = .1$}
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.33\linewidth}
			\centering
			\includegraphicsw{skew01.png}
			\caption{$w = .01$}
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.33\linewidth}
			\centering
			\includegraphicsw{skew001.png}
			\caption{$w = .001$}
		\end{subfigure}
	\end{figure}

	\begin{table}[h]
		\centering
		\caption{Condition numbers of ASC(0)\,/\,ASC(1) system matrices~\eqref{asc_system} \label{fig:w:res}}
			\begin{tabular}[1.2]{ | c | c | c | c |}
				\hline
				$w$ & $\kappa_{\text{ASC(0)}}$ & $\kappa_{\text{ASC(1)}}$ & $\widetilde\kappa_{\text{ASC(1)}}$\\
				\hline
				$10^{-1}$ & 41.0 & 1\,730       & 41.0  \\
				\hline
				$10^{-2}$ & 45.2 & 2\,817       & 45.1  \\
				\hline
				$10^{-3}$ & 48.3 & 16\,391      & 48.3   \\
				\hline
				$10^{-4}$ & 49.0 & 152\,325     & 49.0    \\
				\hline
				$10^{-5}$ & 49.1 & $1.5\times10^6$&49.1  \\
				\hline
			\end{tabular}
	%	\hfill
%		\begin{subfigure}{.55\linewidth}
%			\centering
%			\includegraphicsw{logplot.png}
%		\end{subfigure}
	\end{table}

	Numerical results are shown in Table~\ref{fig:w:res}. We observe that the condition number~$\kappa_{\text{ASC(0)}}$ of $S_\bmesh$ for ASC(0) levels off if $w$ gets smaller. The condition number~$\kappa_{\text{ASC(1)}}$ of ASC(1) depends on $w$ and behaves as $O(w^{-1})$ for $w\to0$. A closer look at the spectrum of      $S_\bmesh$  reveals that the growth of the condition
number for    ASC(1) is due to presence of only few (three for this example) small eigenvalues, which tend to zero. To illustrate this, Table~\ref{fig:w:res} shows the ``effective'' condition number of $S_\bmesh$ that is defines
as
	$$
		\widetilde{\vect\kappa}_{\text{ASC(1)}} = {\mu_{\text{max}}}/{\mu_3}
	$$
	where  $\mu_{\text{min}}^1 = \mu_0 \ge \mu_1 \ge \dots \ge \mu_{\text{max}}$ are the eigenvalues of~$\vect S_\bmesh$ of ASC(1). From this results we see that the effective condition number of ASC(1) stays bounded with respect to the interface position and is  close to the condition number of ASC(0). We hypothesize that the number of outliers in the  spectrum of $\vect S_\bmesh$ is proportional to the number of multi-material cells with small cuts.

	It is well-known that the presence of a few outliers in the spectrum does not affect the asymptotic convergence of the conjugate gradient (CG) iterative methods, see, e.g., \cite{olshanskii2014iterative}. Indeed, in our experiments the CG method was found to be equally effective for solving systems of algebraic equations resulting from ASC(0) and ASC(1).
%Starting from some iteration CG method behaves like extreme eigenvalues are not present in the spectrum.
%That is, several small eigenvalues with no clustering is not an obstacle neither for the optimal convergence rate of Krylov solvers, nor for the~$\LTwo$-convergence of the discrete solution.

 	\subsection{Unsteady problem}

	We finally apply the ASC methods to simulate the time dependent diffusion problem.  In the mixed form, the problem reads
	\begin{equation}\label{dual_transient}
		\left\{\begin{split}
			\vect K^{-1}\,\vect u &+ \nabla\,p\,&= 0&\quad\text{in } \Omega , \\
			\nabla\cdot\vect u    &+ \frac{\partial}{\partial t}\,p       &= f&\quad\text{in } \Omega,
		\end{split}\right.
\end{equation}
for   $t\in(0, T]$ with initial data $p(\vect x, 0) = p_0(\vect x)$ and
boundary data as in \eqref{dual:bc:neumann}. After discretizing in time by the implicit Euler method, the problem takes the form \eqref{dual}--\eqref{dual:bc:neumann} with $c=|\Delta t|^{-1}$ and we apply the spacial discretization described in section~\ref{sec:ASC}. For the purpose of comparison, we apply   arithmetic and harmonic homogenization methods followed by a MFD discretization.

%We use the implicit Euler method to discretize~\eqref{dual_transient} in time. This leads to a sequence of problems~\eqref{dual} with nonzero source term~$f$. For the space discretization we use ASC(0), ASC(1), arithmetic, and harmonic homogenization methods.

%		\begin{equation}
%			p = g_D \quad\text{on } \partial\Omega_D,\qquad %\label{dual:bc:dirichlet} \\
%			\vect u \cdot {\vect n} = g_N \quad\text{on } \partial\Omega_N, \label{dual_transient:bc:neumann}
%		\end{equation}
%%
%	\begin{subequations}\label{dual_transient}
%		\begin{empheq}[left = \empheqlbrace]{alignat=2}
%		\vect K^{-1}\,\vect u &+ \nabla\,p                              &= 0,\\
%		\nabla\cdot\vect u    &+ \frac{\partial}{\partial t}\,p\:       &= f
%		\end{empheq}
%		\text{posed in $\Omega \times (0, T]$ with initial data}
%		\begin{equation}\label{dual_transient:ic}
%		p(\vect x, 0) = p_0(\vect x)
%		\end{equation}
%		\text{and boundary data}
%		\begin{align}
%		p &= g_D \quad\text{on } \partial\Omega_D, \label{dual_transient:bc:dirichlet} \\
%		\vect u \cdot \hat{\vect n} &= g_N \quad\text{on } \partial\Omega_N. \label{dual_transient:bc:neumann}
%		\end{align}
%	\end{subequations}

The computational domain is the same as in section~\ref{sec:threemat} with the example of three different materials. $\Omega = \Omega_1 \cup \Omega_2 \cup \Omega_3$ is divided into three subdomains: $\Omega_1 = \{\vect x \in \Rn{2} : \|{\bf x} - {\bf x}_0\| \ge 0.2\}$,
	$\Omega_2 = \{\vect x \in \Rn{2} : 0.15 \le \|{\bf x} - {\bf x}_0\| \le 0.2\}$, $\vect x_0 = (0.5, 0.5)$, and $\Omega_3 = (0,1)^2 \setminus (\Omega_1\cup\Omega_2)$. The diffusion tensor is set as $\vect K_i = k_i\,\vect I$, $k_1 = 1, k_2 = 0.002$, and $k_3 = 10$.

	We prescribe Dirichlet boundary data $g_D = 1$ on the left side of the unit square, while right, top, and bottom sides are prescribed no-flux boundary condition,  $g_N \equiv 0$. The external source term is zero, $f= 0$. The initial concentration is set to be
	\begin{equation*}
		p_0(\vect x) = (1 - \vect x)^{10}.	
	\end{equation*}
The equilibrium state for $t\to\infty$ is obviously $p \equiv 1$. In our computations, we set the final time~$T = 5$.

	\begin{figure}[h]
		\centering
		\begin{subfigure}{.4\linewidth}
			\centering
			\includegraphicsw{transient2/supermesh.png}
			\caption{Conforming (super)mesh of~$\Omega$}
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.58\linewidth}
			\centering
			\includegraphicsw{transient2/ref_slices.png}
			\caption{Cuts~$p_*\left((x,0.5), t\right)$ of the reference solution}	
		\end{subfigure}%
\caption{Triangulation of~$\Omega$ used to obtain the reference solution and cuts of the reference solution for~$t \in \{0.13, 0.25, \dots, 5\}$ \label{fig:transient:ref}}
	\end{figure}

	We first compute solution $p_*$ to the problem~(\ref{dual_transient}) using $P2$ finite element method on sufficiently fine mesh consisting of  4\,908 triangles. This mesh is illustrated in Figure~\ref{fig:transient:ref} (left). The reference mesh is consistent with material interfaces so it consists only of single-material cells. Time step~$\Delta t$ is chosen as~$T / 40$. This solution was found to be (almost) mesh independent and will serve as the  reference solution. The center cutline profiles ~$p_*\left((x,0.5), t\right)$   are shown in the Figure~\ref{fig:transient:ref} (right) for several values of~$t \in (0, T]$.

	  For ASC(0), ASC(1), arithmetic and harmonic homogenization methods we use two Voronoi meshes with~$h = 1.5 \times 10^{-1}$ (124 base\,cells) and $h = 8.1 \times 10^{-2}$ (465 base\,cells).
          The coarse mesh contains 20 multi-material cells and two macro-face sharing three materials. The fine mesh contains 50 multi-material cells and no three material macro-faces. For all these methods we use 20 time frames, $\Delta t = T / 20$. Results are shown in Figures~\ref{fig:transient:comp}\,--\,\ref{fig:transient:err}.

	\begin{figure}[h]
		\centering
		\begin{subfigure}{.3\linewidth}
			\centering
			\includegraphicsw{transient2/movie_frames/ref/frame_1s34.png}
			\caption{Reference}
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.3\linewidth}
			\centering
			\includegraphicsw{transient2.1/movie_frames/arithmetic_homo/frame_1s43.png}
			\caption{Arithmetic homo.}	
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.3\linewidth}
			\centering
			\includegraphicsw{transient2.1/movie_frames/harmonic_homo/frame_1s43.png}
			\caption{Harmonic homo.}	
		\end{subfigure}%
		\par
		\begin{subfigure}{.3\linewidth}
			\centering
			\includegraphicsw{transient2.1/movie_frames/asc0/frame_1s43.png}
			\caption{ASC(0)}
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.3\linewidth}
			\centering
			\includegraphicsw{transient2.1/movie_frames/asc1/frame_1s43.png}
			\caption{ASC(1)}	
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.3\linewidth}
			\centering
			\includegraphicsw{transient2.1/movie_frames/asc_diff/frame_1s43.png}
			\caption{ASC(0,\,1) difference}	
		\end{subfigure}%
\caption{Comparison of the discrete solutions~$p_h$ for~$h = 1.5 \times 10^{-1}$, $t = 1.25$. \label{fig:transient:comp}}
	\end{figure}

	%% \begin{figure}[h]
	%% 	\centering
	%% 	\begin{subfigure}{.45\linewidth}
	%% 		\centering
	%% 		\includegraphicsw{transient2.1/movie_slices_frames/frame_0s25.png}
	%% 		\caption{Coarse mesh, $t = 0.25$}
	%% 	\end{subfigure}%
	%% 	\hfill
	%% 	\begin{subfigure}{.45\linewidth}
	%% 		\centering
	%% 		\includegraphicsw{transient2.1/movie_slices_frames/frame_1s50.png}
	%% 		\caption{Coarse mesh, $t = 1.50$}	
	%% 	\end{subfigure}%
	%% 	\par
	%% 	\begin{subfigure}{.45\linewidth}
	%% 		\centering
	%% 		\includegraphicsw{transient2/movie_slices_frames/frame_0s25.png}
	%% 		\caption{Fine mesh, $t = 0.25$}
	%% 	\end{subfigure}%
	%% 	\hfill
	%% 	\begin{subfigure}{.45\linewidth}
	%% 		\centering
	%% 		\includegraphicsw{transient2/movie_slices_frames/frame_1s50.png}
	%% 		\caption{Fine mesh, $t = 1.50$}	
	%% 	\end{subfigure}%
	%% 	\caption{Comparison of the cuts~$p_h((x,0.5), t)$ of discrete solutions for coarse and fine meshes, $h = 1.5 \times 10^{-1}$ and $h = 8.1 \times 10^{-2}$. 		\label{fig:transient:cuts}}
	%% \end{figure}

	\begin{figure}[h]
		\centering
		\begin{subfigure}{.8\linewidth}
			\centering
			\includegraphicsw{transient2.1/l2err.png}
			\caption{Coarse mesh}
		\end{subfigure}%
		\par
		\begin{subfigure}{.8\linewidth}
			\centering
			\includegraphicsw{transient2/l2err.png}
			\caption{Fine mesh}	
		\end{subfigure}%
		\caption{$\lTwo$-norm of the error computed for the inclusion~$\Omega_2 \cup \Omega_3$ for coarse and fine meshes, $h = 1.5 \times 10^{-1}$ and $h = 8.1 \times 10^{-2}$. \label{fig:transient:err}}
	\end{figure}

	From the figures it is easy to appreciate  that among all the methods only  ASC(1)  provides a reasonable approximation for the coarse mesh, cf. Figures~\ref{fig:transient:comp}.
        %and~\ref{fig:transient:cuts}
        Numerical solution computed with ASC(0)  overestimates incoming fluxes  for the ring.  This solution converges to the equilibrium state~$p_h \approx 1$ at approximately $t = 3.75$, which is significantly earlier than the time when same state is achieved by the reference solution  for the same coarse mesh. Note that the coarse mesh contains faces with three materials, and we saw already that ASC(0) may fail to converge for this case even for stationary examples\footnotemark{}.
	%
	Arithmetic homogenization performs poorly for both mesh levels (even finer mesh near the inclusions is required to provide reasonably accurate solution). Harmonic homogenization shows reasonable results only for the fine mesh.

        In Figure \ref{fig:transient:err} we present the $\lTwo$-norm of the error $p_* - p_h$ computed for the inclusion~$\Omega_2 \cup \Omega_3$ as a function of time.
        Since all numerical solutions eventually converge to the same steady state,  numerical errors for any method decrease for large enough time.
        On earlier stages ASC(1) outperforms all methods on the coarse mesh and provides comparable results with ASC(0) scheme and the harmonic homogenization approach
        on the fine mesh.

	\footnotetext{
		We tried replacing Voronoi mesh with a triangulation such that the number of triangles is close to the number of the polygonal cells in the fine Voronoi mesh (456 elements for the triangular mesh v.s. 465 for the Voronoi mesh); the achieved difference is that the triangular mesh has faces with three materials, and Voronoi mesh does not. Nevertheless, ASC(0) performed poorly for this example converging to the steady-state at approximately $t = 3$.
	}

### 2018-11-26 asc.tex
Refactor theoretical part

@@
 \usepackage{amsthm} % proofs
+\usepackage{stmaryrd} % llbracket for jumps
 % bold for everything
@@
 % lowercase mathcal font
-%\usepackage{dutchcal}
+\usepackage{dutchcal}
 
@@
 \newcommand{\mmesh}{{\vect{\mathcal \tau}}}
+\newcommand{\bface}{F}
 \newcommand{\bfaces}[1][]{{\vect{\mathcal F}_{\text{#1}}}}
-\newcommand{\mfaces}[1][]{{\vect{ f}_{\text{#1}}}}
+\newcommand{\mface}{f}
+\newcommand{\mfaces}[1][]{{\vect{\mathcal f}_{\text{#1}}}}
 
@@
 \newcommand{\HDivSpace}[1][\Omega]{{\mathbb H_\text{div}\left({#1}\right)}}
+\newcommand{\HDivNodeSpace}[1][\Omega]{{\mathbb H_\text{div,\,0}\left({#1}\right)}}
+\newcommand{\HHalfSpace}[1][\bface]{{\mathbb H^{\frac{1}{2}}\left({#1}\right)}}
 \newcommand{\PnSpace}[2]{{\mathbb P^{#1}\left({#2}\right)}}
@@
 \newcommand{\Sasha}[1]{\colorbox{Cyan}{\textbf{Sasha}:} #1}
+\newcommand{\toDiscuss}[1]{\colorbox{Cyan}{\textbf{\,!\,}:} #1}
 
@@
 
+%\let\oldarray\array
+%\renewcommand{\array}[1][2pt]{\arraycolsep=#1\def\arraystretch{1.5}\oldarray}
+
 \begin{abstract}
@@
 The method allows for a general polygonal mesh which is unfitted to the material interfaces.
-Moreover, the interfaces can be discontinuous across the mesh edges as typical for numerical reconstructions using the volume or moments of fluid methods.
+Moreover, the interfaces can be discontinuous across the mesh edges as typical for numerical reconstructions using the volume or moment-of-fluid methods.
 We apply a mimetic finite difference method to solve local diffusion problems and use $P_1$ (mortar) edge elements to couple local problems into the global system.
@@
 This includes immersed boundary method \cite{peskin2002immersed}, level-set method \cite{sethian1999level}, and unfitted finite element methods \cite{belytschko2009review,burman2015cutfem}, to name several popular numerical approaches.
- The present study is motivated by the successful applications of the volume of fluid (VOF)~\cite{hirt1981volume} and the moment of fluids (MOF) methods~\cite{ahn2009adaptive} for the numerical  reconstruction of time-dependent interfaces.
+ The present study is motivated by the successful applications of the volume-of-fluid (VOF)~\cite{hirt1981volume} and the moment-of-fluid (MOF) methods~\cite{ahn2009adaptive} for the numerical  reconstruction of time-dependent interfaces.
 Both  methods do not require a mesh aligned with the  interfaces and reconstruct them from the information about the volumes of materials in each cell.
@@
 In this report, we devise  a higher order method for the numerical solution of the diffusion problem with discontinuous  coefficients on a general polyhedral mesh, which does not respect the position of multi-material interfaces.
-The method builds upon the approximate static condensation (ASC) algorithm first  proposed in ~\cite{kikinzon2017approximate}; it admits high-contrast diffusion coefficients and discontinuous reconstruction of the interfaces as typical for the volume/moment of fluid method.
+The method builds upon the approximate static condensation (ASC) algorithm first  proposed in ~\cite{kikinzon2017approximate}; it admits high-contrast diffusion coefficients and discontinuous reconstruction of the interfaces as typical for the volume/moment-of-fluid method.
 The ASC approach uses the formulation of the interface diffusion problem as a system of local inter-cell problems  coupled through the concentration values and fluxes on the cell faces.
@@
 Following~\cite{kikinzon2017approximate}, we apply the mimetic finite difference (MFD) method from~\cite{lipnikov2014mimetic} to approximate the local diffusion problems on this fine fitted mesh.
-After eliminating inter-cell degrees of freedom, one obtains a system of linear algebraic equations for the face concentration degrees of freedom.
+After eliminating inter-cell degrees of freedom (d.o.f.), one obtains a system of linear algebraic equations for the face concentration degrees of freedom.
 The fluxes and inter-element degrees of freedom are recovered by simple postprocessing.
@@
 \section{Model problem and macro-mesh decomposition} \label{sec:model}
+
 In a polygonal bounded domain $\Omega \subset \Rn{2}$  we consider the following diffusion problem in the mixed form
 \begin{equation}\label{dual}
-		\left\{\begin{split}
-			\vect K^{-1}\,\vect u &+ \nabla\,p\,&= 0&\quad\text{in } \Omega , \\
-			\nabla\cdot\vect u    &+ c\,p       &= f&\quad\text{in } \Omega,
-		\end{split}\right.
+	\arraycolsep=2pt\def\arraystretch{1.5}
+	\left\{\begin{array}{rcrccl}
+		\vect K^{-1}\,\vect u & + & \nabla\,p & = & 0 &\quad\text{in } \Omega , \\
+		\nabla\cdot\vect u    & + & c\,p      & = & f &\quad\text{in } \Omega
+		\end{array}\right.
 \end{equation}
@@
 	p = g_D \quad\text{on } \partial\Omega_D,\qquad %\label{dual:bc:dirichlet} \\
-			\vect u \cdot {\vect n} = g_N \quad\text{on } \partial\Omega_N. \label{dual:bc:neumann}
+	\vect u \cdot \hat{\vect n} = g_N \quad\text{on } \partial\Omega_N. \label{dual:bc}
 \end{equation}
-Here $p$ is a concentration and $\vect u$ is the diffusive flux, $\vect K$ is the positive definite  symmetric diffusivity tensor, which we assume constant within each material subdomain, $c\ge0$ is the reaction coefficient, $\vect n$ is the outward normal vector to $\partial\Omega$, $g_D$ and $g_N$ are Dirichlet and Neumann boundary data, respectively.
-In the context of fluid flows in porous media, \eqref{dual}--\eqref{dual:bc:neumann} is also known as the Darcy problem.
-In this case, $p$ has the meaning of pressure, $\vect u$ is fluid velocity and $\vect K$ is the permeability tensor.
+Here $p$ is a concentration and $\vect u$ is the diffusive flux, $\vect K$ is the positive definite  symmetric diffusivity tensor, which we assume constant within each material subdomain, $c\ge0$ is the reaction coefficient, $\hat{\vect n}$ is the outward normal vector to $\partial\Omega$, $g_D$ and $g_N$ are Dirichlet and Neumann boundary data, respectively.
+In the context of fluid flows in porous media, \eqref{dual}--\eqref{dual:bc} is also known as the Darcy problem.
+In this case, $p$ has the meaning of pressure, $\vect u$ is fluid velocity, and $\vect K$ is the permeability tensor.
 
@@
 	\centering
-		\caption{The figure illustrates global unstructured polyhedral mesh (left); Physical interfaces for three materials and cut cells, i.e.
-multi-material cells (central); The piecewise-planar discontinuous reconstruction of the interfaces by the moment of fluid method (right).
-Everything is shown for two refinement level of the base mesh.
-\label{fig:problem_geometry}}
 	\begin{subfigure}{.33\linewidth}
@@
 	\end{subfigure}
+	\caption{The figure illustrates global unstructured polyhedral mesh (left); Physical interfaces for three materials and cut cells, i.e.
+multi-material cells (central); The piecewise-planar discontinuous reconstruction of the interfaces by the moment-of-fluid method (right).
+Everything is shown for two refinement level of the base mesh.
+\label{fig:problem_geometry}}
 \end{figure}
@@
 surfaces where $\vect K$ may experience discontinuities, may cut through the macro-mesh in an arbitrary way; see Figure~\ref{fig:problem_geometry} (center).
-The polygonal cells ${\bcell \in \bmesh}$ cut by the interfaces are further called Multi-Material Cells (MMC).
+The polygonal cells ${\bcell \in \bmesh}$ cut by the interfaces are further called Multi-Material Cells (MMCs).
 In practice,  we are given a reconstructed interface by a volume-of-fluid or moment-of-fluid method.
@@
 Denote by $\bfaces$ the collection of all faces of the macro-mesh $\bmesh$.
-We shall distinct between the subset of internal and external faces,  $\bfaces = \bfaces[int] \cup \bfaces[ext]$\footnote{For the sake of  notation, we shall use  ~$\bfaces$ to denote both the set of elements and the corresponding domain formed by their union~$\cup_{F\in \bfaces} \bar{F}$; same for $\bfaces[int]$, $\bfaces[ext]$ and other collections of mesh elements introduced later in the text.
-The meaning should be clear from a context}.
-Introducing the new unknown $\lambda\in H^{\frac12}(\bfaces)$, we reformulate \eqref{dual}--\eqref{dual:bc:neumann} as a system of local problems coupled through the boundary data
+We shall distinct between the subset of internal and external faces,  $\bfaces = \bfaces[int] \cup \bfaces[ext]$\footnote{For the sake of  notation, we shall use~$\bfaces$ to denote both the set of elements and the corresponding domain formed by their union~$\cup_{F\in \bfaces} \bar{F}$; same for $\bfaces[int]$, $\bfaces[ext]$ and other collections of mesh elements introduced later in the text.
+The meaning should be clear from a context.}.
+Introducing the new unknown \toDiscuss{$\lambda \in \HHalfSpace[\bfaces]$}, we reformulate \eqref{dual}--\eqref{dual:bc} as a system of local problems coupled through the boundary data
 and flux continuity condition:
- 	\begin{eqnarray}\label{dual_mini}
-		%\begin{empheq}[left = \empheqlbrace]{alignat=2}
-\left\{
-\begin{split}
-			\vect K^{-1}\,\vect u &+ \nabla\,p\,    &= 0       &\quad\text{in } \bcell, \\
-			\nabla\cdot\vect u    &+ c\,p           &= f       &\quad\text{in } \bcell, \\
-			                      &\phantom{+cc\,}p &= \lambda &\quad\text{on } \partial\bcell, %\label{dual_mini:trace}
-		%\end{empheq}
-\end{split}
-\right.&
-\qquad \forall~\bcell\in\bmesh,\\
-        \left[\vect u\cdot\hat{\vect n}\right]=0\quad\text{on } F& \qquad \forall~F\in\bfaces[int]  \label{flux_cond}
+\begin{eqnarray}
+	\arraycolsep=2pt\def\arraystretch{1.5}
+	\left\{\begin{array}{rcrccl}
+		\vect K^{-1}\,\vect u                    & + & \nabla\,p & = & 0       &\quad\text{in } \bcell, \\
+		\nabla\cdot\vect u                       & + & c\,p      & = & f       &\quad\text{in } \bcell, \\
+		                                         &   & p         & = & \lambda &\quad\text{on } \partial\bcell, %\label{dual_mini:trace}
+	\end{array}\right. 
+	& \qquad \forall~\bcell\in\bmesh, \label{dual_mini} \\
+	\llbracket\vect u \cdot \hat{\vect n}\rrbracket = 0\quad\:\:\text{on } F,\:\:\:\:
+	& \qquad\quad \forall~F\in\bfaces[int]. \label{flux_cond}
 \end{eqnarray}
-Here $\hat{\vect n}$ denotes a normal vector to the face $F\in\bfaces[int]$ and $\left[\vect u\cdot\hat{\vect n}\right]$ is the jump of the normal flux across $F$.
-On the outer boundary $\partial\Omega$ we assume \eqref{dual:bc:neumann}.
+Here $\hat{\vect n}$ denotes a normal vector to the face $F\in\bfaces[int]$ and $\llbracket \vect u\cdot\hat{\vect n} \rrbracket$ is the jump of the normal flux across $F$.
+On the outer boundary $\partial\Omega$ we assume \eqref{dual:bc}.
 
@@
 Before we go into details of the method, we note that $\lambda$ can also  be observed as the Lagrange multiplier corresponding to the normal flux condition~\eqref{flux_cond}.
-The problem \eqref{dual_mini}--\eqref{flux_cond} can be formulated in the weak form: Find  $\vect u  \in \bigotimes\limits_{\bcell\in\bmesh}\HDivSpace[\bcell]$, $ p\in\LTwoSpace[\Omega]$, $\lambda\in H^{\frac12}(\bfaces[int])$ such that $\vect u\cdot{\vect n}=g_N$ on $\partial\Omega_N$ and
-	%\begin{empheq}[box=\widefbox]{equation}
+The problem \eqref{dual_mini}--\eqref{flux_cond} can be formulated in the weak form: \toDiscuss{Find}  $\vect u \in \bigotimes\limits_{\bcell\in\bmesh}\HDivNodeSpace[\bcell]$, $ p\in\LTwoSpace$, $\lambda \in \bigotimes\limits_{\bface\in\bfaces[int]}\HHalfSpace$ such that
 \begin{equation}\label{weak_form}
 	\begin{split}
-				\int_{\Omega} \vect K^{-1}\,\vect u\cdot\vect v \diff \vect x - \sum_{\bcell\in\bmesh}\int_\bcell p\,\nabla\cdot\vect v \diff \vect x +\int_{\bfaces[int]} \lambda\,\left[\vect v\cdot\hat{\vect n}\right] \diff \vect l &- \int_{\bfaces[int]}\left[\vect u\cdot\hat{\vect n}\right]\mu\diff \vect l, \\
-				+\sum_{\bcell\in\bmesh}\int_\bcell \nabla\cdot\vect u\,q \diff \vect x + \int_\Omega c\,p\,q \diff \vect x &= \int_\Omega f\,q \diff \vect x-\int_{\partial\Omega_D}\vect v\cdot{\vect n}g_D\diff \vect l
+		\int_{\Omega} \vect K^{-1}\,\vect u\cdot\vect v \diff \vect x - \sum_{\bcell\in\bmesh}\int_\bcell p\,\nabla\cdot\vect v \diff \vect x + \sum_{\bface\in\bfaces[int]}\int_{\bface} \lambda\,\llbracket\vect v\cdot\hat{\vect n}\rrbracket \diff l &= -\int_{\partial\Omega_D} g_D\,\vect v\cdot\hat{\vect n} \diff l, \\
+		\sum_{\bcell\in\bmesh}\int_\bcell \nabla\cdot\vect u\,q \diff \vect x + \int_\Omega c\,p\,q \diff \vect x &= \int_\Omega f\,q \diff \vect x, \\
+		\sum_{\bface\in\bfaces[int]}\int_{\bface} \llbracket\vect u\cdot\hat{\vect n}\rrbracket\,\mu \diff l &= 0
 \end{split}
 \end{equation}
-for all $\vect v  \in \bigotimes\limits_{\bcell\in\bmesh}\HDivSpace[\bcell]$, $ q\in\LTwoSpace[\Omega]$, $\mu\in H^{\frac12}(\bfaces[int])$.
+for all $\vect v \in \bigotimes\limits_{\bcell\in\bmesh}\HDivNodeSpace[\bcell]$, $q \in \LTwoSpace[\Omega]$, and $\mu \in \bigotimes\limits_{\bface\in\bfaces[int]}\HHalfSpace$\footnotemark{}.
 
-	\section{Approximate Static Condensation Method} \label{sec:ASC}
+\footnotetext{Here we assumed~$g_N \equiv 0$.
+The case $g_N \ne 0$ is handled via the change of variables~$\vect u = \vect u_0 + \vect u_N$, $\vect u_0\cdot\hat{\vect n} = 0$ and $\vect u_N\cdot\hat{\vect n} = g_N$ on~$\partial\Omega_N$ with some fixed~$\vect u_N \in \bigotimes\limits_{\bcell\in\bmesh}\HDivSpace[\bcell]$.}
 
-	In this section we describe  approximate static condensation method of order $n$ ( ASC($n$)\,), for solving the multi-material heterogeneous diffusion problem~\eqref{dual}.
+%Find  $\vect u  \in \bigotimes\limits_{\bcell\in\bmesh}\HDivSpace[\bcell]$, $ p\in\LTwoSpace[\Omega]$, $\lambda\in H^{\frac12}(\bfaces[int])$ such that $\vect u\cdot\hat{\vect n}=g_N$ on $\partial\Omega_N$ and
+%\begin{equation}\label{weak_form}
+%		\begin{split}
+%				\int_{\Omega} \vect K^{-1}\,\vect u\cdot\vect v \diff \vect x - \sum_{\bcell\in\bmesh}\int_\bcell p\,\nabla\cdot\vect v \diff \vect x +\int_{\bfaces[int]} \lambda\,\left[\vect v\cdot\hat{\vect n}\right] \diff \vect l &- \int_{\bfaces[int]}\left[\vect u\cdot\hat{\vect n}\right]\mu\diff \vect l, \\
+%				+\sum_{\bcell\in\bmesh}\int_\bcell \nabla\cdot\vect u\,q \diff \vect x + \int_\Omega c\,p\,q \diff \vect x &= \int_\Omega f\,q \diff \vect x-\int_{\partial\Omega_D}\vect v\cdot\hat{\vect n}g_D\diff \vect l
+%		\end{split}
+%\end{equation}
+%for all $\vect v  \in \bigotimes\limits_{\bcell\in\bmesh}\HDivSpace[\bcell]$, $ q\in\LTwoSpace[\Omega]$, $\mu\in H^{\frac12}(\bfaces[int])$.
 
-        Consider an arbitrary but fixed cell $T\in\bmesh$. We now introduce the discretization of the local diffusion problem \eqref{dual_mini} in $T$.
-        To this end, we consider the local mesh $\mmesh(T)$ of $T$, which is reffered as mini-mesh. While the original triangulation $\bmesh$ is referred as macro-mesh.
+\section{Approximate static condensation method} \label{sec:ASC}
+
+In this section we describe  approximate static condensation method of order $n$, ASC($n$), for solving the multi-material heterogeneous diffusion problem~\eqref{dual}.
+
+Consider an arbitrary but fixed cell $T\in\bmesh$.
+We now introduce the discretization of the local diffusion problem \eqref{dual_mini} in $T$.
+To this end, we consider the local mesh $\mmesh(T)$ of $T$, which is referred as mini-mesh.
+While the original triangulation $\bmesh$ is referred as macro-mesh.
 \begin{wrapfigure}{r}{0.4\textwidth}
@@
 We shall discretize \eqref{dual_mini} in $T$ in terms of average fluxes assigned to each face from $\mfaces(T)$,
-we denote the corresponding vector by ${\vect u}_\mmesh\in\mathbb{R}^{n_f}$, $n_f=2\,(\#\mfaces(T))$,  and concentration values assigned to each cell  ${\tau \in \mmesh(T)}$, we denote the corresponding vector by ${\vect p}_\mmesh\in\mathbb{R}^{n_p}$, $n_p=\#\mmesh(T)$.
+we denote the corresponding vector by ${\vect u}_\mmesh\in\mathbb{R}^{n_f}$, \toDiscuss{$n_f=\#\mfaces(T)$},  and concentration values assigned to each cell ${\tau \in \mmesh(T)}$, we denote the corresponding vector by ${\vect p}_\mmesh\in\mathbb{R}^{n_p}$, $n_p=\#\mmesh(T)$.
 The given data is the source term vector ${\vect f}_\mmesh\in \mathbb{R}^{n_p}$ and the concentration values $\lambda$ on the boundary of $T$.
@@
 		\begin{pmatrix}
-			\vect M_\mmesh & \vect B^T_\mmesh \\
+			\phantom{-}\vect M_\mmesh & \vect B^T_\mmesh \\
 			-\vect B_\mmesh & \vect \Sigma_\mmesh
@@
 	\end{equation}
-Here $\vect M_\mmesh,~\vect\Sigma_\mmesh$, $\vect B^T_\mmesh$, $-\vect B_\mmesh$ are vector-mass, mass, gradient and divergence matrices, respectively.
-$C_\mmesh$ is a diagonal scaling matrix. i.e. the mass matrix for ${\vect \lambda}_\mmesh$ unknowns;
-$\vect E_\mmesh \in \mathbb{R}^{n_{\lambda}\times n_f} $ is a rectangular matrix with 0 and 1 entries which sparsifies a vector from  $\mathbb{R}^{n_{\lambda}}$
+Here $\vect M_\mmesh$, $\vect\Sigma_\mmesh$, $\vect B^T_\mmesh$, $(-\vect B_\mmesh)$ are vector-mass, mass, gradient and divergence matrices, respectively.
+\toDiscuss{$(-\vect C_\mmesh)$} is a diagonal scaling matrix. i.e. the mass matrix for ${\vect \lambda}_\mmesh$ unknowns;
+$\vect E_\mmesh \in \toDiscuss{\mathbb{R}^{n_f \times n_\lambda}}$ is a rectangular matrix with 0 and 1 entries which sparsifies a vector from  $\mathbb{R}^{n_{\lambda}}$
 to a vector from  $\mathbb{R}^{n_{f}}$.
@@
 \end{equation}
-where $E_\mmesh^T$ is the restriction matrix with entries equal $0$ or $1$.
+where $\vect E_\mmesh^T$ is the restriction matrix with entries equal $0$ or $1$.
 
@@
 \begin{align} \label{defA}
-		\vect A_\mmesh &= \vect E^T_\mmesh \left( \vect M^{-1}_\mmesh + \vect M^{-1}_\mmesh\,\vect B^T_\mmesh \left( \vect \Sigma_\mmesh + \vect B_\mmesh\,\vect M^{-1}_\mmesh\,\vect B^{T}_\mmesh\right)^{-1} \vect B_\mmesh\,\vect M^{-1}_\mmesh \right) \vect E_\mmesh, \\
+	\vect A_\mmesh &= \vect E^T_\mmesh \left( \vect M^{-1}_\mmesh - \vect M^{-1}_\mmesh\,\vect B^T_\mmesh \left( \vect \Sigma_\mmesh + \vect B_\mmesh\,\vect M^{-1}_\mmesh\,\vect B^{T}_\mmesh\right)^{-1} \vect B_\mmesh\,\vect M^{-1}_\mmesh \right) \vect E_\mmesh, \\
 	{\vect a}_\mmesh &= \vect E^{T}_\mmesh\,\vect M^{-1}_\mmesh\,\vect B^T_\mmesh \left( \vect \Sigma_\mmesh + \vect B_\mmesh\,\vect M^{-1}_\mmesh\,\vect B^{T}_\mmesh\right)^{-1} {\vect f}_\mmesh.
 \end{align}
-Note that matrices ~$\vect A_\mmesh$ and vector~${\vect a}_\mmesh$ are computed locally for each $T\in\bmesh$.
+Note that matrices~$\vect A_\mmesh$ and vectors~${\vect a}_\mmesh$ are computed locally for each $T\in\bmesh$.
 \smallskip
@@
 \[
-\Lambda=\left\{\lambda\in L^2(F)\,:\, \lambda\in P_n~\text{for any}~F\in\bfaces[int]\right\}.
+\Lambda=\left\{\lambda\in \LTwoSpace[\toDiscuss{\bfaces[int]}]\,:\, \lambda\in P_n~\text{for any}~F\in\bfaces[int]\right\}.
 \]
@@
 \end{equation}
-	Here~$\{s\}_{i=0,\dots,n}$ is the set of $L^2(F)$-orthogonal polynomials of degree~$n$.
+Here~$\{\,s_i\,\}_{i=0,\dots,n}$ is the set of $\LTwoSpace[\bface]$-orthogonal polynomials of degree~$n$.
 
- For $F \in \bfaces[int]$ shared by two polygonal cells~$\bcell^\pm\in \bmesh$  denote by~$\mfaces^\pm_F \subset \mfaces_{\text{ext}}(T^\pm)$ the subsets of mini-faces that belong to the macro-face~$F$ from each side.
-Let~$\nu_F \coloneqq \max\,\{ \#\,\mfaces^+_F,\,\#\,\mfaces^-_F \}$.
-With each face $F \in \bfaces_\bcell$ we associate~$\min\,\{ n+1, \nu_F \}$ degrees of freedom~\eqref{asc_dofs} in the $\Lambda$ space. The local and global number of DOFs are
+For $F \in \bfaces[int]$ shared by two polygonal cells~$\bcell^\pm\in \bmesh$  denote by~$\mfaces_F(T^\pm) \subset \mfaces_{\text{ext}}(T^\pm)$ the subsets of mini-faces that belong to the macro-face~$F$ from each side.
+Let $\nu_F \coloneqq \max\,\{ \#\,\mfaces_F(T^+),\,\#\,\mfaces_F(T^-) \}$.
+\toDiscuss{We} set~$\bfaces_\bcell \subset \bfaces$ to be a subset of macro-faces forming the boundary of a cell~$T$.
+With each face $F \in \bfaces_\bcell$ we associate~$\min\,\{ n+1, \nu_F \}$ degrees of freedom~\eqref{asc_dofs} in the $\Lambda$ space.
+The local and global number of d.o.f.
+are
 \[
@@
 
-Further denote by~${{\vect \lambda}_\bcell \in \Rn{n_\bcell}}$ a vector of DOFs for elements of $\Lambda$ associated with all macro-faces spanning the boundary of~$\bcell$.
-We need a correspondence between elements of $\Lambda$ and local edge elements $\lambda_\mmesh$ used as boundary data in local problem \eqref{local}.
+Further denote by~${{\vect \lambda}_\bcell \in \Rn{n_\bcell}}$ a vector of d.o.f.
+for elements of $\Lambda$ associated with all macro-faces spanning the boundary of~$\bcell$.
+We need a correspondence between elements of $\Lambda$ and local \toDiscuss{edge elements} $\vect \lambda_\mmesh$ used as boundary data in local problem \eqref{local}.
 This corresponding is given by the interpolation matrix $ \vect R_\mmesh$,
@@
 	%The interpolating matrix~$\vect R_\mmesh$ is completely defined by~$n$ and boundary mini\,faces~$\mfaces[ext]$ of~$\mmesh$.
-If we find the mortar vector ~${\vect \lambda}_\bcell$, we recover the local approximation to the edge concentration, i.e. ${\vect \lambda}_\mmesh$, from~\eqref{asc_lambda}.
+If we find the mortar vector ~${\vect \lambda}_\bcell$, we recover the local approximation to the \toDiscuss{edge} concentration, i.e. ${\vect \lambda}_\mmesh$, from~\eqref{asc_lambda}.
 Further we solve numerically local subproblems in~\eqref{dual_mini} applying the mimetic FD method. This completes the solution algorithm for \eqref{dual}.
@@
 \end{equation}
-with $\vect u|_{\bcell^+}(x)={\vect u}^\text{ext}_\mmesh(f)|f|$, if $x\in f$ for $f\in \mfaces[ext](\bcell^+)$, and ${\vect u}^\text{ext}_\mmesh(f)$ is the local flux assigned to $f$.
+with \toDiscuss{$\big(\vect u|_{\bcell^+}\cdot\hat{\vect n}\big)(\vect x) = u^\text{ext}_\mmesh(f)\,|f|$}, if $\vect x \in f$ for $f\in\mfaces_F(T^+)$, and $u^\text{ext}_\mmesh(f) \in \vect u^\text{ext}_\mmesh$ is the local flux assigned to $f$.
 Similar definition applies to $\vect u|_{\bcell^-}$.
-This and ~\eqref{asc_flux_lambda} result in the linear algebraic system
+This and~\eqref{asc_flux_lambda} result in the linear algebraic system
 \begin{equation}\label{asc_system}
@@
 with	$\vect S_\bmesh \in \Rn{n_\bmesh \times n_\bmesh}, {\vect \lambda}_\bmesh, {\vect b}_\bmesh \in \Rn{n_\bmesh}$.
-Neumann boundary condition in~\eqref{dual:bc:neumann} is handle in the similar way, and Dirichlet boundary data in~\eqref{dual:bc:neumann} is enforced strongly in~\eqref{asc_system}.
+Neumann boundary condition in~\eqref{dual:bc} is handled in the similar way, and Dirichlet boundary data in~\eqref{dual:bc} is enforced strongly in~\eqref{asc_system}.
 
 Matrix~$\vect S_\bmesh$ is sparse and its sparsity pattern does not depend on mini-meshes. Some useful properties of this matrix will be discussed in the next section.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 We concentrate on ASC(1), which we implement and validate  in the next section.
-We shall make necessary remarks about ASC(0) as it is largely obtain by obvious simplifications of ASC(1).
+We shall make necessary remarks about ASC(0) as it is largely obtained by obvious simplifications of ASC(1).
 
@@
 		\svginputw{e_plus_2.pdf_tex}
-			\caption{$\nu_F = 2$}		
+		\caption{$\nu_F = 3$}		
 	\end{subfigure}
-\caption{$\lambda_{ij}(\mmesh)$ are local d.o.f. used in MFD for $\lambda$ from \eqref{dual_mini}, $\lambda_{i}(T)$, $\lambda'_{i}(T)$ are global d.o.f. used to describe mortar space $\Lambda$.
-Left: Face $F$ is single-material and uses one global d.o.f.; Right: Face $F$ is multi-material and uses two global d.o.f.\label{fig:asc_dofs:asc1:mmc}}
+	\caption{$\lambda_{ji}(\mmesh)$ are local d.o.f.
+used in MFD for $\lambda$ from \eqref{dual_mini}, $\lambda_j(T)$, $\lambda'_j(T)$ are global d.o.f.
+used to describe mortar space $\Lambda$.
+Left: Face $F$ is single-material and uses one global d.o.f.; Right: Face $F$ is multi-material and uses two global d.o.f.
+	\label{fig:asc_dofs:asc1:mmc}}
 \end{figure}
 
-The method uses local piecewise constant  and global piecewise $P_1$ (for ASC(1)\,) approximation of the concentration on $\bfaces$.
-Local piecewise constant approximations $\lambda_\mmesh$, however, use finer local subdivisions and so $\lambda_\mmesh$ does not belong to the restriction of the global space $\Lambda$ on the boundary of a given cell $T$.
+The method uses local piecewise constant  and global piecewise $P_1$ \big(for ASC(1)\big) approximation of the concentration on $\bfaces$.
+Local piecewise constant approximations $\vect\lambda_\mmesh$, however, use finer local subdivisions, so $\vect\lambda_\mmesh$ does not belong to the restriction of the global space $\Lambda$ on the boundary of a given cell $T$.
 For the method, we define a mapping given by the matrix $\vect R_\mmesh$ to map global to local degrees of freedom and $\vect R_\mmesh^T$ from local   to global.
@@
 
-We  define $\vect R_\mmesh$ locally for any fixed $T\in\bmesh$.
+We define $\vect R_\mmesh$ locally for any fixed $\bcell\in\bmesh$.
 Let us enumerate all faces of the given $T$ by index $j$.
@@
 Further, denote by $\lambda_{j\,i}(\mmesh)$ the local d.o.f.
-assigned  to the $i$-th mini-face~ belonging to the $j$-th macro-face~, and by $\lambda_{j}(T)$, $\lambda_{j}'(T)$ to moments defining an element from $\Lambda$ on the $j$-th macro-face (see Figure~\ref{fig:asc_dofs:asc1:mmc})) so that
+assigned to the $i$-th mini-face belonging to the $j$-th macro-face, and by $\lambda_{j}(T)$, $\lambda_{j}'(T)$ two moments defining an element from $\Lambda$ on the $j$-th macro-face \big(see Figure~\ref{fig:asc_dofs:asc1:mmc})\big) so that
 we have for $\lambda\in\Lambda$,
@@
 
-Integrating \eqref{lambda_intermsof_moments} over all mini-faces $f\in \mfaces(T)\cap F$ ($f$ has local index $i$ among mini-faces belonging to $F$) and re-scaling, we get
+Integrating \eqref{lambda_intermsof_moments} over all mini-faces \toDiscuss{$f \in \mfaces_\bface(\bcell)$} ($f$ has local index $i$ among mini-faces belonging to $F$) and re-scaling, we get
 \begin{equation}\label{asc1_interp}
@@
 where $s_{j\,i} $ is a signed distance between centroids of~$f$  and~$F$.
-For the corresponding vectors of unknowns  ${\vect \lambda}_\mmesh = \{ \lambda_{j\,i}(\mmesh) \}$ and ${\vect \lambda}_\bcell = \{ \lambda_{i}(\bcell) \}$ this defines
-the matrix $\vect R_\mmesh$ through
-\[
-{\vect \lambda}_\mmesh=\vect R_\mmesh {\vect \lambda}_\bcell.
-\]
-For the example in Figure~\ref{fig:asc_dofs:asc1:mmc}\,(left), $\vect R_\mmesh$ is given by
+For the corresponding vectors of unknowns  ${\vect \lambda}_\mmesh = \{ \lambda_{j\,i}(\mmesh) \}$ and \toDiscuss{${\vect \lambda}_\bcell = \{ \lambda_{j}(\bcell) \} \cup \{ \lambda'_{j}(\bcell) \}$} this defines
+the matrix $\vect R_\mmesh$ through~\eqref{asc_lambda}. For the example in Figure~\ref{fig:asc_dofs:asc1:mmc} (left), $\vect R_\mmesh$ is given by
 \begin{equation*}\footnotesize
@@
 \begin{equation*}
-\left\{
-\begin{split}
-		\sum_{f\in \mfaces(T^+)\cap F} u^{\text{ext}}_{\mmesh^+}(f)\,|f| &+ \sum_{f\in \mfaces(T^-)\cap F} u^{\text{ext}}_{\mmesh^-}(f)\,|f| &= 0 \\
-		\sum_{f\in \mfaces(T^+)\cap F} u^{\text{ext}}_{\mmesh^+}(f)\,\int_{f} s_1 \diff{l} &+ \sum_{f\in \mfaces(T^-)\cap F} u^{\text{ext}}_{\mmesh^-}(f)\,\int_{f} s_1 \diff{l} &= 0
-\end{split}
-\right.
+	\left\{\begin{split}
+		\sum_{f\in \mfaces_F(T^+)} u^{\text{ext}}_{\mmesh^+}(f)\,|f| &+ \sum_{f\in \mfaces_F(T^-)} u^{\text{ext}}_{\mmesh^-}(f)\,|f| &= 0, \\
+		\sum_{f\in \mfaces_F(T^+)} u^{\text{ext}}_{\mmesh^+}(f)\,\int_{f} s_1 \diff{l} &+ \sum_{f\in \mfaces_F(T^-)} u^{\text{ext}}_{\mmesh^-}(f)\,\int_{f} s_1 \diff{l} &= 0
+	\end{split}\right.
 %\quad\Leftrightarrow \\
@@
 where $i$ and $j$ are the local indexes of the face $F$ in the cells $T^+$ and $T^-$, respectively.
-If $F$ from $T^+$ belong to the Neumann part of the boundary, then we have
-	\begin{align*}
-		\left( \vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,{\vect u}^{\text{ext}}_{\mmesh^+} \right)_i &= \left( \vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,{\vect g}_{N\,\mmesh^+} \right)_i, \quad
-		{\vect g}_{N\,\mmesh^+} &\coloneqq \left\{ \int_f g_N\,s_k \diff{l}\,/\,|f| \right\}_{f \in \mfaces[ext,\,\textit{N}]}, \quad k = 0, 1.
-	\end{align*}
+\toDiscuss{For} the Neumann part of the boundary we set $\mfaces_N(\bcell) \coloneqq \{ f \in \mfaces[ext](\bcell)\::\:f \subset \partial\Omega_N \}$.
+If $F$ from $T^+$ belongs to the Neumann part of the boundary, then we have
+\begin{equation*}
+	\left( \vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,{\vect u}^{\text{ext}}_{\mmesh^+} \right)_i = \left( \vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,{\vect g}_{N\,\mmesh^+} \right)_i, \quad
+	{\vect g}_{N\,\mmesh^+} \coloneqq \left\{ \int_f g_N\,s_k \diff{l}\,/\,|f| \right\}_{f\,\in\,\mfaces_N(\bcell),\:k\,\in\,\{0,\,1\}}.
+\end{equation*}
 
@@
 		\Big( \underbrace{\left( \vect R^T_{\mmesh^-}\,\vect C_{\mmesh^-}\,\vect A_{\mmesh^-}\,\vect C_{\mmesh^-}\,\vect R_{\mmesh^-} \right)}_{\vect S_{\bcell^-} \coloneqq} {\vect \lambda}_{\bcell^-} \Big)_j = \\
-			\big( \underbrace{\vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,{\vect a}_{\mmesh^+}}_{{\vect b}_{\bcell^+}} \big)_i
+		\big( \underbrace{\vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,{\vect a}_{\mmesh^+}}_{{\vect b}_{\bcell^+} \coloneqq} \big)_i
 		&+
-			\big( \underbrace{\vect R^T_{\mmesh^-}\,\vect C_{\mmesh^-}\,{\vect a}_{\mmesh^-}}_{{\vect b}_{\bcell^-}} \big)_j.
+		\big( \underbrace{\vect R^T_{\mmesh^-}\,\vect C_{\mmesh^-}\,{\vect a}_{\mmesh^-}}_{{\vect b}_{\bcell^-} \coloneqq} \big)_j.
 	\end{split}
@@
 \end{align}
-where $N_\bcell$ defines global to local mapping for the cell $T$.
+where $\vect N_\bcell$ defines global to local mapping for the cell $T$.
 
-From~\eqref{local_system} it is clear that~$\vect S_\bmesh$ is sparse: Global  $\lambda_{\bmesh\,i}$ interacts only with d.o.f.
-associated with faces of macro elements that share $i$th base\,face.
-For example, if $F\in\bfaces[ext]$ is shared by two quadrilaterals and has global index $i$, then $i$th row of~$\vect S_\bmesh$ will have~7 nonzero elements.
+From~\eqref{local_system} it is clear that~$\vect S_\bmesh$ is sparse: Global d.o.f.
+$\lambda_m(\bmesh)$, $\lambda'_m(\bmesh)\in\vect\lambda_\bmesh$ interact only with d.o.f.
+associated with faces of macro-cells that share $m$th macro-face.
+For example, if \toDiscuss{$F\in\bfaces[int]$} is shared by two quadrilaterals and has global index $m$, then $m$th row of~$\vect S_\bmesh$ will have~$m_\text{nnz}$ nonzero elements, $7 \le m_\text{nnz} \le 14$ (for ASC(0) $m_\text{nnz} = 7$).
 %; if $i$th base\,face is a face shared by a quadrilateral and a triangle, $i$th row of~$\vect S_\bmesh$ will have~6 nonzero elements and so forth.
@@
 Same arguments hold for ASC(0) after obvious simplifications.
+\\
 %\begin{theorem}\label{thm:asc0}
@@
 %	\end{proof}
-
 \begin{lemma}\label{thm:asc1}
@@
 	\end{equation}
-		where~$m \coloneqq$ number of base\,faces spanning~$\bcell$ and
+	where~$m \coloneqq$ number of macro-faces spanning~$\bcell$ and
 	\begin{equation*}
@@
 	\end{equation*}
-		$1 < m_k$ is the number of mini-faces of the~$k$th macro-face, $ s_{k\,i}$ is the signed distance between centroids of~$i$th mini-face and~$k$th base\,face.
+	$1 < m_k$ is the number of mini-faces of the~$k$th macro-face, $ s_{k\,i}$ is the signed distance between centroids of~$i$th mini-face and~$k$th macro-face.
 If~$\bcell$ contains only one material, then $\vect R_\mmesh = \vect I$ and hence $\Ker\vect R_\mmesh = \{ {\vect 0} \}$, so we assume that there is at least one multi-material  face.
 
-		Clearly, matrix~$\vect R_\mmesh$ has a non\,--\,trivial kernel iff
+	Clearly, matrix~$\vect R_\mmesh$ has a non-trivial kernel iff
 	\begin{equation*}
@@
 		 s_1 = \frac{1}{2}\left( |f_1| - |F| \right), \quad
-			 s_2 = |f_1| + \frac{1}{2}\left( |f_2| - |F| \right)
+		 s_2 = |f_1| + \frac{1}{2}\left( |f_2| - |F| \right),
 	\]
@@
 	Hence $ s_1 \ne  s_2$, and~$\Ker\vect R_\mmesh = \{ {\vect 0} \}$ follows.
-
 \end{proof}
 
-	\begin{theorem} Matrix $\vect S_\bmesh$ is symmetric. If $c \ne 0$ or $|\partial\Omega_D|>0 $, then  $\vect S_\bmesh$ is positive definite.
+\begin{theorem} 
+	Matrix $\vect S_\bmesh$ is symmetric \toDiscuss{and non-negative definite}. If $c \ne 0$ or $|\partial\Omega_D|>0 $, then  $\vect S_\bmesh$ is positive definite.
 \end{theorem}
-
 \begin{proof}
 	From the identity \eqref{defA} it immediately follows that $\vect A_{\mmesh}$ is symmetric and non-negative definite.
-Thus, the symmetry of $\vect S_\bmesh$ follows from the definition in \eqref{local_system}--\eqref{global_system_assembly}.
+Thus, the first statement follows from the definition of~$\vect S_\bmesh$ in \eqref{local_system}--\eqref{global_system_assembly}.
 It is easy to see that $\vect A_{\mmesh}$ is positive definite for all~$\bcell$, where $c \ne 0$.
-Hence if $c \ne 0$ in $\Omega$ , then \eqref{local_system}--\eqref{global_system_assembly} and the full ranks of $\vect R$-s and $\vect C$-s imply
-the positive definiteness of $\vect S_\bmesh$.
+Hence if $c \ne 0$ in $\Omega$, then \eqref{local_system}--\eqref{global_system_assembly} and the full ranks of $\vect R_\mmesh$'s and $\vect C_\mmesh$'s imply the positive definiteness of $\vect S_\bmesh$.
 	Now we show the positive definiteness of $\vect S_\bmesh$ if $|\partial\Omega_D|>0 $. Consider  any given $\bcell\in\bmesh$.
 	Matrix  $\vect A_{\mmesh}$ defines the discrete Dirichlet-to-Neumann map for $\partial\bcell$.
-If $\partial\bcell\cap\partial\Omega_D$, then $\mbox{ker}(\vect A_{\mmesh})=0$.
-Otherwise $\mbox{dim}(\mbox{ker}(\vect A_{\mmesh}))=1$ and $\vect A_{\mmesh}\vect C_{\mmesh}\lambda_\mmesh=0$ implies that $\lambda_\mmesh$ is constant on $\partial\bcell$.
+	If $\partial\bcell\cap\partial\Omega_D$, then $\Ker \vect A_{\mmesh} = \{\vect 0\}$.
+Otherwise $\mbox{dim}(\Ker \vect A_{\mmesh})=1$ and $\vect A_{\mmesh}\,\vect C_{\mmesh}\,\vect\lambda_\mmesh=0$ implies that $\vect\lambda_\mmesh$ is constant on $\partial\bcell$.
 Consider some $\lambda$ from the mortar space $\Lambda$ and corresponding vector of moments  $\vect \lambda_\bmesh$.
-Using connectivity of the mesh one easily finds that $\vect R_\mmesh \lambda_\bmesh$ can be constant on every $T\in\bmesh$ only if $\lambda$ is constant.
-Due to the assumption $|\partial\Omega_D|>0 $ this implies $\lambda=0$.
+Using connectivity of the mesh one easily finds that \toDiscuss{$\vect R_\mmesh\,\vect\lambda_\mmesh$} can be constant on every $T\in\bmesh$ only if $\lambda$ is constant.
+Due to the assumption $|\partial\Omega_D|>0$ this implies $\lambda=0$.
 	% Thus we have
@@
 	%		for some~$\bcell \in \bmesh$ since~$\Ker\vect R_\mmesh = \{ {\vect 0} \}$. So
-Hence for any $0\neq\lambda_\bmesh\in \mathbb{R}^{n_\bmesh}$ we have
+	Hence for any $\vect0\neq\vect\lambda_\bmesh\in \mathbb{R}^{n_\bmesh}$ we have
 	\begin{align*}
-			\left(\vect S_\bmesh\,\lambda_\bmesh,\,\lambda_\bmesh\right) &\stackrel{\eqref{global_system_assembly}}{=}
-			\Big( \big( \sum_{\bcell \in \bmesh} \vect N^T_\bcell\,\vect S_\bcell\,\vect N_\bcell \big){\lambda_\bmesh},\,{\lambda_\bmesh} \Big) =
-			\sum_{\bcell \in \bmesh} \big( \vect S_\bcell\,\vect N_\bcell\,{\lambda_\bmesh},\,\underbrace{\vect N_\bcell\,{\lambda_\bmesh}}_{{\vect x} \coloneqq} \big)\\
-& =
-			\sum_{\bcell \in \bmesh} \big(\vect S_\bcell\,{\vect x},\,{\vect x} \big) > 0.
+		\left(\vect S_\bmesh\,\vect\lambda_\bmesh,\,\vect\lambda_\bmesh\right) &\stackrel{\eqref{global_system_assembly}}{=}
+		\Big( \big( \sum_{\bcell \in \bmesh} \vect N^T_\bcell\,\vect S_\bcell\,\vect N_\bcell \big){\vect\lambda_\bmesh},\,{\vect\lambda_\bmesh} \Big) =
+		\sum_{\bcell \in \bmesh} \big( \vect S_\bcell\,\vect N_\bcell\,{\vect\lambda_\bmesh},\,\underbrace{\vect N_\bcell\,{\vect\lambda_\bmesh}}_{{\vect \lambda_\bcell} \coloneqq} \big) \\
+		& = \sum_{\bcell \in \bmesh} \big(\vect S_\bcell\,{\vect \lambda_\bcell},\,{\vect \lambda_\bcell} \big) > 0.
 	\end{align*}
-The last inequality holds, since the exists $\bcell$ such that $\vect x=N_\bcell\,{\lambda_\bmesh}$ is not in the kernel for $\lambda_\bmesh\neq0$.
+	The last inequality holds, since there exists $\bcell$ such that $\vect \lambda_\bcell=\vect N_\bcell\,{\vect\lambda_\bmesh}$ is not in the kernel for $\vect\lambda_\bmesh\neq\vect0$.
 \end{proof}
@@
 
- \subsection*{Acknowledgements} Alexander Zhiliakov acknowledges the internship opportunity in Methods and Algorithms group of the Los Alamos National Laboratory.
+\subsection*{Acknowledgments} Alexander Zhiliakov acknowledges the internship opportunity in Methods and Algorithms group of the Los Alamos National Laboratory.
+
 \bibliographystyle{plain}

### 2018-11-26 asc.tex
added co-authors and diffusion to the title

--- 2018-11-16 asc.tex
@@
 
-\title{A higher order approximate static condensation method for multi-material problems}
+\title{A higher order approximate static condensation method for multi-material diffusion problems}
 \author{
@@
 Maxim Olshanskii\thanks{Department of Mathematics, University of Houston, Houston, Texas 77204 (molshan@math.uh.edu); Partially supported by NSF through grant  DMS-1717516.}
+\and Evgeny Kikinzon \thanks{Los Alamos National Laboratory, Los Alamos,
+  New Mexico, USA (kikinzon@lanl.gov).}
+\and Mikhail Shashkov\thanks{Los Alamos National Laboratory, Los Alamos,
+  New Mexico, USA (shashkov@lanl.gov).}
 }

### 2018-11-27 asc.tex
Modify SPD proof + add minor fixes to theoretical part

--- 2018-11-26 asc.tex
@@
 
-\DeclareMathOperator{\Ker}{Ker}
-
-% listings
-%\usepackage{listings}
-%\lstset{
-%	basicstyle=\linespread{.95}\footnotesize\ttfamily\color{black},
-%	keywordstyle=\color{green!40!black},
-%	emphstyle=\bfseries\color{green!40!black},
-%	commentstyle=\itshape\color{purple!40!black},
-%	identifierstyle=\color{blue!30!black},
-%	showstringspaces=false,
-%	stringstyle=\color{orange},
-%	numbers=left,
-%	tabsize=2,
-%	breaklines=true,
-%	breakatwhitespace=true,
-%	language=C++
-%}
+\DeclareMathOperator{\Ker}{ker}
+\DeclareMathOperator{\Dim}{dim}
 
@@
 
-\begin{document}
-
-\title{A higher order approximate static condensation method for multi-material problems}
+\title{A higher order approximate static condensation method for multi-material diffusion problems}
 \author{
@@
 	Maxim Olshanskii\thanks{Department of Mathematics, University of Houston, Houston, Texas 77204 (molshan@math.uh.edu); Partially supported by NSF through grant  DMS-1717516.}
+	\and Evgeny Kikinzon \thanks{Los Alamos National Laboratory, Los Alamos,
+		New Mexico, USA (kikinzon@lanl.gov).}
+	\and Mikhail Shashkov\thanks{Los Alamos National Laboratory, Los Alamos,
+		New Mexico, USA (shashkov@lanl.gov).}
 }
+
+\begin{document}
 
@@
 	\section{Introduction}
+
 	Multi-phase and multi-material processes are ubiquitous in nature and engineering.
@@
 	In this report, we devise  a higher order method for the numerical solution of the diffusion problem with discontinuous  coefficients on a general polyhedral mesh, which does not respect the position of multi-material interfaces.
-The method builds upon the approximate static condensation (ASC) algorithm first  proposed in ~\cite{kikinzon2017approximate}; it admits high-contrast diffusion coefficients and discontinuous reconstruction of the interfaces as typical for the volume/moment-of-fluid method.
+The method builds upon the approximate static condensation (ASC) algorithm first proposed in~\cite{kikinzon2017approximate}; it admits high-contrast diffusion coefficients and discontinuous reconstruction of the interfaces as typical for the volume/moment-of-fluid method.
 The ASC approach uses the formulation of the interface diffusion problem as a system of local inter-cell problems  coupled through the concentration values and fluxes on the cell faces.
@@
 The meaning should be clear from a context.}.
-Introducing the new unknown \toDiscuss{$\lambda \in \HHalfSpace[\bfaces]$}, we reformulate \eqref{dual}--\eqref{dual:bc} as a system of local problems coupled through the boundary data
+	Introducing the new unknown $\lambda \in \HHalfSpace[\bfaces]$, we reformulate \eqref{dual}--\eqref{dual:bc} as a system of local problems coupled through the boundary data
 	and flux continuity condition:
@@
 	Before we go into details of the method, we note that $\lambda$ can also  be observed as the Lagrange multiplier corresponding to the normal flux condition~\eqref{flux_cond}.
-The problem \eqref{dual_mini}--\eqref{flux_cond} can be formulated in the weak form: \toDiscuss{Find}  $\vect u \in \bigotimes\limits_{\bcell\in\bmesh}\HDivNodeSpace[\bcell]$, $ p\in\LTwoSpace$, $\lambda \in \bigotimes\limits_{\bface\in\bfaces[int]}\HHalfSpace$ such that
+The problem \eqref{dual_mini}--\eqref{flux_cond} can be formulated in the weak form: Find $\vect u \in \bigotimes\limits_{\bcell\in\bmesh}\HDivSpace[\bcell]$ s.t.
+$\vect u \cdot \hat{\vect n} = g_N$ on $\partial\Omega_N$, $ p\in\LTwoSpace$, $\lambda\in\HHalfSpace[{\bfaces[int]}]$ such that
 	\begin{equation}\label{weak_form}
@@
 	\end{equation}
-for all $\vect v \in \bigotimes\limits_{\bcell\in\bmesh}\HDivNodeSpace[\bcell]$, $q \in \LTwoSpace[\Omega]$, and $\mu \in \bigotimes\limits_{\bface\in\bfaces[int]}\HHalfSpace$\footnotemark{}.
+	for all $\vect v \in \bigotimes\limits_{\bcell\in\bmesh}\HDivSpace[\bcell]$ s.t.
+$\vect v \cdot \hat{\vect n} = 0$ on $\partial\Omega_N$, $q \in \LTwoSpace[\Omega]$, and $\mu \in \HHalfSpace[{\bfaces[int]}]$.
 
-\footnotetext{Here we assumed~$g_N \equiv 0$.
+	%	\footnotetext{Here we assumed~$g_N \equiv 0$.
 The case $g_N \ne 0$ is handled via the change of variables~$\vect u = \vect u_0 + \vect u_N$, $\vect u_0\cdot\hat{\vect n} = 0$ and $\vect u_N\cdot\hat{\vect n} = g_N$ on~$\partial\Omega_N$ with some fixed~$\vect u_N \in \bigotimes\limits_{\bcell\in\bmesh}\HDivSpace[\bcell]$.}
-
 	%Find  $\vect u  \in \bigotimes\limits_{\bcell\in\bmesh}\HDivSpace[\bcell]$, $ p\in\LTwoSpace[\Omega]$, $\lambda\in H^{\frac12}(\bfaces[int])$ such that $\vect u\cdot\hat{\vect n}=g_N$ on $\partial\Omega_N$ and
@@
 	We shall discretize \eqref{dual_mini} in $T$ in terms of average fluxes assigned to each face from $\mfaces(T)$,
-we denote the corresponding vector by ${\vect u}_\mmesh\in\mathbb{R}^{n_f}$, \toDiscuss{$n_f=\#\mfaces(T)$},  and concentration values assigned to each cell ${\tau \in \mmesh(T)}$, we denote the corresponding vector by ${\vect p}_\mmesh\in\mathbb{R}^{n_p}$, $n_p=\#\mmesh(T)$.
+	we denote the corresponding vector by ${\vect u}_\mmesh\in\mathbb{R}^{n_f}$, $n_f=\#\mfaces(T)$,  and concentration values assigned to each cell ${\tau \in \mmesh(T)}$, we denote the corresponding vector by ${\vect p}_\mmesh\in\mathbb{R}^{n_p}$, $n_p=\#\mmesh(T)$.
 The given data is the source term vector ${\vect f}_\mmesh\in \mathbb{R}^{n_p}$ and the concentration values $\lambda$ on the boundary of $T$.
@@
 	\end{equation}
-Here $\vect M_\mmesh$, $\vect\Sigma_\mmesh$, $\vect B^T_\mmesh$, $(-\vect B_\mmesh)$ are vector-mass, mass, gradient and divergence matrices, respectively.
-\toDiscuss{$(-\vect C_\mmesh)$} is a diagonal scaling matrix. i.e. the mass matrix for ${\vect \lambda}_\mmesh$ unknowns;
-$\vect E_\mmesh \in \toDiscuss{\mathbb{R}^{n_f \times n_\lambda}}$ is a rectangular matrix with 0 and 1 entries which sparsifies a vector from  $\mathbb{R}^{n_{\lambda}}$
+	Here $\vect M_\mmesh$, $\vect\Sigma_\mmesh$, $\vect B^T_\mmesh$, $-\vect B_\mmesh$ are vector-mass, mass, gradient and divergence matrices, respectively.
+$-\vect C_\mmesh$ is a diagonal scaling matrix.
+i.e.
+the mass matrix for ${\vect \lambda}_\mmesh$ unknowns;
+	$\vect E_\mmesh \in \mathbb{R}^{n_f \times n_\lambda}$ is a rectangular matrix with 0 and 1 entries which sparsifies a vector from  $\mathbb{R}^{n_{\lambda}}$
 	to a vector from  $\mathbb{R}^{n_{f}}$.
@@
 	\[
-\Lambda=\left\{\lambda\in \LTwoSpace[\toDiscuss{\bfaces[int]}]\,:\, \lambda\in P_n~\text{for any}~F\in\bfaces[int]\right\}.
+		\Lambda=\left\{\lambda\in \LTwoSpace[{\bfaces[int]}]\,:\, \lambda\in P_n~\text{for any}~F\in\bfaces[int]\right\}.
 	\]
@@
 Let $\nu_F \coloneqq \max\,\{ \#\,\mfaces_F(T^+),\,\#\,\mfaces_F(T^-) \}$.
-\toDiscuss{We} set~$\bfaces_\bcell \subset \bfaces$ to be a subset of macro-faces forming the boundary of a cell~$T$.
+We set~$\bfaces_\bcell \subset \bfaces$ to be the subset of macro-faces forming the boundary of a cell~$T$.
 With each face $F \in \bfaces_\bcell$ we associate~$\min\,\{ n+1, \nu_F \}$ degrees of freedom~\eqref{asc_dofs} in the $\Lambda$ space.
@@
 for elements of $\Lambda$ associated with all macro-faces spanning the boundary of~$\bcell$.
-We need a correspondence between elements of $\Lambda$ and local \toDiscuss{edge elements} $\vect \lambda_\mmesh$ used as boundary data in local problem \eqref{local}.
+We need a correspondence between elements of $\Lambda$ and local face elements $\vect \lambda_\mmesh$ used as boundary data in local problem \eqref{local}.
 	This corresponding is given by the interpolation matrix $ \vect R_\mmesh$,
@@
 	%The interpolating matrix~$\vect R_\mmesh$ is completely defined by~$n$ and boundary mini\,faces~$\mfaces[ext]$ of~$\mmesh$.
-If we find the mortar vector ~${\vect \lambda}_\bcell$, we recover the local approximation to the \toDiscuss{edge} concentration, i.e. ${\vect \lambda}_\mmesh$, from~\eqref{asc_lambda}.
+	If we find the mortar vector ~${\vect \lambda}_\bcell$, we recover the local approximation to the face concentration, i.e. ${\vect \lambda}_\mmesh$, from~\eqref{asc_lambda}.
 	Further we solve numerically local subproblems in~\eqref{dual_mini} applying the mimetic FD method. This completes the solution algorithm for \eqref{dual}.
@@
 	\end{equation}
-with \toDiscuss{$\big(\vect u|_{\bcell^+}\cdot\hat{\vect n}\big)(\vect x) = u^\text{ext}_\mmesh(f)\,|f|$}, if $\vect x \in f$ for $f\in\mfaces_F(T^+)$, and $u^\text{ext}_\mmesh(f) \in \vect u^\text{ext}_\mmesh$ is the local flux assigned to $f$.
+	with $\big(\vect u|_{\bcell^+}\cdot\hat{\vect n}\big)(\vect x) = u^\text{ext}_\mmesh(f)\,|f|$, if $\vect x \in f$ for $f\in\mfaces_F(T^+)$, and $u^\text{ext}_\mmesh(f)$ is the local flux assigned to $f$ (component of~$\vect u^\text{ext}_\mmesh$).
 Similar definition applies to $\vect u|_{\bcell^-}$.
@@
 Further, denote by $\lambda_{j\,i}(\mmesh)$ the local d.o.f.
-assigned to the $i$-th mini-face belonging to the $j$-th macro-face, and by $\lambda_{j}(T)$, $\lambda_{j}'(T)$ two moments defining an element from $\Lambda$ on the $j$-th macro-face \big(see Figure~\ref{fig:asc_dofs:asc1:mmc})\big) so that
-we have for $\lambda\in\Lambda$,
+assigned to the $i$-th mini-face belonging to the $j$-th macro-face, and by $\lambda^{(0)}_{j}(T)$, $\lambda^{(1)}_{j}(T)$ two moments defining an element from $\Lambda$ on the $j$-th macro-face (see Figure~\ref{fig:asc_dofs:asc1:mmc}) so that we have
 	\begin{equation}\label{lambda_intermsof_moments}
-	{\lambda}\big({\vect r}(t)\big) = \lambda_{j}'(T)|F|\,t + \left( \lambda_{j}(T) - \frac{\lambda_{j}'(T)\,|F|}{2} \right),\qquad  F\in\bfaces[int],
+		{\lambda}\big({\vect r}(t)\big) = \lambda^{(1)}_{j}(T)\,|F|\,t + \left( \lambda^{(0)}_{j}(T) - \frac{\lambda^{(1)}_{j}(T)\,|F|}{2} \right),\qquad  F\in\bfaces[int]
 	\end{equation}
-where $t\in(0,1)$ and ${\vect r}\::\:\left(0,1\right) \rightarrow F$ is the affine parametrization of $F$, which has index $j$ among macro-faces of $T$.
+	for $\lambda\in\Lambda$. Here $t\in(0,1)$ and ${\vect r}\::\:\left(0,1\right) \rightarrow F$ is the affine parametrization of $F$, which has index $j$ among macro-faces of $T$.
 
-Integrating \eqref{lambda_intermsof_moments} over all mini-faces \toDiscuss{$f \in \mfaces_\bface(\bcell)$} ($f$ has local index $i$ among mini-faces belonging to $F$) and re-scaling, we get
+	Integrating \eqref{lambda_intermsof_moments} over all mini-faces $f \in \mfaces_\bface(\bcell)$ ($f$ has local index $i$ among mini-faces belonging to $F$) and re-scaling, we get
 	\begin{equation}\label{asc1_interp}
@@
 		\begin{cases}
-		\lambda_{j}(\bcell) +  s_{j\,i}\,\lambda'_{j}(\bcell), & \text{if}~F~\text{is a multi-material face}, \\
-		\lambda_{j}(\bcell),                                   & \text{otherwise},
+			\lambda^{(0)}_{j}(\bcell) +  s_{j\,i}\,\lambda^{(1)}_{j}(\bcell), & \text{if}~F~\text{is a multi-material face}, \\
+			\lambda^{(0)}_{j}(\bcell),                                        & \text{otherwise},
 		\end{cases}
@@
 	where $s_{j\,i} $ is a signed distance between centroids of~$f$  and~$F$.
-For the corresponding vectors of unknowns  ${\vect \lambda}_\mmesh = \{ \lambda_{j\,i}(\mmesh) \}$ and \toDiscuss{${\vect \lambda}_\bcell = \{ \lambda_{j}(\bcell) \} \cup \{ \lambda'_{j}(\bcell) \}$} this defines
+For the corresponding vectors of unknowns  ${\vect \lambda}_\mmesh = \{ \lambda_{j\,i}(\mmesh) \}$ and ${\vect \lambda}_\bcell = \{ \lambda^{(0)}_{j}(\bcell) \} \cup \{ \lambda^{(1)}_{j}(\bcell) \}$ this defines
 	the matrix $\vect R_\mmesh$ through~\eqref{asc_lambda}. For the example in Figure~\ref{fig:asc_dofs:asc1:mmc} (left), $\vect R_\mmesh$ is given by
@@
 	Now, when the mappings between local and global approximations of $\lambda$ are defined, we are ready to proceed with the assembly of the global matrix $\vect S_\bmesh$.
-	The flux continuity over the face $F$ condition ~\eqref{flux_cont} yields
+The flux continuity over the face $F$ \big(condition~\eqref{flux_cont}\big) yields
 	\begin{equation*}
@@
 	where $i$ and $j$ are the local indexes of the face $F$ in the cells $T^+$ and $T^-$, respectively.
-\toDiscuss{For} the Neumann part of the boundary we set $\mfaces_N(\bcell) \coloneqq \{ f \in \mfaces[ext](\bcell)\::\:f \subset \partial\Omega_N \}$.
+For the Neumann part of the boundary of~$\bcell^\pm$ we set $\mfaces_N(\bcell^\pm) \coloneqq \{ f \in \mfaces[ext](\bcell^\pm)\::\:f \subset \partial\Omega_N \}$.
 If $F$ from $T^+$ belongs to the Neumann part of the boundary, then we have
@@
 		\left( \vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,{\vect u}^{\text{ext}}_{\mmesh^+} \right)_i = \left( \vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,{\vect g}_{N\,\mmesh^+} \right)_i, \quad
-	{\vect g}_{N\,\mmesh^+} \coloneqq \left\{ \int_f g_N\,s_k \diff{l}\,/\,|f| \right\}_{f\,\in\,\mfaces_N(\bcell),\:k\,\in\,\{0,\,1\}}.
+		{\vect g}_{N\,\mmesh^+} \coloneqq \left\{ \int_f g_N\,s_k \diff{l}\,/\,|f| \right\}_{f\,\in\,\mfaces_N(\bcell^+),\:k\,\in\,\{0,\,1\}}.
 	\end{equation*}
@@
 	From~\eqref{local_system} it is clear that~$\vect S_\bmesh$ is sparse: Global d.o.f.
-$\lambda_m(\bmesh)$, $\lambda'_m(\bmesh)\in\vect\lambda_\bmesh$ interact only with d.o.f.
+$\lambda^{(0)}_m(\bmesh)$, $\lambda^{(1)}_m(\bmesh)$ (components of~$\vect\lambda_\bmesh$) interact only with d.o.f.
 associated with faces of macro-cells that share $m$th macro-face.
-For example, if \toDiscuss{$F\in\bfaces[int]$} is shared by two quadrilaterals and has global index $m$, then $m$th row of~$\vect S_\bmesh$ will have~$m_\text{nnz}$ nonzero elements, $7 \le m_\text{nnz} \le 14$ (for ASC(0) $m_\text{nnz} = 7$).
+For example, if $F\in\bfaces[int]$ is shared by two quadrilaterals and has global index $m$, then $m$th row of~$\vect S_\bmesh$ has at most 14 nonzero elements for ASC(1) and at most 7 for ASC(0).
 %; if $i$th base\,face is a face shared by a quadrilateral and a triangle, $i$th row of~$\vect S_\bmesh$ will have~6 nonzero elements and so forth.
@@
 Same arguments hold for ASC(0) after obvious simplifications.
-\\
 	%\begin{theorem}\label{thm:asc0}
@@
 	\begin{proof}
+		\vskip -.3cm
 		From~\eqref{asc1_interp} we have that for any cell~$\bcell$ and its mini-mesh~$\mmesh(T)$
@@
 	\end{proof}
-
+	\vskip .3cm
 	\begin{theorem} 
-	Matrix $\vect S_\bmesh$ is symmetric \toDiscuss{and non-negative definite}. If $c \ne 0$ or $|\partial\Omega_D|>0 $, then  $\vect S_\bmesh$ is positive definite.
+		Matrix $\vect S_\bmesh$ is symmetric. If $c > 0$ or $|\partial\Omega_D|>0 $, then  $\vect S_\bmesh$ is positive definite.
 	\end{theorem}
 	\begin{proof}
-	From the identity \eqref{defA} it immediately follows that $\vect A_{\mmesh}$ is symmetric and non-negative definite.
-Thus, the first statement follows from the definition of~$\vect S_\bmesh$ in \eqref{local_system}--\eqref{global_system_assembly}.
-It is easy to see that $\vect A_{\mmesh}$ is positive definite for all~$\bcell$, where $c \ne 0$.
-Hence if $c \ne 0$ in $\Omega$, then \eqref{local_system}--\eqref{global_system_assembly} and the full ranks of $\vect R_\mmesh$'s and $\vect C_\mmesh$'s imply the positive definiteness of $\vect S_\bmesh$.
+		\vskip -.3cm
+		First, noting that for any two symmetric positive definite matrices $\vect A_1$ and $\vect A_2$ inequality $\vect A_1 \ge \vect A_2$ implies $\vect A_1^{-1} \le \vect A_2^{-1}$, we conclude 
+		\begin{equation}\label{aux2}
+			\widetilde{\vect B}^T \left( \vect \Sigma+ \widetilde{\vect B}\,\widetilde{\vect B}^{T}\right)^{-1} \widetilde{\vect B}
+			\le
+			\widetilde{\vect B}^T \left(\widetilde{\vect B}\,\widetilde{\vect B}^{T}\right)^{-1} \widetilde{\vect B} \le \vect I,
+		\end{equation}
+		where $\vect \Sigma$ is any symmetric and non-negative definite matrix, $\widetilde{\vect B}$ is any matrix such that \\ ${\Ker\widetilde{\vect B}^T = \{ \vect 0 \}}$, and $\vect I$ is identity matrix.
+To check the last inequality in~\eqref{aux2}, one can consider, e.g., the SVD decomposition of $\widetilde{\vect B}$.
+
+		From the identities~\eqref{defA} and~\eqref{aux2} with $\widetilde{\vect B}^T \coloneqq \vect M^{-\frac12}_\mmesh\,\vect B_\mmesh^T$, $\vect \Sigma \coloneqq \vect \Sigma_\mmesh$ it immediately follows that $\vect A_{\mmesh}$ is symmetric and non-negative definite.
+The symmetry of $\vect S_\bmesh$ follows from the definition in \eqref{local_system}--\eqref{global_system_assembly}.
+		By similar considerations, it is easy to see that $\vect A_{\mmesh}$ is positive definite for all~$\bcell$, where $c > 0$.
+Hence if $c > 0$ in $\Omega$ , then \eqref{local_system}--\eqref{global_system_assembly} and the full ranks of $\vect R_\mmesh$'s and $\vect C_\mmesh$'s imply
+		the positive definiteness of $\vect S_\bmesh$.
+
 		Now we show the positive definiteness of $\vect S_\bmesh$ if $|\partial\Omega_D|>0 $. Consider  any given $\bcell\in\bmesh$.
@@
 		If $\partial\bcell\cap\partial\Omega_D$, then $\Ker \vect A_{\mmesh} = \{\vect 0\}$.
-Otherwise $\mbox{dim}(\Ker \vect A_{\mmesh})=1$ and $\vect A_{\mmesh}\,\vect C_{\mmesh}\,\vect\lambda_\mmesh=0$ implies that $\vect\lambda_\mmesh$ is constant on $\partial\bcell$.
+Otherwise $\Dim\big(\Ker \vect A_{\mmesh}\big) = 1$ and $\vect A_{\mmesh}\,\vect C_{\mmesh}\,\vect\lambda_\mmesh=0$ implies that $\vect\lambda_\mmesh$ is constant on $\partial\bcell$.
 Consider some $\lambda$ from the mortar space $\Lambda$ and corresponding vector of moments  $\vect \lambda_\bmesh$.
-Using connectivity of the mesh one easily finds that \toDiscuss{$\vect R_\mmesh\,\vect\lambda_\mmesh$} can be constant on every $T\in\bmesh$ only if $\lambda$ is constant.
+Using connectivity of the mesh one easily finds that $\vect R_\mmesh\,\vect\lambda_\bcell$ can be constant on every $T\in\bmesh$ only if $\lambda$ is constant.
 Due to the assumption $|\partial\Omega_D|>0$ this implies $\lambda=0$.

### 2018-11-27 num_sec.tex
Fix directory path for images

@@
 			\centering
-			\includegraphicsw{transient2.1/movie_frames/arithmetic_homo/frame_1s43.png}
+			\includegraphicsw{transient2-1/movie_frames/arithmetic_homo/frame_1s43.png}
 			\caption{Arithmetic homo.}	
@@
 			\centering
-			\includegraphicsw{transient2.1/movie_frames/harmonic_homo/frame_1s43.png}
+			\includegraphicsw{transient2-1/movie_frames/harmonic_homo/frame_1s43.png}
 			\caption{Harmonic homo.}	
@@
 			\centering
-			\includegraphicsw{transient2.1/movie_frames/asc0/frame_1s43.png}
+			\includegraphicsw{transient2-1/movie_frames/asc0/frame_1s43.png}
 			\caption{ASC(0)}
@@
 			\centering
-			\includegraphicsw{transient2.1/movie_frames/asc1/frame_1s43.png}
+			\includegraphicsw{transient2-1/movie_frames/asc1/frame_1s43.png}
 			\caption{ASC(1)}	
@@
 			\centering
-			\includegraphicsw{transient2.1/movie_frames/asc_diff/frame_1s43.png}
+			\includegraphicsw{transient2-1/movie_frames/asc_diff/frame_1s43.png}
 			\caption{ASC(0,\,1) difference}	
@@
 	%% 		\centering
-	%% 		\includegraphicsw{transient2.1/movie_slices_frames/frame_0s25.png}
+	%% 		\includegraphicsw{transient2-1/movie_slices_frames/frame_0s25.png}
 	%% 		\caption{Coarse mesh, $t = 0.25$}
@@
 	%% 		\centering
-	%% 		\includegraphicsw{transient2.1/movie_slices_frames/frame_1s50.png}
+	%% 		\includegraphicsw{transient2-1/movie_slices_frames/frame_1s50.png}
 	%% 		\caption{Coarse mesh, $t = 1.50$}	
@@
 			\centering
-			\includegraphicsw{transient2.1/l2err.png}
+			\includegraphicsw{transient2-1/l2err.png}
 			\caption{Coarse mesh}

### 2018-11-27 asc.tex
Motivate discrete l2-norm, polish numerical section

@@
 \newcommand{\PnSpace}[2]{{\mathbb P^{#1}\left({#2}\right)}}
+\newcommand{\HSpace}[1]{{\mathbb H^{#1}\left(\Omega\right)}}
 
@@
 			\includegraphicsw{ring_base_voronoi.png}
-			\caption{Base Mesh}
+			\caption{Base mesh}
 			\label{fig:problem_geometry:base_mesh}
@@
 multi-material cells (central); The piecewise-planar discontinuous reconstruction of the interfaces by the moment-of-fluid method (right).
-Everything is shown for two refinement level of the base mesh.
-\label{fig:problem_geometry}}
+Everything is shown for two refinement level of the base mesh \label{fig:problem_geometry}}
 	\end{figure}
@@
 			\includegraphics[width=0.3\textwidth]{./ring_mini_voronoi_cell.png}%{./Pictures/mainscreen1.png}
-			\caption{Local polyhedral mesh for a three-material cell $T\in\bmesh$.\label{fig:mmesh}}
+			\caption{Local polyhedral mesh for a three-material cell $T\in\bmesh$ \label{fig:mmesh}}
 		\end{center}

### 2018-11-27 num_sec.tex
Motivate discrete l2-norm, polish numerical section

@@
 
-We define \textit{discrete} $\LTwo$\,--\,norm of $v \in \mathbb V_h \subset \LTwoSpace$
+Let $h$ be a max cell diameter for the macro-mesh~$\bmesh_h$, and $\mathbb V_h \subset \LTwoSpace$ be a space of piecewise constant
+functions on each cell~$\mcell \in \mmesh(\bcell)$, $\bcell \in \bmesh_h$. We define \textit{discrete} $\LTwo$-norm of $v \in \LTwoSpace$ as
 \begin{equation}\label{l2}
@@
 \end{equation}
-where $P_h \coloneqq$ $\LTwo$\,--\,projection operator on the space of piecewise constant
-functions on each mesh element~$\bcell \in \bmesh_h$ (or on each~$\mcell \in \mmesh_h$
-if $\bcell$ is a  multi-material cell).
+where $P_h\;:\;\LTwoSpace\rightarrow\mathbb V_h$ is $\LTwo$-projection operator.
 
-The the discretization error $e_h = p - p_h$ is defined as:
+For the error~$e_h \coloneqq p - p_h$ between the exact and computed solutions we have
+\begin{equation}\label{l2norm}
+	\errlTwo{h} \coloneqq \| e_h \|_{\lTwoSpace} = \| p - p_h \|_{\lTwoSpace} = \| P_h\,p - P_h\,p_h \|_{\LTwoSpace} = \| P_h\,p - p_h \|_{\LTwoSpace}
+\end{equation}
+since~$P_h$ is linear and~$p_h \in \mathbb V_h$. The discrete norm~\eqref{l2norm} of the discretization error is computed as follows:
+$$
+	\errlTwo{h} = \left[\sum\limits_{\bcell \in \bmesh_h}\sum\limits_{\mcell\in\mmesh(\bcell)} \left(\frac{1}{|\mcell|}\int_{\mcell} p \diff{\vect x} - p_h(\mcell)\right)^2|\mcell|\right]^\frac12,
+$$
+where $|\mcell|$ is the area of cell $\mcell$.
 
-\begin{equation*}
-  \errlTwo{} =  \|e_h  \|_{\lTwoSpace} = \| P_h\,p - P_h\,p_h \|_{\LTwoSpace} = \| P_h\,p - p_h \|_{\LTwoSpace}
-\end{equation*}
-\noindent since~$P_h$ is linear and~$p_h \in \mathbb V_h$.  Then the discrete norm of the discretization error is computed as follows:
+If~$\bmesh_h$ consists of triangles and no material interfaces are present, ASC($n$) boils down to mixed-hybrid Raviart\,--\,Thomas finite element method (which is algebraically equivalent to~$R\,T_0$ finite element method).
+In this particular case we have~\cite{M2AN_1980__14_3_249_0}
 $$
-\errlTwo{} = \left[\sum\limits_{\bcell \in \bmesh_h}\sum\limits_{\mcell\in\mmesh_h(\bcell)} \left(\frac{1}{|\mcell|}\int_{\mcell} p \,{\rm dx} - p_{\mcell}\right)^2|\mcell|\right]^2,
+	\|\vect u - \vect u_h\|_{\LTwoSpace} \le c\,h\,\|\vect u\|_{\HSpace{1}},\quad\|p - p_h\|_{\LTwoSpace} \le c \left( h\,\|p\|_{\HSpace{1}} + h^2\,\|p\|_{\HSpace{2}} \right),
 $$
-where $|\mcell|$ is
-the area of cell $\mcell$.
+so one cannot expect ASC($n$) $\LTwo$-convergence to be better than linear. Note that
+\begin{equation}\label{l2L2}
+	\| p - p_h \|_{\lTwoSpace} \le \| p - p_h \|_{\LTwoSpace}
+\end{equation}
+since $\| p - p_h \|_{\lTwoSpace} = \| P_h\,(p - p_h) \|_{\lTwoSpace} \le \|P_h\|_{\mathcal L(\LTwoSpace, \mathbb V_h)} \| p - p_h \|_{\LTwoSpace}$, and the operator norm~$\|P_h\|_{\mathcal L(\LTwoSpace, \mathbb V_h)} = 1$ by Pythagorean theorem.
+Thus one may expect some improvement in $\lTwo$-convergence as one increases~$n$ for ASC($n$).
 
@@
 	\end{subfigure}
-		\caption{Material distribution for pseudo-multi-material problem 2-materials(left), 3-materials(right) \label{fig:fake}}		
+	\caption{Material distribution for pseudo-multi-material problem: two materials (left), three materials (right)
+	\label{fig:fake}}		
 \end{figure}
@@
 The first set of tests is designed to check the property of the method to accurately recover the solution that is the polynomial of degree~1.
-Let us consider the diffusion problem~\eqref{dual} with~$c \equiv f \equiv 0$,
-$\partial\Omega_D = \partial\Omega$. The computational domain $\Omega=[0,1]^2$
-is divided into several subdomains by nonintersecting straight lines.
-In these settings the interface reconstruction algorithm MOF reconstructs
-the interfaces exactly. To test the {\it linearity preservation} property,
- we set up a pseudo-multi-material problem with the diffusion tensor being the
- same in all subdomains, $\vect K_i = \vect I$ .
- The exact solution a linear function. The geometry of two cases under consideration is shown in Figure~
-\ref{fig:fake}.
+Let us consider the diffusion problem~\eqref{dual} with~$c \equiv f \equiv 0$, $\partial\Omega_D = \partial\Omega$.
+The computational domain $\Omega=(0,1)^2$ is divided into several subdomains by non-intersecting straight lines.
+In these settings the interface reconstruction algorithm MOF reconstructs the interfaces exactly.
+To test the {\it linearity preservation} property, we set up a pseudo-multi-material problem with the diffusion tensor being the same in all subdomains, $\vect K_i = \vect I$.
+The exact solution a linear function.
+The geometry of two cases under consideration is shown in Figure~\ref{fig:fake}.
 
-	We denote
-        %the exact pressure solution by~$p$ and
-        the solution computed  with the ASC($n$) method by~$p_{h,\,n}$, $n = 0, 1$.
-
-        For ASC(0) we have~$\errlTwo{0} = 6.38 \times 10^{-2}$ and $6.41 \times 10^{-2}$ for the configurations shown in Figures~\ref{fig:fake:2} and~\ref{fig:fake:3}, respectively.
+We denote the solution computed  with the ASC($n$) method by~$p_{h,\,n}$, $n = 0, 1$.
+For ASC(0) we have~$\errlTwo{h,\,0} = 6.38 \times 10^{-2}$ and $6.41 \times 10^{-2}$ for the configurations shown in Figures~\ref{fig:fake:2} and~\ref{fig:fake:3}, respectively.
 That is, ASC(0) is not able to recover $P_1$ solutions exactly.
 
-	Since ASC(1) approximates interface traces with $P_1$ functions
-        it recovers edge-based degrees of freedom exactly in the sense of mean values. This results in exact reconstruction
-        of cell-based unknowns and {\it linearity preservation} property for both examples, i.e.,
+Since ASC(1) approximates interface traces with $P_1$ functions it recovers edge-based degrees of freedom exactly in the sense of mean values.
+This results in exact reconstruction of cell-based unknowns and {\it linearity preservation} property for both examples, i.e.
 \begin{equation*}
-		\errlTwo{1} = \left\| p - p_{h,\,1} \right\|_{\lTwoSpace} = 0.
+	\errlTwo{h,\,1} = \left\| p - p_{h,\,1} \right\|_{\lTwoSpace} = 0.
 \end{equation*}
-
-	%% As we saw in previous section,
-        In general, one may not expect concentration and flux convergence to be better than second order with respect to~$\lTwo$\,--\,error for ASC($1$).
+% As we saw in previous section,
+%In general, one may not expect concentration and flux convergence to be better than second order with respect to~$\lTwo$\,--\,error for ASC($1$).
 However, taking the example above into account, one may expect that convergence of ASC(1) with respect to~$\lTwo$-norm is superior
-        to  convergence properties of ASC(0).
+%to  convergence properties of ASC(0).
 
@@
 
-        In this set of tests, we consider the diffusion problem~\eqref{dual} with~$c = f = 0$, $\partial\Omega_D = \partial\Omega$,
-        and two different materials in the domain.
+In this set of tests, we consider the diffusion problem~\eqref{dual} with~$c \equiv f \equiv 0$, $\partial\Omega_D = \partial\Omega$, and two different materials in the domain.
 $\vect K = k\,\vect I$, $k = 1$ in the left part of the domain and $k = 0.1$ in the right (see Figure~\ref{fig:pwlin:mat}).
@@
 
-	For this example we use a sequence of square base\,meshes~$\bmesh_i$, $i = 1, 2, 3, 4$; $h_i \coloneqq$ max diameter of the cell. We denote by
+For this example we use a sequence of square base\,meshes~$\bmesh_{h_i}$, $i = 1, 2, 3, 4$. We denote by
 \begin{equation*}
-		\rho_{n,\,i} \coloneqq \frac{\log \errlTwo{n,\,i} / \errlTwo{n,\,i+1}}{\log h_i / h_{i+1}}
+	\rho_{h_i,\,n} \coloneqq \frac{\ln \errlTwo{h_i,\,n} / \errlTwo{h_{i+1},\,n}}{\ln h_i / h_{i+1}}
 \end{equation*}
-the reduction rate order of ASC($n$) in ~$\lTwo$\,-\,norm between $i$ and $i+1$ refinement step. We also compute the $\ell^{\infty}$-norm of the error
+the reduction rate order of ASC($n$) in~$\lTwo$-norm between $i$th and $(i+1)$th refinement steps. We also compute the $\ell^{\infty}$-norm of the error
 \begin{equation*}
-		\errInf{n,\,i} \coloneqq \left\| p - p_{h_i,\,n} \right\|_\infty
+	\errInf{h_i,\,n} \coloneqq \left\| p - p_{h_i,\,n} \right\|_\infty
 \end{equation*}
@@
 
-	\begin{table}[h!]\small
+\begin{table}[h!]
 	\centering
 	\caption{Piecewise linear example: convergence \label{fig:conv:pwlin}}
+	\footnotesize
 	\begin{tabular}[1.5]{| c | c || c | c || c |}
@@
 Numerical results are shown in Table~\ref{fig:conv:pwlin}.
-We observe that ASC(0) converges linearly with respect to $\lTwo$-norm, and ASC(1) has the convergence rate close to quadratic with respect to the $\lTwo$-norm.
+We observe that ASC(0) converges linearly with respect to the $\lTwo$-norm, and ASC(1) has the convergence rate close to quadratic with respect to the $\lTwo$-norm.
 
@@
 
-	\subsubsection{Two Materials}\label{sec:twomat}
+\subsubsection{Two materials}\label{sec:twomat}
 
@@
 
-	Let us consider the diffusion problem~\eqref{dual} with~$c = 0$,
-        $\partial\Omega_D = \partial\Omega$. The computational domain is divided into
-        subdomains: $\Omega_1 = \{ {\bf x} : \|{\bf x} - {\bf x}_0\|< 0.25,~
-        {\bf x}_0 = (0.5,0.5)\}$ and  $\Omega_2 = [0,1]^2 / \Omega_1$.
-        The diffusion tensor is set  $\vect K_i = k_i\,\vect I$ in $\Omega_i$,
-        $k_1 = 0.001$ and $k_2=1$. The exact solution is piecewise quadratic such
-        that the normal flux is continuous across the interface (see Figure~\ref{fig:pwquad2}).
-        For this problem, we compared convergence properties of the  ASC(0) and ASC(1) methods
-        on a sequence of Voronoi meshes.
+Let us consider the diffusion problem~\eqref{dual} with~$c \equiv 0$, $\partial\Omega_D = \partial\Omega$.
+The computational domain is divided into subdomains: $\Omega_1 = \{ {\bf x} : \|{\bf x} - {\bf x}_0\|< 0.2\}$ with~${\bf x}_0 = (0.5,0.5)$ and $\Omega_2 = (0,1)^2 \setminus \bar{\Omega}_1$.
+The diffusion tensor is set to be $\vect K_i = k_i\,\vect I$ in $\Omega_i$, $k_1 = 0.001$ and $k_2=1$.
+The exact solution is piecewise quadratic such that the normal flux is continuous across the interface (see Figure~\ref{fig:pwquad2}).
+For this problem we compare convergence properties of the  ASC(0) and ASC(1) methods on a sequence of Voronoi meshes.
 
-	\begin{table}[h!]\small
+\begin{table}[h!]
 	\centering
 	\caption{Piecewise quadratic example, two materials: convergence \label{tab:conv:pwquad2}}
-		\begin{tabular}[1.5]{| c | c || c | c || c |}
+	\footnotesize
+	\begin{tabular}[1.1]{| c | c || c | c || c |}
 		\hline
@@
 		\hline
+	\end{tabular}
+	\begin{tabular}[1.1]{| c | c || c | c || c |}
 		\hline
@@
 The norms of the errors are shown in Table~\ref{tab:conv:pwquad2}.
- ASC(1) demonstrates  convergence with the  rate in the $\lTwo$-norm close to quadratic.  ASC(0) convergence rate  fluctuates significantly.
+ASC(1) demonstrates convergence with the rate in the $\lTwo$-norm close to quadratic.
+ASC(0) convergence rate fluctuates significantly.
 
-        We also observe a bump in the max norm error for ASC(1) on the second mesh level,
-        $h = 1.5\times10^{-1}$. To have some insight, we show the corresponding mesh in the Figure~\ref{fig:conv:pwquad2:inf:mesh}.
-        One may note that the interface reconstruction produces significant discontinuity of
-        interfaces: A small volume of the external material, i.e. the one occupying $\Omega_2$ domain, appears
-        inside the disk, domain $\Omega_1$. Due to constant trace approximation, ASC(0)
-        is not sensitive to such  irregularity.
+We also observe a bump in the max norm error for ASC(1) on the second mesh level, $h = 1.5\times10^{-1}$.
+To have some insight, we show the corresponding mesh in the Figure~\ref{fig:conv:pwquad2:inf:mesh}.
+One may note that the interface reconstruction produces significant discontinuity of interfaces: A small volume of the external material, i.e.
+the one occupying $\Omega_2$ domain, appears inside the disk (domain $\Omega_1$).
+Due to constant trace approximation, ASC(0) is not sensitive to such irregularity.
 It turns out that for ASC(1) the $\ell^\infty$ norm of the error is affected by the appearance of such small isolated cut cells.
-At the same time, this  %as expected,
-        does not affect the $\lTwo$-convergence of ASC(1).
+At the same time, this does not affect the $\lTwo$-convergence of ASC(1).
 
-        \begin{figure}
+\begin{figure}[h]
 	\centering
@@
 	\end{subfigure}%
-\hskip1ex
+	\hskip .6cm
 	\begin{subfigure}{.33\linewidth}
@@
 This figure illustrates the appearance of small isolated material volumes during numerical reconstruction of material interfaces.
-This may affect the $\ell^\infty$ error norm of the ASC(1).}
+This may affect the $\ell^\infty$ error norm of the ASC(1)}
 \end{figure}
 
-%	\clearpage
-
-	\subsubsection{Three Materials}\label{sec:threemat}
+\subsubsection{Three materials}\label{sec:threemat}
 
@@
 
-	In the next group of numerical tests, we consider the same  diffusion problem~\eqref{dual}
-        with~$c = 0$, $\partial\Omega_D = \partial\Omega$. The computational domain is now
-        divided into three subdomains: $\Omega_1 = \{{\bf x} : \|{\bf x} - {\bf x}_0\| < 0.2$,
-        $\Omega_2 = \{{\bf x} : 0.2 \le \|{\bf x} - {\bf x}_0\| < 0.25$, and
-        $\Omega_3 = [0,1]^2 / (\Omega_1\cup\Omega_2)$. The diffusion tensor is set to be
-        $\vect K_i = k_i\,\vect I$, $k_{1} = k_{3} = 1$, $k_2 = 0.001$.
-        The geometry represents a ring with $k_2=0.001$ inside the ring and $k_{1} = k_{3} = 1$ outside
-        the ring. The exact solution is piecewise quadratic such that the normal flux is
-        continuous across the interface; see Figure~\ref{fig:pwquad3}.
+In the next group of numerical tests, we consider the same  diffusion problem~\eqref{dual} with~$c \equiv 0$, $\partial\Omega_D = \partial\Omega$.
+The computational domain is now divided into three subdomains: $\Omega_1 = \{{\bf x} : \|{\bf x} - {\bf x}_0\| < 0.15\}$, $\Omega_2 = \{{\bf x} : 0.15 < \|{\bf x} - {\bf x}_0\| < 0.2\}$, and $\Omega_3 = (0,1)^2 \setminus (\bar{\Omega}_1\cup\bar{\Omega}_2)$.
+The diffusion tensor is set to be $\vect K_i = k_i\,\vect I$, $k_{1} = k_{3} = 1$, $k_2 = 0.001$.
+The geometry represents a ring with $k_2=0.001$ inside the ring and $k_{1} = k_{3} = 1$ outside the ring.
+The exact solution is piecewise quadratic such that the normal flux is continuous across the interface; see Figure~\ref{fig:pwquad3}.
 We use a sequence of triangular meshes to study convergence for this example.
@@
 	\end{tabular}
-	  \centering
 	\begin{tabular}[1.1]{c | c | c || c | c || c |}
@@
 	  \end{tabular}
-
 \end{table}
@@
 We compare ASC(0), ASC(1), arithmetic, and harmonic homogenization.
-        Note that up to mesh level~$h = 8.3\times10^{-2}$ base\,
-        faces with three materials are present, and starting from %
-        {$h = 6.7\times10^{-2}$} the meshes are fine
-        enough so that only   macro-faces sharing one or two materials occur.
+Note that up to mesh level~$h = 8.3\times10^{-2}$ macro-faces with three materials are present, and starting from {$h = 6.7\times10^{-2}$} the meshes are fine enough so that only macro-faces sharing one or two materials occur.
 
-	We see that ASC(0) starts to converge linearly with respect to $\lTwo$-error
-        once~$h < 6.7\times10^{-2}$. ASC(1) demonstrates a robust behaviour and shows the convergence
-        rate close to quadratic with respect to $\lTwo$-error as in previous examples,
-        and performs better than homogenization approaches.
+We see that ASC(0) starts to converge linearly with respect to $\lTwo$-norm once~$h < 6.7\times10^{-2}$.
+ASC(1) demonstrates a robust behavior and shows the convergence rate close to quadratic with respect to $\lTwo$-norm as in previous examples, and performs better than homogenization approaches.
 
@@
 %	
-
-	In this section, we study the dependence of the condition number of matrix $S_\bmesh$ on the position of the material interface against the background mesh.
+In this section, we study the dependence of the condition number of matrix $\vect S_\bmesh$ on the position of the material interface against the background mesh.
 For this purpose, we solve the diffusion problem~\eqref{dual} in the unit square with $\partial\Omega = \partial\Omega_D$, $\vect K = k\,\vect I$, $k = 1$ on the left part and $k = 0.1$ on the right.
@@
 		\hline
-			\end{tabular}
+	\end{tabular}%
 	%	\hfill
@@
 Numerical results are shown in Table~\ref{fig:w:res}.
-We observe that the condition number~$\kappa_{\text{ASC(0)}}$ of $S_\bmesh$ for ASC(0) levels off if $w$ gets smaller.
+We observe that the condition number~$\kappa_{\text{ASC(0)}}$ of $\vect S_\bmesh$ for ASC(0) levels off if $w$ gets smaller.
 The condition number~$\kappa_{\text{ASC(1)}}$ of ASC(1) depends on $w$ and behaves as $O(w^{-1})$ for $w\to0$.
-A closer look at the spectrum of      $S_\bmesh$  reveals that the growth of the condition
-number for    ASC(1) is due to presence of only few (three for this example) small eigenvalues, which tend to zero.
-To illustrate this, Table~\ref{fig:w:res} shows the ``effective'' condition number of $S_\bmesh$ that is defines
-as
+A closer look at the spectrum of~$\vect S_\bmesh$ reveals that the growth of the condition number for ASC(1) is due to presence of only few (three for this example) small eigenvalues, which tend to zero.
+To illustrate this, Table~\ref{fig:w:res} shows the ``effective'' condition number of $\vect S_\bmesh$ that is defined as
 $$
@@
 $$
-	where  $\mu_{\text{min}}^1 = \mu_0 \ge \mu_1 \ge \dots \ge \mu_{\text{max}}$ are the eigenvalues of~$\vect S_\bmesh$ of ASC(1).
+where $\mu_{\text{min}} = \mu_0 \ge \mu_1 \ge \dots \ge \mu_{\text{max}}$ are the eigenvalues of~$\vect S_\bmesh$ of ASC(1).
 From this results we see that the effective condition number of ASC(1) stays bounded with respect to the interface position and is  close to the condition number of ASC(0).
@@
 It is well-known that the presence of a few outliers in the spectrum does not affect the asymptotic convergence of the conjugate gradient (CG) iterative methods, see, e.g., \cite{olshanskii2014iterative}.
-Indeed, in our experiments the CG method was found to be equally effective for solving systems of algebraic equations resulting from ASC(0) and ASC(1).
+Indeed, in our experiments the CG method (with algebraic multigrid preconditioner) was found to be equally effective for solving systems of algebraic equations resulting from ASC(0) and ASC(1).
 %Starting from some iteration CG method behaves like extreme eigenvalues are not present in the spectrum.
@@
 
-	We finally apply the ASC methods to simulate the time dependent diffusion problem.  In the mixed form, the problem reads
+We finally apply the ASC methods to simulate the time-dependent diffusion problem. In the mixed form, the problem reads
 \begin{equation}\label{dual_transient}
-		\left\{\begin{split}
-			\vect K^{-1}\,\vect u &+ \nabla\,p\,&= 0&\quad\text{in } \Omega , \\
-			\nabla\cdot\vect u    &+ \frac{\partial}{\partial t}\,p       &= f&\quad\text{in } \Omega,
-		\end{split}\right.
-\end{equation}
-for   $t\in(0, T]$ with initial data $p(\vect x, 0) = p_0(\vect x)$ and
-boundary data as in \eqref{dual:bc:neumann}.
+	\arraycolsep=2pt\def\arraystretch{1.7}
+	\left\{\begin{array}{rcrccl}
+		\vect K^{-1}\,\vect u & + & \nabla\,p & = & 0 &\quad\text{in } \Omega , \\
+		\nabla\cdot\vect u    & + & \frac{\partial}{\partial t}\,p      & = & f &\quad\text{in } \Omega
+	\end{array}\right.
+\end{equation}%
+%\begin{equation}\label{dual_transient}
+%		\left\{\begin{split}
+%			\vect K^{-1}\,\vect u &+ \nabla\,p\,&= 0&\quad\text{in } \Omega , \\
+%			\nabla\cdot\vect u    &+ \frac{\partial}{\partial t}\,p       &= f&\quad\text{in } \Omega,
+%		\end{split}\right.
+%\end{equation}
+for $t\in(0, T]$ with initial data $p(\vect x, 0) = p_0(\vect x)$ and boundary data as in \eqref{dual:bc:neumann}.
 After discretizing in time by the implicit Euler method, the problem takes the form \eqref{dual}--\eqref{dual:bc:neumann} with $c=|\Delta t|^{-1}$ and we apply the spacial discretization described in section~\ref{sec:ASC}.
@@
 The computational domain is the same as in section~\ref{sec:threemat} with the example of three different materials.
-$\Omega = \Omega_1 \cup \Omega_2 \cup \Omega_3$ is divided into three subdomains: $\Omega_1 = \{\vect x \in \Rn{2} : \|{\bf x} - {\bf x}_0\| \ge 0.2\}$,
-	$\Omega_2 = \{\vect x \in \Rn{2} : 0.15 \le \|{\bf x} - {\bf x}_0\| \le 0.2\}$, $\vect x_0 = (0.5, 0.5)$, and $\Omega_3 = (0,1)^2 \setminus (\Omega_1\cup\Omega_2)$.
-The diffusion tensor is set as $\vect K_i = k_i\,\vect I$, $k_1 = 1, k_2 = 0.002$, and $k_3 = 10$.
+$\Omega_1 = \{{\bf x} : \|{\bf x} - {\bf x}_0\| < 0.15\}$, $\Omega_2 = \{{\bf x} : 0.15 < \|{\bf x} - {\bf x}_0\| < 0.2\}$, and $\Omega_3 = (0,1)^2 \setminus (\bar{\Omega}_1\cup\bar{\Omega}_2)$.
+The diffusion tensor is set as $\vect K_i = k_i\,\vect I$, $k_1 = 10, k_2 = 0.002$, and $k_3 = 1$.
 
 We prescribe Dirichlet boundary data $g_D = 1$ on the left side of the unit square, while right, top, and bottom sides are prescribed no-flux boundary condition, $g_N \equiv 0$.
-The external source term is zero, $f= 0$.
+The external source term is zero, $f \equiv 0$.
 The initial concentration is set to be
 \begin{equation*}
-		p_0(\vect x) = (1 - \vect x)^{10}.	
+	p_0(x,\,y) = (1 - x)^{10}.	
 \end{equation*}
@@
 		\includegraphicsw{transient2/ref_slices.png}
-			\caption{Cuts~$p_*\left((x,0.5), t\right)$ of the reference solution}	
+		\caption{Cuts~$p_*\big((x,0.5), t\big)$ of the reference solution}	
 	\end{subfigure}%
@@
 This solution was found to be (almost) mesh independent and will serve as the  reference solution.
-The center cutline profiles ~$p_*\left((x,0.5), t\right)$   are shown in the Figure~\ref{fig:transient:ref} (right) for several values of~$t \in (0, T]$.
+The center cutline profiles~$p_*\big((x,0.5), t\big)$   are shown in the Figure~\ref{fig:transient:ref} (right) for several values of~$t \in (0, T]$.
 
 For ASC(0), ASC(1), arithmetic and harmonic homogenization methods we use two Voronoi meshes with~$h = 1.5 \times 10^{-1}$ (124 base\,cells) and $h = 8.1 \times 10^{-2}$ (465 base\,cells).
-          The coarse mesh contains 20 multi-material cells and two macro-face sharing three materials.
+The coarse mesh contains 20 multi-material cells and two macro-faces sharing three materials.
 The fine mesh contains 50 multi-material cells and no three material macro-faces.
@@
 Results are shown in Figures~\ref{fig:transient:comp}\,--\,\ref{fig:transient:err}.
+
+\clearpage
 
@@
 	\end{subfigure}%
-\caption{Comparison of the discrete solutions~$p_h$ for~$h = 1.5 \times 10^{-1}$, $t = 1.25$. \label{fig:transient:comp}}
+	\caption{Comparison of the discrete solutions~$p_h$ for~$h = 1.5 \times 10^{-1}$, $t = 1.25$ \label{fig:transient:comp}}
+ 	\centering
+ 	\vskip 1cm
+ 	\begin{subfigure}{.45\linewidth}
+ 		\centering
+ 		\includegraphicsw{transient2-1/movie_slices_frames/frame_0s25.png}
+ 		\caption{Coarse mesh, $t = 0.25$}
+ 	\end{subfigure}%
+ 	\hfill
+ 	\begin{subfigure}{.45\linewidth}
+ 		\centering
+ 		\includegraphicsw{transient2-1/movie_slices_frames/frame_1s50.png}
+ 		\caption{Coarse mesh, $t = 1.50$}	
+ 	\end{subfigure}%
+ 	\par
+ 	\begin{subfigure}{.45\linewidth}
+ 		\centering
+ 		\includegraphicsw{transient2/movie_slices_frames/frame_0s25.png}
+ 		\caption{Fine mesh, $t = 0.25$}
+ 	\end{subfigure}%
+ 	\hfill
+ 	\begin{subfigure}{.45\linewidth}
+ 		\centering
+ 		\includegraphicsw{transient2/movie_slices_frames/frame_1s50.png}
+		\caption{Fine mesh, $t = 1.50$}	
+	\end{subfigure}%
+	\caption{Comparison of the cuts~$p_h\big((x,0.5), t\big)$ of discrete solutions for coarse and fine meshes, $h = 1.5 \times 10^{-1}$ and $h = 8.1 \times 10^{-2}$ 		\label{fig:transient:cuts}}
 \end{figure}
 
-	%% \begin{figure}[h]
-	%% 	\centering
-	%% 	\begin{subfigure}{.45\linewidth}
-	%% 		\centering
-	%% 		\includegraphicsw{transient2-1/movie_slices_frames/frame_0s25.png}
-	%% 		\caption{Coarse mesh, $t = 0.25$}
-	%% 	\end{subfigure}%
-	%% 	\hfill
-	%% 	\begin{subfigure}{.45\linewidth}
-	%% 		\centering
-	%% 		\includegraphicsw{transient2-1/movie_slices_frames/frame_1s50.png}
-	%% 		\caption{Coarse mesh, $t = 1.50$}	
-	%% 	\end{subfigure}%
-	%% 	\par
-	%% 	\begin{subfigure}{.45\linewidth}
-	%% 		\centering
-	%% 		\includegraphicsw{transient2/movie_slices_frames/frame_0s25.png}
-	%% 		\caption{Fine mesh, $t = 0.25$}
-	%% 	\end{subfigure}%
-	%% 	\hfill
-	%% 	\begin{subfigure}{.45\linewidth}
-	%% 		\centering
-	%% 		\includegraphicsw{transient2/movie_slices_frames/frame_1s50.png}
-	%% 		\caption{Fine mesh, $t = 1.50$}	
-	%% 	\end{subfigure}%
-	%% 	\caption{Comparison of the cuts~$p_h((x,0.5), t)$ of discrete solutions for coarse and fine meshes, $h = 1.5 \times 10^{-1}$ and $h = 8.1 \times 10^{-2}$. 		\label{fig:transient:cuts}}
-	%% \end{figure}
+\clearpage
 
@@
 	\end{subfigure}%
-		\caption{$\lTwo$-norm of the error computed for the inclusion~$\Omega_2 \cup \Omega_3$ for coarse and fine meshes, $h = 1.5 \times 10^{-1}$ and $h = 8.1 \times 10^{-2}$. \label{fig:transient:err}}
+	\caption{$\lTwo$-norm of the error computed for the inclusion~$\Omega_1 \cup \Omega_2$ for coarse and fine meshes, $h = 1.5 \times 10^{-1}$ and $h = 8.1 \times 10^{-2}$ \label{fig:transient:err}}
 \end{figure}
@@
 From the figures it is easy to appreciate  that among all the methods only  ASC(1)  provides a reasonable approximation for the coarse mesh, cf. Figures~\ref{fig:transient:comp}.
-        %and~\ref{fig:transient:cuts}
 Numerical solution computed with ASC(0) overestimates incoming fluxes for the ring.
-This solution converges to the equilibrium state~$p_h \approx 1$ at approximately $t = 3.75$, which is significantly earlier than the time when same state is achieved by the reference solution  for the same coarse mesh.
-Note that the coarse mesh contains faces with three materials, and we saw already that ASC(0) may fail to converge for this case even for stationary examples\footnotemark{}.
-	%
+This solution converges to the equilibrium state~$p_h \approx 1$ at approximately $t = 3.75$, which is significantly earlier than the time when same state is achieved by the reference solution.
+Note that the coarse mesh contains faces with three materials, and we saw already that ASC(0) may fail to converge for this case even for stationary examples.
+
+We tried replacing Voronoi mesh with a triangulation such that the number of triangles is close to the number of the polygonal cells in the fine Voronoi mesh (456 elements for the triangular mesh v.s.
+465 for the Voronoi mesh); the achieved difference is that the triangular mesh has faces with three materials, and Voronoi mesh does not.
+Nevertheless, ASC(0) performed poorly for this example converging to the steady-state at approximately $t = 3$.
+
 Arithmetic homogenization performs poorly for both mesh levels (even finer mesh near the inclusions is required to provide reasonably accurate solution).
@@
 
-        In Figure \ref{fig:transient:err} we present the $\lTwo$-norm of the error $p_* - p_h$ computed for the inclusion~$\Omega_2 \cup \Omega_3$ as a function of time.
+In Figure~\ref{fig:transient:err} we present the $\lTwo$-norm of the error $p_* - p_h$ computed for the inclusion~$\Omega_1 \cup \Omega_2$ as a function of time.
 Since all numerical solutions eventually converge to the same steady state, numerical errors for any method decrease for large enough time.
-        On earlier stages ASC(1) outperforms all methods on the coarse mesh and provides comparable results with ASC(0) scheme and the harmonic homogenization approach
-        on the fine mesh.
-
-	\footnotetext{
-		We tried replacing Voronoi mesh with a triangulation such that the number of triangles is close to the number of the polygonal cells in the fine Voronoi mesh (456 elements for the triangular mesh v.s.
-465 for the Voronoi mesh); the achieved difference is that the triangular mesh has faces with three materials, and Voronoi mesh does not.
-Nevertheless, ASC(0) performed poorly for this example converging to the steady-state at approximately $t = 3$.
-	}
+On earlier stages ASC(1) outperforms all methods on the coarse mesh and provides comparable results with ASC(0) scheme and the harmonic homogenization approach on the fine mesh.

### 2018-11-28 asc.tex
Fix typos and minor mistakes

@@
 			\includegraphicsw{ring_base_voronoi.png}
-			\caption{Base mesh}
+			\caption{Macro-mesh}
 			\label{fig:problem_geometry:base_mesh}
@@
 multi-material cells (central); The piecewise-planar discontinuous reconstruction of the interfaces by the moment-of-fluid method (right).
-Everything is shown for two refinement level of the base mesh \label{fig:problem_geometry}}
+Everything is shown for two refinement level of the macro-mesh \label{fig:problem_geometry}}
 	\end{figure}
@@
 surfaces where $\vect K$ may experience discontinuities, may cut through the macro-mesh in an arbitrary way; see Figure~\ref{fig:problem_geometry} (center).
-The polygonal cells ${\bcell \in \bmesh}$ cut by the interfaces are further called Multi-Material Cells (MMCs).
+The polygonal cells ${\bcell \in \bmesh}$ cut by the interfaces are further called multi-material cells (MMCs).
 In practice,  we are given a reconstructed interface by a volume-of-fluid or moment-of-fluid method.
-This reconstructed interface may be discontinuous across faces of MMC, but locally within each ${\bcell \in \bmesh}$ it is a collection of planar surfaces; see Figure~\ref{fig:problem_geometry} (right).
+This reconstructed interface may be discontinuous across faces of MMCs, but locally within each ${\bcell \in \bmesh}$ it is a collection of planar surfaces; see Figure~\ref{fig:problem_geometry} (right).
 
@@
 	\begin{equation}\label{system_mini}
-		{\vect u}^\text{ext}_\mmesh \coloneqq \vect E_\mmesh^T\,{\vect u}_\mmesh
+		{\vect u}^\text{ext}_\mmesh \coloneqq \vect E_\mmesh^T\,{\vect u}_\mmesh,
 	\end{equation}
@@
 	\[
-		n_\bcell = \sum_{F \in \bfaces_\bcell} \min\,\{ n+1, \nu_F \} \quad\text{and}\quad
-		n_\bmesh = \sum_{F \in \bfaces} \min\,\{ n+1, \nu_F \},
+		n_\bcell \coloneqq \sum_{F \in \bfaces_\bcell} \min\,\{ n+1, \nu_F \} \quad\text{and}\quad
+		n_\bmesh \coloneqq \sum_{F \in \bfaces} \min\,\{ n+1, \nu_F \},
 	\]
@@
 		\caption{$\lambda_{ji}(\mmesh)$ are local d.o.f.
-used in MFD for $\lambda$ from \eqref{dual_mini}, $\lambda_j(T)$, $\lambda'_j(T)$ are global d.o.f.
+used in MFD for $\lambda$ from \eqref{dual_mini}, $\lambda^{(0)}_j(T)$, $\lambda^{(1)}_j(T)$ are global d.o.f.
 used to describe mortar space $\Lambda$.
@@
 Same arguments hold for ASC(0) after obvious simplifications.
+	\vskip .2cm
 	%\begin{theorem}\label{thm:asc0}
@@
 		\Big( \big( \sum_{\bcell \in \bmesh} \vect N^T_\bcell\,\vect S_\bcell\,\vect N_\bcell \big){\vect\lambda_\bmesh},\,{\vect\lambda_\bmesh} \Big) =
-		\sum_{\bcell \in \bmesh} \big( \vect S_\bcell\,\vect N_\bcell\,{\vect\lambda_\bmesh},\,\underbrace{\vect N_\bcell\,{\vect\lambda_\bmesh}}_{{\vect \lambda_\bcell} \coloneqq} \big) \\
+		\sum_{\bcell \in \bmesh} \big( \vect S_\bcell\,\vect N_\bcell\,{\vect\lambda_\bmesh},\,\underbrace{\vect N_\bcell\,{\vect\lambda_\bmesh}}_{{\vect \lambda_\bcell} =} \big) \\
 		& = \sum_{\bcell \in \bmesh} \big(\vect S_\bcell\,{\vect \lambda_\bcell},\,{\vect \lambda_\bcell} \big) > 0.

### 2018-11-28 asc.tex
edited Acknowledgments

--- 2018-11-27 asc.tex
@@
 
-	\subsection*{Acknowledgments} Alexander Zhiliakov acknowledges the internship opportunity in Methods and Algorithms group of the Los Alamos National Laboratory.
-
+	\subsection*{Acknowledgments} 
+        Funded by the Department of Energy at Los Alamos National Laboratory
+        under contracts DE-AC52-06NA25396 and the DOE Office of Science
+        Advanced Computing Research (ASCR) program in Applied Mathematical
+        Sciences. Alexander Zhiliakov acknowledges the internship opportunity in the Los Alamos National Laboratory.
 	\bibliographystyle{plain}

### 2018-11-28 num_sec.tex
Fix a typo in the sec name

@@
-\section{Numerical Results}\label{sec:num}
+\section{Numerical results}\label{sec:num}
 
@@
 To test the {\it linearity preservation} property, we set up a pseudo-multi-material problem with the diffusion tensor being the same in all subdomains, $\vect K_i = \vect I$.
-The exact solution a linear function.
+The exact solution is a linear function.
 The geometry of two cases under consideration is shown in Figure~\ref{fig:fake}.
@@
 For this purpose, we solve the diffusion problem~\eqref{dual} in the unit square with $\partial\Omega = \partial\Omega_D$, $\vect K = k\,\vect I$, $k = 1$ on the left part and $k = 0.1$ on the right.
-We keep the mesh fixed, and change the position of the interface so that the minimal length of mini-faces~$w$ gets smaller, $w = 10^{-1}, 10^{-2}, \dots, 10^{-5}$ (see Figure~\ref{fig:w}).
+We keep the mesh fixed, and change the position of the interface so that the minimal length~$w$ of mini-faces gets smaller, $w = 10^{-1}, 10^{-2}, \dots, 10^{-5}$ (see Figure~\ref{fig:w}).
 
@@
 	\centering
-	\caption{Distribution of materials leads to  different values of the minimal length of mini-faces $w$ \label{fig:w}}
+	\caption{Distribution of materials leads to  different values of the minimal length~$w$ of mini-faces \label{fig:w}}
 	\begin{subfigure}{.33\linewidth}
@@
 $$
-where $\mu_{\text{min}} = \mu_0 \ge \mu_1 \ge \dots \ge \mu_{\text{max}}$ are the eigenvalues of~$\vect S_\bmesh$ of ASC(1).
+where $\mu_{\text{min}} = \mu_0 \le \mu_1 \le \dots \le \mu_{\text{max}}$ are the eigenvalues of~$\vect S_\bmesh$ of ASC(1).
 From this results we see that the effective condition number of ASC(1) stays bounded with respect to the interface position and is  close to the condition number of ASC(0).
@@
 %\end{equation}
-for $t\in(0, T]$ with initial data $p(\vect x, 0) = p_0(\vect x)$ and boundary data as in \eqref{dual:bc:neumann}.
-After discretizing in time by the implicit Euler method, the problem takes the form \eqref{dual}--\eqref{dual:bc:neumann} with $c=|\Delta t|^{-1}$ and we apply the spacial discretization described in section~\ref{sec:ASC}.
+for $t\in(0, T]$ with initial data $p(\vect x, 0) = p_0(\vect x)$ and boundary data as in \eqref{dual:bc}.
+After discretizing in time by the implicit Euler method, the problem takes the form \eqref{dual}--\eqref{dual:bc} with $c=|\Delta t|^{-1}$ and we apply the spacial discretization described in section~\ref{sec:ASC}.
 For the purpose of comparison, we apply arithmetic and harmonic homogenization methods followed by a MFD discretization.
@@
 Numerical solution computed with ASC(0) overestimates incoming fluxes for the ring.
-This solution converges to the equilibrium state~$p_h \approx 1$ at approximately $t = 3.75$, which is significantly earlier than the time when same state is achieved by the reference solution.
+This solution converges to the equilibrium state~$p_h \approx 1$ at approximately $t = 3.75$, which is significantly earlier than the time when the same state is achieved by the reference solution.
 Note that the coarse mesh contains faces with three materials, and we saw already that ASC(0) may fail to converge for this case even for stationary examples.

### 2018-12-21 asc.tex
Flip the sign of the affine shift for ext fluxes dofs
Eugene's changes

@@
 	Mathematical models of such processes are often formulated in terms of systems of partial differential equations with discontinuous coefficients and interface conditions on time-dependent internal boundaries.
-	Due to their high complexity, these models   resist analytical treatment, and hence numerical simulations became an indispensable tool for solving the models and gaining insights into underlying phenomena.
+	Due to their high complexity, these models are not suitable for analytical treatment, and hence numerical simulations became an indispensable tool for solving the models and gaining insights into underlying phenomena.
 
@@
 This includes immersed boundary method \cite{peskin2002immersed}, level-set method \cite{sethian1999level}, and unfitted finite element methods \cite{belytschko2009review,burman2015cutfem}, to name several popular numerical approaches.
-	The present study is motivated by the successful applications of the volume-of-fluid (VOF)~\cite{hirt1981volume} and the moment-of-fluid (MOF) methods~\cite{ahn2009adaptive} for the numerical  reconstruction of time-dependent interfaces.
-Both  methods do not require a mesh aligned with the  interfaces and reconstruct them from the information about the volumes of materials in each cell.
-	% implicitly with the help of a characteristic function
-	% and construct allow for general polygonal computational meshes not fitted to the position of the interface.
-	The superior conservation properties of the  VOF and MOF approaches, however, commonly come at a price of recovering piecewise smooth interface approximation that is  discontinuous across the faces of the underlying computational mesh.
+However, numerous applications require local conservation of material volumes on computational meshes that do not explicitly track material interfaces.
+This is typical for simulations of high speed multi-material flows, where shocks and vorticity often require the use of the Arbitrary Lagrangian-Eulerian method.
+The complication with this method is that over the course of simulation, material interfaces become unaligned with the computational mesh, with their shape and position inside mesh cells not being explicitly known.
 
-	In this report, we devise  a higher order method for the numerical solution of the diffusion problem with discontinuous  coefficients on a general polyhedral mesh, which does not respect the position of multi-material interfaces.
-The method builds upon the approximate static condensation (ASC) algorithm first proposed in~\cite{kikinzon2017approximate}; it admits high-contrast diffusion coefficients and discontinuous reconstruction of the interfaces as typical for the volume/moment-of-fluid method.
-The ASC approach uses the formulation of the interface diffusion problem as a system of local inter-cell problems  coupled through the concentration values and fluxes on the cell faces.
+    The standard approach to dealing with cells intersected by material interfaces, also known as multi-material cells, is by using a homogenization of  material properties, where a single artificial material assigned to the cell has properties that are calculated based on a volumetric distribution of real materials contained in that cell.
+This allows to use standard discretization methods if one needs to solve for other physics, such as the heat transfer, on every time step of the simulation.
+Then, ad-hoc methods can be used to interpolate the solution for the contained materials based on the computed cell-average values~\cite{dawes2013solving}.
+This approach does not accurately model in-cell material interactions and can result in non-physical solutions when materials are substantially different.
+
+    The alternatives generally require for the so-called interface reconstruction to be used in order to approximate material interfaces inside multi-material cells.
+Interface reconstruction methods typically represent materials in a cell by non-overlapping single-material polytopes that match given volume fractions.
+The most popular approach is based on using a single linear interface to represent an interface between two materials, and is commonly called the Piecewise-Linear Interface Calculation (PLIC).
+The volume-of-fluid (VOF)~\cite{hirt1981volume} is perhaps the most famous example of PLIC-type methods, which also include the moment-of-fluid (MOF) methods~\cite{ahn2009adaptive} that can provide better accuracy if centroids of materials are known.
+Recently introduced extended interface reconstruction methods, such as X-MOF~\cite{kikinzon2018xmof}, construct local meshes inside multi-material cells, where every cell of the local mesh contains only one material, and full local topology is available.
+
+    The common drawback of interface reconstruction is that reconstructed material interfaces are discontinuous on the interfaces between multi-material cells.
+One approach to dealing with this issue is through merging the local meshes with the computational mesh, thus effectively refining the mesh so that every cell contains only one material~\cite{garimella2011supermesh}.
+This is a non-trivial computational geometry problem, and the resulting mesh in 2D typically contains very small and co-linerar faces, while the extension of this approach to 3D is infeasible for general unstructured meshes.
+
+	In this article, we consider the numerical solution of the diffusion problem with discontinuous coefficients on polytopal meshes with multi-material cells.
+We assume that interface reconstruction is performed using an extended method, which provides local single-material meshes with full topological data for multi-material cells.
+One might consider solving this problem with Nitsche’s methods used in the framework of cut-cells~\cite{dolbow2012nitsche, burman2015cutfem, hansbo2002unfitted} or extended finite element methods (X-FEM)~\cite{dolbow2008xfem}.
+However, these methods are typically not locally conservative, and interface reconstruction is usually used when volume conservation is a requirement.
+Additionally, the discontinuity of material interfaces across faces of multi-material cells can be large enough to result in a significant loss of accuracy for these methods.
+
+	We present a higher order method for solving this problem that builds upon the approximate static condensation (ASC) algorithm first proposed in~\cite{kikinzon2017approximate}; it admits high-contrast diffusion coefficients and discontinuous reconstruction of the interfaces.
+The ASC approach uses the formulation of the interface diffusion problem as a system of problems on local meshes that are coupled through the concentration values and fluxes on the faces of multi-material cells.
 This face concentration serves as the new primal unknown and it is further approximated by piecewise  polynomial functions defined on all faces of the global (unfitted polygonal) mesh.
@@
 	Although the latter potentially leads to more accurate results  (and in some cases we shall see that it provides convergent results, when the $P_0$ version fails), it also raises some questions about stability and robustness, which we address in the present report.
+	One might note that using $P_1$ (piecewise linear) approximation to the face concentration puts the proposed method into the framework of mortar methods~\cite{yotov2009mortar,mortar}.
+While those methods were developed for different types of problems and substantially differ in terms of implementation, but the proposed method fits their high-level formulation.
 
@@
 Posed in each polygonal cell, these problems are given by diffusion equations with discontinuous coefficients.
-The method benefits from the observation that   for any fixed cell $T$,  material interfaces, which possibly intersect with $T$,  induce a \emph{consistent polygonal subdivision} (local mesh) of $T$.
-Opposite to the global mesh, the local one is \emph{fitted} to interfaces, i.e.
-each micro polyhedral element is shared only by one material.
-Following~\cite{kikinzon2017approximate}, we apply the mimetic finite difference (MFD) method from~\cite{lipnikov2014mimetic} to approximate the local diffusion problems on this fine fitted mesh.
+On the other hand, local meshes produces by extended interface reconstruction methods, unlike the the global mesh, contain only single-material cells.
+Following~\cite{kikinzon2017approximate}, we apply the mimetic finite difference (MFD) method from~\cite{lipnikov2014mimetic} to approximate the local diffusion problems on these local meshes.
 	After eliminating inter-cell degrees of freedom (d.o.f.), one obtains a system of linear algebraic equations for the face concentration degrees of freedom.
@@
 	\begin{equation}\label{asc_flux_lambda}
-		{\vect u}^\text{ext}_\mmesh = \vect A_\mmesh\,\vect C_\mmesh\,\vect R_\mmesh\,{\vect \lambda}_\bcell + {\vect a}_\mmesh.
+		{\vect u}^\text{ext}_\mmesh = \vect A_\mmesh\,\vect C_\mmesh\,\vect R_\mmesh\,{\vect \lambda}_\bcell - {\vect a}_\mmesh.
 	\end{equation}

### 2019-01-16 asc.tex
Add Maxim's changes to the introduction

--- 2018-11-28 asc.tex
@@
 	Mathematical models of such processes are often formulated in terms of systems of partial differential equations with discontinuous coefficients and interface conditions on time-dependent internal boundaries.
-	Due to their high complexity, these models   resist analytical treatment, and hence numerical simulations became an indispensable tool for solving the models and gaining insights into underlying phenomena.
+	Due to their high complexity, these models defy analytical treatment, and hence numerical simulations became an indispensable tool for solving the models and gaining insights into underlying phenomena.
 
 	Past decades evidenced an explosive growth in developing of efficient computational techniques for problems with evolving interfaces, which involve interaction between many materials or different phases of matter.
-This includes immersed boundary method \cite{peskin2002immersed}, level-set method \cite{sethian1999level}, and unfitted finite element methods \cite{belytschko2009review,burman2015cutfem}, to name several popular numerical approaches.
-	The present study is motivated by the successful applications of the volume-of-fluid (VOF)~\cite{hirt1981volume} and the moment-of-fluid (MOF) methods~\cite{ahn2009adaptive} for the numerical  reconstruction of time-dependent interfaces.
-Both  methods do not require a mesh aligned with the  interfaces and reconstruct them from the information about the volumes of materials in each cell.
-	% implicitly with the help of a characteristic function
-	% and construct allow for general polygonal computational meshes not fitted to the position of the interface.
-	The superior conservation properties of the  VOF and MOF approaches, however, commonly come at a price of recovering piecewise smooth interface approximation that is  discontinuous across the faces of the underlying computational mesh.
+This includes immersed boundary method~\cite{peskin2002immersed}, immersed interface method~\cite{leveque1994immersed}, and unfitted finite element methods \cite{belytschko2009review,burman2015cutfem}, to name several popular numerical approaches.
+Depending on how the interface is treated numerically, one can distinguish between methods that smear the interface over a strip of finite thickness which should be further resolved by the mesh, like in the phase field approach~\cite{steinbach2009phase}, and methods that use a sharp interface representation, as in the level-set method \cite{sethian1999level}.
+If one applies a sharp representation to handle complex geometries or interfaces undergoing large deformations, it is convenient to allow the  interface to cut through the background mesh in an arbitrary way.
+In turn, this leads to the problem of building accurate and stable approximations for  so-called multi-material cells, i.e.
+the mesh cells intersected by material interfaces.
+In particular, one is interested in discretizations to be robust with respect to how interfaces intersect the mesh and to the contrast of  material properties, e.g.
+the ratio of physical parameters.
+This is the setting and the problem  we focus in this paper.
 
-	In this report, we devise  a higher order method for the numerical solution of the diffusion problem with discontinuous  coefficients on a general polyhedral mesh, which does not respect the position of multi-material interfaces.
-The method builds upon the approximate static condensation (ASC) algorithm first proposed in~\cite{kikinzon2017approximate}; it admits high-contrast diffusion coefficients and discontinuous reconstruction of the interfaces as typical for the volume/moment-of-fluid method.
-The ASC approach uses the formulation of the interface diffusion problem as a system of local inter-cell problems  coupled through the concentration values and fluxes on the cell faces.
-This face concentration serves as the new primal unknown and it is further approximated by piecewise  polynomial functions defined on all faces of the global (unfitted polygonal) mesh.
+%However, numerous applications require local conservation of material volumes on computational meshes that do not explicitly track material interfaces.
+This is typical for simulations of high speed multi-material flows, where shocks and vorticity often require the use of the Arbitrary Lagrangian-Eulerian method.
+The complication with this method is that over the course of simulation, material interfaces become unaligned with the computational mesh, with their shape and position inside mesh cells not being explicitly known.
+
+One standard approach to handle  multi-material cells is a homogenization procedure.
+In this approach, one assigns to the cells  artificial homogeneous  material properties, which are calculated based on the volumetric shares of different materials in each of the multi-material cells.
+This enables one to apply standard discretization thechniques.
+%if one needs to solve for other physics, such as the heat transfer, on every time step of the simulation.
+     %Then, ad-hoc methods can be used to interpolate the solution for the contained materials based on
+Further one recovers solution in each phase from the computed cell-averaged values~\cite{dawes2013solving}.
+Although being technologically straightforward, the homogenization approach often fails  to accurately model subcell material interactions, which results in non-physical numerical solutions to problems with high-contrast material properties.
+
+As an alternative to the homogenization, one may reconstruct interfaces in each  multi-material cell  using a piecewise planar approximation.
+In this case, single-material domains  in the cell are  non-overlapping polytopes that typically preserve known material volumes.
+%The alternatives generally require for the so-called interface reconstruction to be used in order to approximate material interfaces inside multi-material cells.
+Interface reconstruction methods typically represent materials in a cell by non-overlapping single-material polytopes that match given volume fractions.
+%The most popular approach is based on using a single linear interface to represent an interface between two materials, and is commonly called the Piecewise-Linear Interface Calculation (PLIC). 
+In this paper, we deal with interfaces reconstructed by the volume-of-fluid (VOF)~\cite{hirt1981volume} method, which is a commonly used numerical interface recovery approach.
+The approach includes the moment-of-fluid (MOF) methods~\cite{ahn2009adaptive} that generally provide better accuracy if centroids of material subdomains are known.
+For the numerical experiments here we apply the extended MOF~\cite{kikinzon2018xmof}  to construct local meshes inside multi-material cells such that subcell contains only one material and all information about the local topology is available.
+% MAxim: It was not clear why you particularly mention  X-MOF. So I assume that it is what you use for experiments.
+
+%A drawback of interface reconstruction is that reconstructed material interfaces are discontinuous on the interfaces between multi-material cells.
+The conservation properties of the  VOF and MOF approaches, however, come at a price of recovering a piecewise planar interface approximation that is  discontinuous across the faces of the background computational mesh.
+One approach to deal with this issue is merging the local tessellations with the computational mesh, thus effectively refining the mesh so that every cell contains only one material~\cite{garimella2011supermesh}.
+It appears to be a non-trivial computational geometry problem, and the resulting mesh in 2D typically contains very small and co-linear faces, while the extension of this approach to 3D does not seem feasible for general unstructured meshes.
+
+	In this paper, we devise  a higher order method for the numerical solution of the diffusion problem with discontinuous coefficients on polytopal meshes with multi-material cells.
+We assume that interface reconstruction is performed using the extended MOF method, which provides local single-material meshes with full topological data.
+One might consider solving this problem with Nitsche’s methods used in the framework of cut-cells~\cite{burman2015cutfem, hansbo2002unfitted} or extended finite element methods (X-FEM)~\cite{dolbow2008xfem}.
+However, these methods are typically not locally conservative
+%, and interface reconstruction is usually used when volume conservation is a requirement. Additionally, 
+and the discontinuity of material interfaces across faces of multi-material cells can be large enough to result in a significant loss of accuracy.
+
+ The present method builds upon the approximate static condensation (ASC) algorithm proposed in~\cite{kikinzon2017approximate}; it admits high-contrast diffusion coefficients and discontinuous reconstruction of the interfaces.
+The ASC approach uses the formulation of the interface diffusion problem as a system of problems on local meshes that are coupled through the concentration values and fluxes on the faces of multi-material cells.
+This face concentration serves as a new primal unknown and it is further approximated by piecewise  polynomial functions defined on all faces of the global (unfitted polygonal) mesh.
 The original paper ~\cite{kikinzon2017approximate} considered $P_0$ (piecewise constant) approximation to the face concentration, while the present study introduces higher order polynomials for this purpose.
 	Although the latter potentially leads to more accurate results  (and in some cases we shall see that it provides convergent results, when the $P_0$ version fails), it also raises some questions about stability and robustness, which we address in the present report.
+We note that using a skeleton space of  piecewise polynomial functions to couple local unknowns renders the approach as
+a version of a mortar method~\cite{yotov2009mortar,mortar}, although mortar finite element  methods were developed for different types of problems and substantially vary in terms of implementation.
+	%One might note that using $P_1$ (piecewise linear) approximation to the face concentration puts the proposed method into the framework of mortar methods~\cite{yotov2009mortar,mortar}.
+While those methods were developed for different types of problems and substantially differ in terms of implementation, the proposed method fits their high-level formulation.
+
+%The approximate static condensation approach leaves much freedom in the choice of the discretization method for the local diffusion problems.
+Posed in each polygonal cell, these problems are given by diffusion equations with discontinuous coefficients.
+On the other hand, local meshes produced by extended interface reconstruction methods, unlike the the global mesh, contain only single-material cells.
+Following~\cite{kikinzon2017approximate}, we apply the mimetic finite difference (MFD) method from~\cite{lipnikov2014mimetic} to approximate the local diffusion problems on these local meshes.
 
@@
 The fluxes and inter-element degrees of freedom are recovered by simple postprocessing.
-In the report, we study the performance of the method in terms of accuracy, robustness with respect to the interfaces position,  and algebraic stability.
+Further, we study the performance of the method in terms of accuracy, robustness with respect to the interfaces position,  and algebraic stability.
 
@@
 Finally, section~\ref{sec:num} collects results of numerical experiments.
-These results include accuracy tests, numerical comparison with the method from  \cite{kikinzon2017approximate} and with a homogenization method as an alternative approach.
+These results include accuracy tests, numerical comparison with the method from  \cite{kikinzon2017approximate} and with a homogenization method as the alternative approach.
 

### 2019-01-25 num_sec.tex
Added flux results

@@
-\section{Numerical results}\label{sec:num}
+\section{Numerica results}\label{sec:num}
 
@@
 \end{equation}
-since~$P_h$ is linear and~$p_h \in \mathbb V_h$. The discrete norm~\eqref{l2norm} of the discretization error is computed as follows:
+since~$P_h$ is linear and~$p_h \in \mathbb V_h$. The discrete norm~\eqref{l2norm} of the concentration discretization error is computed as follows:
 $$
@@
 $$
-where $|\mcell|$ is the area of cell $\mcell$.
+        where $|\mcell|$ is the area of cell $\mcell$. While the disrete norm of the flux discretization error is defined as follows:
+        $$
+        \varepsilon_h^{l_2} =  \left[\sum\limits_{\bface \in \bmesh_h}
+          A_\bface\left(
+          \sum\limits_{\mface\in\bface}
+          \frac{1}{|\mface|}\int_{\mface}
+          \vect u \diff{\vect s}  - \sum\limits_{\mface\in\bface}\vect u_h(\mface)\right)^2 
+          \right]^\frac12
+        $$
+        where $A_\bface|$ is the representative are of a face $\bface$ which is equal to the arithmetic average
+of areas of cells sharing the face $\bface$.
 
@@
 	\footnotesize
-	\begin{tabular}[1.5]{| c | c || c | c || c |}
+	\begin{tabular}[1.5]{| c | c || c | c | c || c | c  ||}
 		\hline
-		\multirow{5}{*}{\rotatebox{90}{ASC(0)}} & $h$ & $\errlTwo{0}$ & $\rho$ & $\errInf{0}$ \\
-		\cline{2-5}
-		& $3.5\times10^{-1}$ & $7.3\times10^{-1}$ & & 4.8 \\
-		\cline{2-5}
-		& $8.8\times10^{-2}$ & $1.6\times10^{-1}$ & 1.1 & 1.2 \\
-		\cline{2-5}
-		& $2.2\times10^{-2}$ & $3.7\times10^{-2}$ & 1.1 & $3.4\times10^{-1}$ \\
-		\cline{2-5}
-		& $5.5\times10^{-3}$ & $8.9\times10^{-3}$ & 1.0 & $7.9\times10^{-2}$ \\
+		\multirow{5}{*}{\rotatebox{90}{ASC(0)}} & $h$ & $\errlTwo{0}$ & $\rho_p$ & $\errInf{0}$
+                                                              & $\varepsilon^{l_2}_0$ & $\rho_u$ \\              %& $\varepsilon^\infty_0$ \\
+		\cline{2-7}
+		& $3.5\times10^{-1}$ & $7.3\times10^{-1}$ &     & 4.8               & $ 6.6\times10^{-1}$ &  \\              %    & 7.9 \\
+		\cline{2-7}
+		& $8.8\times10^{-2}$ & $1.6\times10^{-1}$ & 1.1 & 1.2               & $ 3.5\times10^{-1}$ & 0.46 \\              %& 6.0\\
+		\cline{2-7}
+		& $2.2\times10^{-2}$ & $3.7\times10^{-2}$ & 1.1 & $3.4\times10^{-1}$ & $ 1.3\times10^{-1}$ & 0.71 \\              %& 5.8\\
+		\cline{2-7}
+		& $5.5\times10^{-3}$ & $8.9\times10^{-3}$ & 1.0 & $7.9\times10^{-2}$ & $ 4.1\times10^{-2}$ & 0.83 \\              %& 6.0\\
 		\hline
 		\hline
-		\multirow{5}{*}{\rotatebox{90}{ASC(1)}} & $h$ & $\errlTwo{1}$ & $\rho$ & $\errInf{1}$ \\
-		\cline{2-5}
-		& $3.5\times10^{-1}$ & $2.5\times10^{-2}$ & & $1.6\times10^{-1}$ \\
-		\cline{2-5}
-		& $8.8\times10^{-2}$ & $1.9\times10^{-3}$ & 1.84 & $6.3\times10^{-2}$ \\
-		\cline{2-5}
-		& $2.2\times10^{-2}$ & $1.6\times10^{-4}$ & 1.79 & $9.8\times10^{-3}$ \\
-		\cline{2-5}
-		& $5.5\times10^{-3}$ & $1.3\times10^{-5}$ & 1.80 & $4.0\times10^{-3}$ \\
+		\multirow{5}{*}{\rotatebox{90}{ASC(1)}} & $h$ & $\errlTwo{1}$ & $\rho$ & $\errInf{1}$
+                & $\varepsilon^{l_2}_1$ & $\rho_u$ \\              %& $\varepsilon^\infty_1$\\
+		\cline{2-7}
+		& $3.5\times10^{-1}$ & $2.5\times10^{-2}$ & & $2.9\times10^{-1}$      & $ 4.6\times10^{-2}$ &   \\              %  &0.51\\
+		\cline{2-7}
+		& $8.8\times10^{-2}$ & $1.9\times10^{-3}$ & 1.84 & $6.6\times10^{-2}$ & $ 2.0\times10^{-2}$ & 0.6 \\              %&0.46\\
+		\cline{2-7}
+		& $2.2\times10^{-2}$ & $1.6\times10^{-4}$ & 1.79 & $4.3\times10^{-2}$ & $ 5.5\times10^{-3}$ & 0.93 \\              %&0.57\\
+		\cline{2-7}
+		& $5.5\times10^{-3}$ & $1.3\times10^{-5}$ & 1.80 & $2.0\times10^{-2}$ & $ 1.3\times10^{-3}$ & 1.   \\  %& 0.46\\
 		\hline
@@
 
-Numerical results are shown in Table~\ref{fig:conv:pwlin}.
-We observe that ASC(0) converges linearly with respect to the $\lTwo$-norm, and ASC(1) has the convergence rate close to quadratic with respect to the $\lTwo$-norm.
+Numerical results are shown in Table~\ref{fig:conv:pwlin}. We observe that ASC(0) converges linearly with respect to the $\lTwo$-norm,
+and ASC(1) has the convergence rate close to quadratic with respect to the $\lTwo$-norm.
+The convergence of the flux errors is also is higher for ASC(1) method and is close to linear convergence.
 
@@
 	\footnotesize
-	\begin{tabular}[1.1]{| c | c || c | c || c |}
+	\begin{tabular}[1.1]{| c | c || c | c | c ||c | c | c ||}
 		\hline
-		\multirow{7}{*}{\rotatebox{90}{ASC(0)}} & $h$ & $\errlTwo{0}$ & ${\rho}$ & $\errInf{0}$ \\
-		\cline{2-5}
-		& $3.0\times10^{-1}$ & $2.4\times10^{-3}$ & & $6.3\times10^{-1}$ \\
-		\cline{2-5}
-		& $1.5\times10^{-1}$ & $6.5\times10^{-4}$ & 2.0 & $7.0\times10^{-3}$ \\
-		\cline{2-5}
-		& $8.1\times10^{-2}$ & $2.6\times10^{-4}$ & 1.4 & $3.2\times10^{-3}$ \\
-		\cline{2-5}
-		& $4.2\times10^{-2}$ & $1.4\times10^{-4}$ & 0.9 & $2.3\times10^{-3}$ \\
-		\cline{2-5}
-		& $2.1\times10^{-2}$ & $3.7\times10^{-5}$ & 1.9 & $1.1\times10^{-3}$ \\
-		\cline{2-5}
-		& $1.0\times10^{-2}$ & $2.7\times10^{-5}$ & 0.4 & $8.6\times10^{-4}$ \\
+		\multirow{7}{*}{\rotatebox{90}{ASC(0)}} & $h$ & $\errlTwo{0}$ & ${\rho_p}$ & $\errInf{0}$
+                & $\varepsilon^{l_2}_0$ & $\rho_u$ \\ %& $\varepsilon^\infty_0$ \\
+		\cline{2-7}
+		& $3.0\times10^{-1}$ & $2.4\times10^{-3}$ &     & $6.3\times10^{-1}$ & $6.9\times10^{-5}$ &  \\ %& $2.6\times10^{-4}$ \\
+		\cline{2-7}
+		& $1.5\times10^{-1}$ & $6.5\times10^{-4}$ & 2.0 & $7.0\times10^{-3}$ & $3.6\times10^{-5}$ & 0.9 \\ %&$1.6\times10^{-4} $ \\
+		\cline{2-7}
+		& $8.1\times10^{-2}$ & $2.6\times10^{-4}$ & 1.4 & $3.2\times10^{-3}$ & $3.4\times10^{-5}$ & 0.09 \\ %&$2.0\times10^{-3}$  \\
+		\cline{2-7}
+		& $4.2\times10^{-2}$ & $1.4\times10^{-4}$ & 0.9 & $2.3\times10^{-3}$ & $2.1\times10^{-5}$ & 0.73 \\ %&$1.0\times10^{-3}$  \\
+		\cline{2-7}
+		& $2.1\times10^{-2}$ & $3.7\times10^{-5}$ & 1.9 & $1.1\times10^{-3}$ & $1.1\times10^{-5}$ & 0.93 \\ %&$6.9\times10^{-4}$  \\
+		\cline{2-7}
+		& $1.0\times10^{-2}$ & $2.7\times10^{-5}$ & 0.4 & $8.6\times10^{-4}$ & $6.5\times10^{-6}$ & 0.75 \\ % &$1.8\times10^{-3}$  \\
 		\hline
 	\end{tabular}
-	\begin{tabular}[1.1]{| c | c || c | c || c |}
+	\begin{tabular}[1.1]{| c | c || c | c | c ||c | c | c || }
 		\hline
-		\multirow{7}{*}{\rotatebox{90}{ASC(1)}} & $h$ & $\errlTwo{1}$ & ${\rho}$ & $\errInf{1}$ \\
-		\cline{2-5}
-		& $3.0\times10^{-1}$ & $2.4\times10^{-3}$ & & $2.1\times10^{-3}$ \\
-		\cline{2-5}
-		& {$1.5\times10^{-1}$} & $7.0\times10^{-4}$ & 1.9 & {$1.3\times10^{-2}$} \\
-		\cline{2-5}
-		& $8.1\times10^{-2}$ & $2.3\times10^{-4}$ & 1.8 & $6.8\times10^{-4}$ \\
-		\cline{2-5}
-		& $4.2\times10^{-2}$ & $6.8\times10^{-5}$ & 1.8 & $3.2\times10^{-4}$ \\
-		\cline{2-5}
-		& $2.1\times10^{-2}$ & $2.0\times10^{-5}$ & 1.8 & $1.1\times10^{-4}$ \\
-		\cline{2-5}
-		& $1.0\times10^{-2}$ & $5.4\times10^{-6}$ & 1.9 & $3.3\times10^{-5}$ \\
+		\multirow{7}{*}{\rotatebox{90}{ASC(1)}} & $h$ & $\errlTwo{1}$ & ${\rho}$ & $\errInf{1}$ 
+                & $\varepsilon^{l_2}_1$ & $\rho_u$ \\ %& $\varepsilon^\infty_1$ \\
+		\cline{2-7}
+		& $3.0\times10^{-1}$ & $2.4\times10^{-3}$ & & $2.1\times10^{-3}$     &$1.2\times10^{-4}$  &  \\ %&$3.0\times10^{-4}$  \\
+		\cline{2-7}
+		& $1.5\times10^{-1}$ & $7.0\times10^{-4}$ & 1.9 & $1.3\times10^{-2}$ &$6.5\times10^{-5}$  & 0.88 \\ %&$8.8\times10^{-4}$  \\
+		\cline{2-7}
+		& $8.1\times10^{-2}$ & $2.3\times10^{-4}$ & 1.8 & $6.8\times10^{-4}$ &$3.0\times10^{-5}$  & 1.25 \\ %&$2.6\times10^{-4}$  \\
+		\cline{2-7}
+		& $4.2\times10^{-2}$ & $6.8\times10^{-5}$ & 1.8 & $3.2\times10^{-4}$ &$1.4\times10^{-5}$  & 1.16 \\ %&$3.2\times10^{-4}$  \\
+		\cline{2-7}
+		& $2.1\times10^{-2}$ & $2.0\times10^{-5}$ & 1.8 & $1.1\times10^{-4}$ &$5.0\times10^{-6}$  & 1.48 \\ %&$2.4\times10^{-4}$  \\
+		\cline{2-7}
+		& $1.0\times10^{-2}$ & $5.4\times10^{-6}$ & 1.9 & $3.3\times10^{-5}$ &$2.2\times10^{-6}$  & 1.18 \\ %&$1.2\times10^{-4}$  \\
 		\hline
@@
 
-The norms of the errors are shown in Table~\ref{tab:conv:pwquad2}.
-ASC(1) demonstrates convergence with the rate in the $\lTwo$-norm close to quadratic.
-ASC(0) convergence rate fluctuates significantly.
+%% \begin{table}[h!]
+%% 	\centering
+%% 	\caption{Piecewise quadratic example, two materials: convergence \label{tab:conv:pwquad2_flux}}
+%% 	\footnotesize
+%% 	\begin{tabular}[1.1]{| c | c || c | c || c |}
+%% 		\hline
+%% 		\multirow{7}{*}{\rotatebox{90}{ASC(0)}} & $h$ & $\errlTwo{0}$ & ${\rho}$ & $\errInf{0}$ \\
+%% 		\cline{2-5}
+%% 		& $3.0\times10^{-1}$ & $9.3\times10^{-5}$ & & $2.6\times10^{-4}$ \\
+%% 		\cline{2-5}
+%% 		& $1.5\times10^{-1}$ & $4.2\times10^{-5}$ & & $1.6\times10^{-4}$ \\
+%% 		\cline{2-5}
+%% 		& $8.1\times10^{-2}$ & $4.6\times10^{-5}$ & & $2.0\times10^{-3}$ \\
+%% 		\cline{2-5}
+%% 		& $4.2\times10^{-2}$ & $2.5\times10^{-5}$ & & $1.1\times10^{-3}$ \\
+%% 		\cline{2-5}
+%% 		& $2.1\times10^{-2}$ & $1.4\times10^{-5}$ & & $6.9\times10^{-4}$ \\
+%% 		\cline{2-5}
+%% 		& $1.0\times10^{-2}$ & $8.9\times10^{-6}$ & & $1.8\times10^{-3}$ \\
+%% 		\hline
+%% 	\end{tabular}
+%% 	\begin{tabular}[1.1]{| c | c || c | c || c |}
+%% 		\hline
+%% 		\multirow{7}{*}{\rotatebox{90}{ASC(1)}} & $h$ & $\errlTwo{1}$ & ${\rho}$ & $\errInf{1}$ \\
+%% 		\cline{2-5}
+%% 		& $3.0\times10^{-1}$ & $1.4\times10^{-4}$ &     & $3\times10^{-4}$ \\
+%% 		\cline{2-5}
+%% 	        & $1.5\times10^{-1}$ & $7.9\times10^{-5}$ & & $8.7\times10^{-4}$ \\
+%% 		\cline{2-5}
+%% 		& $8.1\times10^{-2}$ & $4.0\times10^{-5}$ & & $2.6\times10^{-4}$ \\
+%% 		\cline{2-5}
+%% 		& $4.2\times10^{-2}$ & $1.8\times10^{-5}$ & & $3.2\times10^{-4}$ \\
+%% 		\cline{2-5}
+%% 		& $2.1\times10^{-2}$ & $6.4\times10^{-6}$ & & $2.3\times10^{-4}$ \\
+%% 		\cline{2-5}
+%% 		& $1.0\times10^{-2}$ & $2.7\times10^{-6}$ & & $1.2\times10^{-4}$ \\
+%% 		\hline
+%% 	\end{tabular}
+%% \end{table}
 
+The norms of the errors are shown in Table~\ref{tab:conv:pwquad2}. ASC(1) demonstrates convergence with the rate in the $\lTwo$-norm close to quadratic for scalar unknowns and
+even higher than linear for flux errors. It is important to take into accont that approximation errors in the interface reconstruction
+may  effect the convergence of discretization methods. For example, in these set of tests ASC(0) convergence rate fluctuates significantly for both scalar and flux errors.
 We also observe a bump in the max norm error for ASC(1) on the second mesh level, $h = 1.5\times10^{-1}$.
 To have some insight, we show the corresponding mesh in the Figure~\ref{fig:conv:pwquad2:inf:mesh}.
-One may note that the interface reconstruction produces significant discontinuity of interfaces: A small volume of the external material, i.e.
-the one occupying $\Omega_2$ domain, appears inside the disk (domain $\Omega_1$).
+One may note that the interface reconstruction produces significant discontinuity of interfaces:
+A small volume of the external material, i.e. the one occupying $\Omega_2$ domain, appears inside the disk (domain $\Omega_1$).
 Due to constant trace approximation, ASC(0) is not sensitive to such irregularity.
@@
 
-\clearpage
+%\clearpage
 

### 2019-01-26 asc.tex
Add Maxim's changes

@@
 It is demonstrated that the method is second order accurate on smooth solutions and performs well for problems with high contrast in diffusion coefficients.
-Experiments also show the robustness with respect to position of the interface against the underlying mesh.
+Experiments also show the robustness with respect to position of the material interfaces against the underlying mesh.
 	\end{abstract}
@@
 	Past decades evidenced an explosive growth in developing of efficient computational techniques for problems with evolving interfaces, which involve interaction between many materials or different phases of matter.
-This includes immersed boundary method~\cite{peskin2002immersed}, immersed interface method~\cite{leveque1994immersed}, and unfitted finite element methods \cite{belytschko2009review,burman2015cutfem}, to name several popular numerical approaches.
+These developments include immersed boundary method~\cite{peskin2002immersed}, immersed interface method~\cite{leveque1994immersed}, and unfitted finite element methods \cite{belytschko2009review,burman2015cutfem}, to name several popular numerical approaches.
 Depending on how the interface is treated numerically, one can distinguish between methods that smear the interface over a strip of finite thickness which should be further resolved by the mesh, like in the phase field approach~\cite{steinbach2009phase}, and methods that use a sharp interface representation, as in the level-set method \cite{sethian1999level}.
@@
 the mesh cells intersected by material interfaces.
-In particular, one is interested in discretizations to be robust with respect to how interfaces intersect the mesh and to the contrast of  material properties, e.g.
+In particular, one is interested in discretizations which are robust with respect to how interfaces intersect the mesh and with respect to the contrast of  material properties, e.g.
 the ratio of physical parameters.
@@
 %The most popular approach is based on using a single linear interface to represent an interface between two materials, and is commonly called the Piecewise-Linear Interface Calculation (PLIC).
-In this paper, we deal with interfaces reconstructed by the volume-of-fluid (VOF)~\cite{hirt1981volume} method, which is a commonly used numerical interface recovery approach.
+In this paper, we deal with interfaces reconstructed by the volume-of-fluid (VOF)~\cite{hirt1981volume} method, which is a commonly used numerical  approach to recover interface location.
 The approach includes the moment-of-fluid (MOF) methods~\cite{ahn2009adaptive} that generally provide better accuracy if centroids of material subdomains are known.
@@
 The conservation properties of the  VOF and MOF approaches, however, come at a price of recovering a piecewise planar interface approximation that is  discontinuous across the faces of the background computational mesh.
-One approach to deal with this issue is merging the local tessellations with the computational mesh, thus effectively refining the mesh so that every cell contains only one material~\cite{garimella2011supermesh}.
-It appears to be a non-trivial computational geometry problem, and the resulting mesh in 2D typically contains very small and co-linear faces, while the extension of this approach to 3D does not seem feasible for general unstructured meshes.
+One technique to deal with this issue consists in including the local tessellations into the global computational mesh, thus effectively refining the mesh so that every cell contains only one material~\cite{garimella2011supermesh}.
+This turns out to be a non-trivial computational geometry problem, and the resulting mesh in 2D often contains very small and co-linear faces, while the extension of this approach to 3D does not seem feasible for general unstructured meshes.
 
@@
 	\end{equation}
-	Here $\vect M_\mmesh$, $\vect\Sigma_\mmesh$, $\vect B^T_\mmesh$, $-\vect B_\mmesh$ are vector-mass, mass, gradient and divergence matrices, respectively.
-$-\vect C_\mmesh$ is a diagonal scaling matrix.
-i.e.
+	Here $\vect M_\mmesh$, $\vect\Sigma_\mmesh$, $\vect B^T_\mmesh$, $-\vect B_\mmesh$ are vector-mass, mass, gradient and divergence matrices, respectively; $-\vect C_\mmesh$ is a diagonal scaling matrix, i.e.
 the mass matrix for ${\vect \lambda}_\mmesh$ unknowns;
@@
 
-	Since the continuity of flux condition \eqref{flux_cond} and boundary conditions are enforced on all the \emph{external} edges of $T$, we need to distinct the vector ${\vect u}^\text{ext}_\mmesh$ of fluxes on $\mfaces[ext](T)$, which is just a trivial restriction of ${\vect u}_\mmesh$ on the edges  from $\mfaces[ext](T)$,
+	Since the continuity of flux condition \eqref{flux_cond} and boundary conditions are enforced on  the \emph{external} edges of $T$, we need to distinct the vector ${\vect u}^\text{ext}_\mmesh$ of fluxes on $\mfaces[ext](T)$, which is just a trivial restriction of ${\vect u}_\mmesh$ on the edges  from $\mfaces[ext](T)$,
 	\begin{equation}\label{system_mini}
@@
 However, we cannot do this in a straightforward way, since the discontinuity of material interfaces across the macro-mesh faces may lead to a mismatch of discrete fluxes from two sides of $F\in\bfaces[int]$, including different space dimensions.
-	Therefore, we shall enforce the flux continuity condition in the spirit of the mortar finite element method~\cite{mortar} using the space of function defined on $\bfaces[int]$, which are polynomials of degree at most $n$ on every $F\in\bfaces[int]$, an analog of the Lagrange multiplier space in the mortar method:
+	Therefore, we shall enforce the flux continuity condition in the spirit of the mortar finite element method~\cite{mortar} using the space of functions defined on $\bfaces[int]$, which are polynomials of degree at most $n$ on every $F\in\bfaces[int]$, an analog of the Lagrange multiplier space in the mortar method:
 	\[
@@
 	\end{equation}
-	Here~$\{\,s_i\,\}_{i=0,\dots,n}$ is the set of $\LTwoSpace[\bface]$-orthogonal polynomials of degree~$n$.
+	Here~$\{\,s_i\,\}_{i=0,\dots,n}$ is the set of $\LTwoSpace$-orthogonal polynomials on $F$ of degree~$n$.
 
@@
 	\end{equation}
-	for $\lambda\in\Lambda$. Here $t\in(0,1)$ and ${\vect r}\::\:\left(0,1\right) \rightarrow F$ is the affine parametrization of $F$, which has index $j$ among macro-faces of $T$.
+	for $\lambda\in\Lambda$. Here $t\in(0,1)$ and ${\vect r}\::\:\left(0,1\right) \rightarrow F$ is the affine parametrization of the face $F$ with index $j$ among macro-faces of $T$.
 
@@
 		\vect S_\bmesh = \sum_{\bcell \in \bmesh} \vect N^T_\bcell\,\vect S_\bcell\,\vect N_\bcell, \quad
-		{\vect b}_\bmesh = \sum_{\bcell \in \bmesh} \vect N^T_\bcell\,{\vect b}_\bcell.
+		{\vect b}_\bmesh = \sum_{\bcell \in \bmesh} \vect N^T_\bcell\,{\vect b}_\bcell,
 		%\end{split}
@@
 		\end{equation}
-		where~$m \coloneqq$ number of macro-faces spanning~$\bcell$ and
+		where~$m \coloneqq$ number of macro-faces spanning~$\partial\bcell$ and
 		\begin{equation*}
@@
 		\end{equation*}
-		for some~$k$. Take some $\vect S \equiv \vect S_k$ corresponding to a multi-material face~$F \in \bfaces_\bcell$ with~${l \coloneqq m_k}$ materials,
+		for some~$k$. Take some $\vect S = \vect S_k$ corresponding to a multi-material face~$F \in \bfaces_\bcell$ with~${l \coloneqq m_k}$ materials,
 		\begin{equation*}

### 2019-01-26 num_sec.tex
Add Maxim's changes

@@
-\section{Numerica results}\label{sec:num}
+\section{Numerical results}\label{sec:num}
 
-Let $h$ be a max cell diameter for the macro-mesh~$\bmesh_h$, and $\mathbb V_h \subset \LTwoSpace$ be a space of piecewise constant
+Let $h$ be a maximum cell diameter for the macro-mesh~$\bmesh_h$, and $\mathbb V_h \subset \LTwoSpace$ be a space of piecewise constant
 functions on each cell~$\mcell \in \mmesh(\bcell)$, $\bcell \in \bmesh_h$. We define \textit{discrete} $\LTwo$-norm of $v \in \LTwoSpace$ as
@@
 \end{equation}
-since~$P_h$ is linear and~$p_h \in \mathbb V_h$. The discrete norm~\eqref{l2norm} of the concentration discretization error is computed as follows:
+since~$P_h$ is linear and~$p_h \in \mathbb V_h$. %The discrete norm~\eqref{l2norm} of the concentration discretization error is computed as follows:
+This gives
 $$
@@
 $$
-        where $|\mcell|$ is the area of cell $\mcell$. While the disrete norm of the flux discretization error is defined as follows:
+        where $|\mcell|$ is the area of cell $\mcell$. The discrete norm of the flux discretization error is defined as follows:
         $$
@@
         $$
-        where $A_\bface|$ is the representative are of a face $\bface$ which is equal to the arithmetic average
-of areas of cells sharing the face $\bface$.
+        where $A_\bface$ is the reference volume of a face $\bface$ which is equal to the arithmetic average
+of volumes of cells sharing the face $\bface$.
 
-If~$\bmesh_h$ consists of triangles and no material interfaces are present, ASC($n$) boils down to mixed-hybrid Raviart\,--\,Thomas finite element method (which is algebraically equivalent to~$R\,T_0$ finite element method).
+If~$\bmesh_h$ consists of triangles and \emph{no} material interfaces are present, ASC($n$) reduces to mixed-hybrid Raviart\,--\,Thomas finite element method (which is algebraically equivalent to~$R\,T_0$ finite element method).
 In this particular case we have~\cite{M2AN_1980__14_3_249_0}
@@
 $$
-so one cannot expect ASC($n$) $\LTwo$-convergence to be better than linear. Note that
-\begin{equation}\label{l2L2}
-	\| p - p_h \|_{\lTwoSpace} \le \| p - p_h \|_{\LTwoSpace}
-\end{equation}
-since $\| p - p_h \|_{\lTwoSpace} = \| P_h\,(p - p_h) \|_{\lTwoSpace} \le \|P_h\|_{\mathcal L(\LTwoSpace, \mathbb V_h)} \| p - p_h \|_{\LTwoSpace}$, and the operator norm~$\|P_h\|_{\mathcal L(\LTwoSpace, \mathbb V_h)} = 1$ by Pythagorean theorem.
+so one should not expect ASC($n$) $\LTwo$-convergence to be better than linear. 
+However, since we measure convergence of the averages values and
+%\begin{equation}\label{l2L2}
+$	\| p - p_h \|_{\lTwoSpace} \le \| p - p_h \|_{\LTwoSpace} $
+%\end{equation}
+by the property of projection, we may observe a higher order convergence for smooth solutions.
+%since $\| p - p_h \|_{\lTwoSpace} = \| P_h\,(p - p_h) \|_{\lTwoSpace} \le \|P_h\|_{\mathcal L(\LTwoSpace, \mathbb V_h)} \| p - p_h \|_{\LTwoSpace}$, and the operator norm~$\|P_h\|_{\mathcal L(\LTwoSpace, \mathbb V_h)} = 1$ by Pythagorean theorem.
 Thus one may expect some improvement in $\lTwo$-convergence as one increases~$n$ for ASC($n$).
@@
 
-The first set of tests is designed to check the property of the method to accurately recover the solution that is the polynomial of degree~1.
+The first set of tests is designed to check the property of the method to accurately recover the solution that given by a  polynomial of degree~1.
 Let us consider the diffusion problem~\eqref{dual} with~$c \equiv f \equiv 0$, $\partial\Omega_D = \partial\Omega$.
@@
 In these settings the interface reconstruction algorithm MOF reconstructs the interfaces exactly.
-To test the {\it linearity preservation} property, we set up a pseudo-multi-material problem with the diffusion tensor being the same in all subdomains, $\vect K_i = \vect I$.
+To test this preservation property, we set up a pseudo-multi-material problem with the diffusion tensor being the same in all subdomains, $\vect K_i = \vect I$.
 The exact solution is a linear function.
@@
 Since ASC(1) approximates interface traces with $P_1$ functions it recovers edge-based degrees of freedom exactly in the sense of mean values.
-This results in exact reconstruction of cell-based unknowns and {\it linearity preservation} property for both examples, i.e.
+This results in exact reconstruction of cell-based unknowns and the preservation property holds for both examples, i.e.
 \begin{equation*}
@@
 \begin{equation*}
-	\rho_{h_i,\,n} \coloneqq \frac{\ln \errlTwo{h_i,\,n} / \errlTwo{h_{i+1},\,n}}{\ln h_i / h_{i+1}}
+	\rho_{h_i,\,n} \coloneqq \frac{\ln (\errlTwo{h_i,\,n} / \errlTwo{h_{i+1},\,n})}{\ln (h_i / h_{i+1})}
 \end{equation*}
-the reduction rate order of ASC($n$) in~$\lTwo$-norm between $i$th and $(i+1)$th refinement steps. We also compute the $\ell^{\infty}$-norm of the error
+the convergence order of ASC($n$) in~$\lTwo$-norm between $i$th and $(i+1)$th refinement steps. We also compute the $\ell^{\infty}$-norm of the error
 \begin{equation*}
@@
 
-Numerical results are shown in Table~\ref{fig:conv:pwlin}. We observe that ASC(0) converges linearly with respect to the $\lTwo$-norm,
-and ASC(1) has the convergence rate close to quadratic with respect to the $\lTwo$-norm.
-The convergence of the flux errors is also is higher for ASC(1) method and is close to linear convergence.
+Numerical results are shown in Table~\ref{fig:conv:pwlin}. We see that ASC(0) converges linearly with respect to the $\lTwo$-norm,
+and ASC(1) has the convergence rate close to quadratic with respect to the same norm.
+The convergence of the flux errors is also higher for ASC(1) method and is close to linear convergence.
 
@@
 
-It is well-known that the presence of a few outliers in the spectrum does not affect the asymptotic convergence of the conjugate gradient (CG) iterative methods, see, e.g., \cite{olshanskii2014iterative}.
+It is well-known that the presence of a few outliers in the spectrum does not affect the \emph{asymptotic} convergence of the conjugate gradient (CG) iterative methods, see, e.g., \cite{olshanskii2014iterative}.
 Indeed, in our experiments the CG method (with algebraic multigrid preconditioner) was found to be equally effective for solving systems of algebraic equations resulting from ASC(0) and ASC(1).
@@
 $\Omega_1 = \{{\bf x} : \|{\bf x} - {\bf x}_0\| < 0.15\}$, $\Omega_2 = \{{\bf x} : 0.15 < \|{\bf x} - {\bf x}_0\| < 0.2\}$, and $\Omega_3 = (0,1)^2 \setminus (\bar{\Omega}_1\cup\bar{\Omega}_2)$.
-The diffusion tensor is set as $\vect K_i = k_i\,\vect I$, $k_1 = 10, k_2 = 0.002$, and $k_3 = 1$.
+The diffusion tensor is set to be $\vect K_i = k_i\,\vect I$, $k_1 = 10, k_2 = 0.002$, and $k_3 = 1$.
 
@@
 
-We first compute solution $p_*$ to the problem~(\ref{dual_transient}) using $P2$ finite element method on sufficiently fine mesh consisting of 4\,908 triangles.
+We first compute solution $p_*$ to the problem~(\ref{dual_transient}) using $P_2$ finite element method on sufficiently fine mesh consisting of 4\,908 triangles.
 This mesh is illustrated in Figure~\ref{fig:transient:ref} (left).
@@
 The fine mesh contains 50 multi-material cells and no three material macro-faces.
-For all these methods we use 20 time frames, $\Delta t = T / 20$.
+For all these methods we use 20 time steps, $\Delta t = T / 20$.
 Results are shown in Figures~\ref{fig:transient:comp}\,--\,\ref{fig:transient:err}.
@@
 	\caption{Comparison of the discrete solutions~$p_h$ for~$h = 1.5 \times 10^{-1}$, $t = 1.25$ \label{fig:transient:comp}}
+\end{figure}
+\begin{figure}[h]
  	\centering
@@
 \end{figure}
-
-\clearpage
 

### 2019-01-26 asc.tex
Fix matrix assembly description

@@
 For the corresponding vectors of unknowns  ${\vect \lambda}_\mmesh = \{ \lambda_{j\,i}(\mmesh) \}$ and ${\vect \lambda}_\bcell = \{ \lambda^{(0)}_{j}(\bcell) \} \cup \{ \lambda^{(1)}_{j}(\bcell) \}$ this defines
-	the matrix $\vect R_\mmesh$ through~\eqref{asc_lambda}. For the example in Figure~\ref{fig:asc_dofs:asc1:mmc} (left), $\vect R_\mmesh$ is given by
+	the matrix $\vect R_\mmesh$ through~\eqref{asc_lambda}. For the example in Figure~\ref{fig:asc_dofs:asc1:mmc} (left and right) we have
 	\begin{equation*}\footnotesize
@@
 			0 & 0 & 0 & 0 & 0 & 0 & 1
-		\end{pmatrix}.		
+		\end{pmatrix},
+		\quad
+		\vect \lambda_\mmesh = 
+		\begin{pmatrix}
+			\lambda_{11}(\mmesh) \\
+			\lambda_{12}(\mmesh) \\
+			\lambda_{13}(\mmesh) \\
+			\lambda_{21}(\mmesh) \\
+			\lambda_{22}(\mmesh) \\
+			\lambda_{23}(\mmesh) \\
+			\lambda_{31}(\mmesh) \\
+			\lambda_{32}(\mmesh) \\
+			\lambda_{41}(\mmesh) \\
+		\end{pmatrix};	
 	\end{equation*}
+	for the moment d.o.f. we have
+	\begin{align*}\footnotesize
+		\vect \lambda_\bcell =& 
+		\left(
+			\lambda^{(0)}_1(\bcell),\,
+			\lambda^{(1)}_1(\bcell),\,
+			\lambda^{(0)}_2(\bcell),\,
+			\lambda^{(1)}_2(\bcell),\,
+			\lambda^{(0)}_3(\bcell),\,
+			\lambda^{(1)}_3(\bcell),\,
+			\lambda^{(0)}_4(\bcell)
+		\right)^T
+		\text{ and} \\
+		&\left(
+			\lambda^{(0)}_1(\bcell),\,
+			\lambda^{(1)}_1(\bcell),\,
+			\lambda^{(0)}_2(\bcell),\,
+			\lambda^{(1)}_2(\bcell),\,
+			\lambda^{(0)}_3(\bcell),\,
+			\lambda^{(1)}_3(\bcell),\,
+			\lambda^{(0)}_4(\bcell),\,
+			\lambda^{(1)}_4(\bcell)
+		\right)^T		
+	\end{align*}
+	for Figure~\ref{fig:asc_dofs:asc1:mmc} (left) and Figure~\ref{fig:asc_dofs:asc1:mmc} (right), respectively.
 For ASC(0) the matrix $\vect R_\mmesh$  is as above with rows containing $s_{ij}$-s eliminated.
@@
 The flux continuity over the face $F$ \big(condition~\eqref{flux_cont}\big) yields
-	\begin{equation*}
+	\begin{equation}\label{eq:aux1pre}
 		\left\{\begin{split}
@@
 		%		\sum_{i \in I_{\mfaces^+_F}} u^{\text{ext}}_{\mmesh^+\,i}\,\Delta s^+_i\,|\mfaces^+_{F\,i}| &+ \sum_{i \in I_{\mfaces^-_F}} u^{\text{ext}}_{\mmesh^-\,i}\,\Delta s^-_i\,|\mfaces^-_{F\,i}| = 0,
-	\end{equation*}
+	\end{equation}
 	or in the matrix form
 	\begin{equation}\label{eq:aux1}
-		\left( \vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,{\vect u}^{\text{ext}}_{\mmesh^+} \right)_i + \left( \vect R^T_{\mmesh^-}\,\vect C_{\mmesh^-}\,{\vect u}^{\text{ext}}_{\mmesh^-} \right)_j = 0,
+		\left( \vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,{\vect u}^{\text{ext}}_{\mmesh^+} \right)_{i+m} + \left( \vect R^T_{\mmesh^-}\,\vect C_{\mmesh^-}\,{\vect u}^{\text{ext}}_{\mmesh^-} \right)_{j+m} = 0, \quad m \in \{0, 1\}
 	\end{equation}
 	where $i$ and $j$ are the local indexes of the face $F$ in the cells $T^+$ and $T^-$, respectively.
-For the Neumann part of the boundary of~$\bcell^\pm$ we set $\mfaces_N(\bcell^\pm) \coloneqq \{ f \in \mfaces[ext](\bcell^\pm)\::\:f \subset \partial\Omega_N \}$.
+($m = 0$ corresponds to the first equation in~\eqref{eq:aux1pre} and $m = 1$ corresponds to the second one; further we omit ``$+m$" for simplicity.) For the Neumann part of the boundary of~$\bcell^\pm$ we set $\mfaces_N(\bcell^\pm) \coloneqq \{ f \in \mfaces[ext](\bcell^\pm)\::\:f \subset \partial\Omega_N \}$.
 If $F$ from $T^+$ belongs to the Neumann part of the boundary, then we have

### 2019-01-26 asc.tex
Fix a typo

@@
 	\end{equation}
-	where $i$ and $j$ are the local indexes of the face $F$ in the cells $T^+$ and $T^-$, respectively.
-($m = 0$ corresponds to the first equation in~\eqref{eq:aux1pre} and $m = 1$ corresponds to the second one; further we omit ``$+m$" for simplicity.) For the Neumann part of the boundary of~$\bcell^\pm$ we set $\mfaces_N(\bcell^\pm) \coloneqq \{ f \in \mfaces[ext](\bcell^\pm)\::\:f \subset \partial\Omega_N \}$.
+	where $i$ and $j$ are the local indexes of the face $F$ in the cells $T^+$ and $T^-$, respectively ($m = 0$ corresponds to the first equation in~\eqref{eq:aux1pre} and $m = 1$ corresponds to the second one; further we omit ``$+m$" for simplicity).
+For the Neumann part of the boundary of~$\bcell^\pm$ we set $\mfaces_N(\bcell^\pm) \coloneqq \{ f \in \mfaces[ext](\bcell^\pm)\::\:f \subset \partial\Omega_N \}$.
 If $F$ from $T^+$ belongs to the Neumann part of the boundary, then we have
@@
 		\left( \vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,{\vect u}^{\text{ext}}_{\mmesh^+} \right)_i = \left( \vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,{\vect g}_{N\,\mmesh^+} \right)_i, \quad
-		{\vect g}_{N\,\mmesh^+} \coloneqq \left\{ \int_f g_N\,s_k \diff{l}\,/\,|f| \right\}_{f\,\in\,\mfaces_N(\bcell^+),\:k\,\in\,\{0,\,1\}}.
+		{\vect g}_{N\,\mmesh^+} \coloneqq \left\{ \int_f g_N\,s_m \diff{l}\,/\,|f| \right\}_{f\,\in\,\mfaces_N(\bcell^+),\:m\,\in\,\{0,\,1\}}.
 	\end{equation*}

### 2019-03-11 Poster/poster.tex
Add poster

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Jacobs Landscape Poster
% LaTeX Template
% Version 1.0 (29/03/13)
%
% Created by:
% Computational Physics and Biophysics Group, Jacobs University
% https://teamwork.jacobs-university.de:8443/confluence/display/CoPandBiG/LaTeX+Poster
% 
% Further modified by:
% Nathaniel Johnston (nathaniel@njohnston.ca)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[final, svgnames]{beamer}

\usepackage[scale=1.24]{beamerposter} % Use the beamerposter package for laying out the poster

% \usetheme{confposter} % Use the confposter theme supplied with this template

\setbeamercolor{block title}{fg=Blue,bg=white} % Colors of the block titles
\setbeamercolor{block body}{fg=black,bg=white} % Colors of the body of blocks
\setbeamercolor{block alerted title}{fg=white,bg=dblue!70} % Colors of the highlighted block titles
\setbeamercolor{block alerted body}{fg=black,bg=dblue!10} % Colors of the body of highlighted blocks
% Many more colors are available for use in beamerthemeconfposter.sty

%-----------------------------------------------------------
% Define the column widths and overall poster size
% To set effective sepwid, onecolwid and twocolwid values, first choose how many columns you want and how much separation you want between columns
% In this template, the separation width chosen is 0.024 of the paper width and a 4-column layout
% onecolwid should therefore be (1-(# of columns+1)*sepwid)/# of columns e.g. (1-(4+1)*0.024)/4 = 0.22
% Set twocolwid to be (2*onecolwid)+sepwid = 0.464
% Set threecolwid to be (3*onecolwid)+2*sepwid = 0.708

\newlength{\sepwid}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
\setlength{\paperwidth}{48in} % A0 width: 46.8in
\setlength{\paperheight}{36in} % A0 height: 33.1in
\setlength{\sepwid}{0.015\paperwidth} % Separation width (white space) between columns
\setlength{\onecolwid}{0.2\paperwidth} % Width of one column
\setlength{\twocolwid}{0.464\paperwidth} % Width of two columns
\setlength{\threecolwid}{0.708\paperwidth} % Width of three columns
\setlength{\topmargin}{-0.5in} % Reduce the top margin size
%-----------------------------------------------------------

\usepackage{graphicx}  % Required for including images

\usepackage{booktabs} % Top and bottom rules for tables

%----------------------------------------------------------------------------------------
%	TITLE SECTION 
%----------------------------------------------------------------------------------------

\title[ASC($n$) Method]{Generalized  Approximate  Static  Condensation  Method  for  a  Heterogeneous  Multi-material Diffusion Problem}
\author[Alexander Zhiliakov]{
	\small{\underline{Alexander Zhiliakov}\inst{1}, Daniil Svyatsky\inst{2}, Maxim Olshanskii\inst{1}, Eugene Kikinzon\inst{2}, Mikhail Shashkov\inst{2}}
	\vskip -1mm
}
\institute[UH, LANL] {
	\begin{tabular}[.8]{c c c}
		\inst{1}Department of Mathematics & \qquad & \inst{2}Los Alamos \\
		University of Houston & & National Laboratory \\
		\includegraphicsw[.2]{logo_uh.png} & & \includegraphicsw[.2]{logo_lanl.png}
	\end{tabular}
	\vskip 3mm
	\tiny{This work was performed under the auspices of the US Department of Energy at Los Alamos National Laboratory under contract DE-AC52-06NA25396; LA-UR-19-20919} 
}

%----------------------------------------------------------------------------------------

% bold for everything
\usepackage{bm}
% lowercase mathcal font
\usepackage{dutchcal}
\hypersetup{
	colorlinks,
	allcolors=.,
	urlcolor=blue,
	filecolor=blue
}
% braces for subeqns and boxes
\usepackage{empheq}
% http://mirror.hmc.edu/ctan/macros/latex/contrib/mathtools/empheq.pdf
\newcommand*\widefbox[1]{\fbox{\hspace{1em}#1\hspace{1em}}}
% hl
\usepackage{soul}
\makeatletter
\let\HL\hl
\renewcommand\hl{%
	\let\set@color\beamerorig@set@color
	\let\reset@color\beamerorig@reset@color
	\HL}
\makeatother
% sub figures / grids of pictures
\usepackage{subcaption} 
\graphicspath{{../img/}} % includegraphics path
\newcommand{\includegraphicsw}[2][1.]{\includegraphics[width=#1\linewidth]{#2}}
\newcommand{\svginputw}[2][\linewidth]{\def\svgwidth{#1}\input{../img/#2}} % pdf_tex path
% tables
\let\oldtabular\tabular
\renewcommand{\tabular}[1][1.5]{\def\arraystretch{#1}\oldtabular}
\usepackage{hhline}
\usepackage{multirow}
% \coloneqq
\usepackage{mathtools}
% math commands for convinience
\DeclareMathOperator{\argmin}{arg\,min}
% bold vectors
\newcommand{\vect}[1]{\boldsymbol{\mathbf{#1}}}

\newcommand{\bcell}{T}
\newcommand{\bmesh}{{\vect{\mathcal T}}}
\newcommand{\mmesh}{{\vect{\mathcal \tau}}}
\newcommand{\bfaces}[1][]{{\vect{\mathcal F}_{\text{#1}}}}
\newcommand{\mfaces}[1][]{{\vect{\mathcal f}_{\text{#1}}}}

\newcommand{\LTwo}{{\mathbb L^2}}
\newcommand{\lTwo}{{\mathcal l^2}}
\newcommand{\HDiv}{{\mathbb H_\text{div}}}
\newcommand{\Rn}[1]{{\mathbb R^{#1}}}
\newcommand{\Pn}[1]{{\mathbb P^{#1}}}
\newcommand{\LTwoSpace}[1][\Omega]{{\mathbb L^2\left({#1}\right)}}
\newcommand{\HSpace}[1]{{\mathbb H^{#1}\left(\Omega\right)}}
\newcommand{\lTwoSpace}[1][\Omega]{{\mathcal l^2\left({#1}\right)}}
\newcommand{\HDivSpace}[1][\Omega]{{\mathbb H_\text{div}\left({#1}\right)}}
\newcommand{\PnSpace}[2]{{\mathbb P^{#1}\left({#2}\right)}}

\newcommand{\errlTwo}[1]{e^{\lTwo}_{#1}}
\newcommand{\errInf}[1]{e^{\infty}_{#1}}

% differentials
\newcommand*\diff{\mathop{}\!\mathrm{d}}
\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}

\DeclareMathOperator{\Ker}{Ker}

\newcommand{\Ltwo}{\mathbb L^2}
\newcommand{\LSpace}[1][\Omega]{\mathbb L^2\left({#1}\right)}

\newenvironment{braced}
{\par\smallskip\hbox to\columnwidth\bgroup
	\hss$\left\{\begin{minipage}{\columnwidth}}
{\end{minipage}\right.$\hss\egroup\smallskip}

% https://tex.stackexchange.com/a/160827/135296
\newcommand\Wider[2][3em]{%
	\makebox[\linewidth][c]{%
		\begin{minipage}{\dimexpr\textwidth+#1\relax}
			\raggedright#2
		\end{minipage}%
	}%
}

\setbeamercolor{block body example}{bg=red!20!white}
\setbeamercolor{block title example}{fg=red, bg=red!40!white}

\begin{document}

\addtobeamertemplate{block end}{}{\vspace*{2ex}} % White space under blocks
\addtobeamertemplate{block alerted end}{}{\vspace*{2ex}} % White space under highlighted (alert) blocks

\setlength{\belowcaptionskip}{2ex} % White space under figures
\setlength\belowdisplayshortskip{2ex} % White space under equations

\begin{frame}[t] % The whole poster is enclosed in one beamer frame

\begin{columns}[t] % The whole poster consists of three major columns, the second of which is split into two columns twice - the [t] option aligns each column's content to the top

\begin{column}{\sepwid}\end{column} % Empty spacer column

\begin{column}{\onecolwid} % The first column

%----------------------------------------------------------------------------------------
%	OBJECTIVES
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

{\Large \textcolor{Blue}{Generalized  Approximate  Static  Condensation  Method  for  a  Heterogeneous  Multi-material Diffusion Problem}}
\vskip .45cm
\underline{Alexander Zhiliakov} (alex@math.uh.edu), Daniil Svyatsky, Maxim Olshanskii, Eugene Kikinzon, Mikhail Shashkov
\vskip .45cm

\begin{block}{Problem Setting}

Our objective is to solve the diffusion problem in the mixed form
\begin{empheq}[left = \empheqlbrace]{alignat=2}
\vect K^{-1}\,\vect u &+ \nabla\,p\,&= 0&\quad\text{in } \Omega \subset \Rn{2}, \nonumber \\
\nabla\cdot\vect u    &+ c\,p       &= f&\quad\text{in } \Omega, \nonumber
\end{empheq}
with boundary data
\begin{equation*}
p = g_D \quad\text{on } \partial\Omega_D, \quad
\vect u \cdot \hat{\vect n} = g_N \quad\text{on } \partial\Omega_N.
\end{equation*}
\textbf{Challenges}:
\begin{itemize}
	\item The diffusion tensor~$\vect K$ may sharply vary in~$\Omega$ and may be discontinuous
	\item We want to use general polygonal meshes, and
	\item \textcolor{Red}{be able to handle material interfaces not aligned with the mesh}  
\end{itemize}

\begin{figure}
	\centering
	\begin{subfigure}{.33\linewidth}
		\centering
		\includegraphicsw{ring_base_voronoi.png}
		\caption{Macro-mesh~$\bmesh$}
	\end{subfigure}%
	\hfill
	\begin{subfigure}{.33\linewidth}
		\centering
		\includegraphicsw{ring_mmcs_voronoi.png}
		\caption{Multi-mat. cells}
	\end{subfigure}%
	\hfill
	\begin{subfigure}{.33\linewidth}
		\centering
		\includegraphicsw{ring_mini_voronoi.png}
		\caption{MOF}
	\end{subfigure}
\end{figure}
Moment-of-fluid interface reconstruction $\Rightarrow$ reconstructed interface may be discontinuous

\begin{columns}
	\begin{column}{.4\textwidth}
		\begin{flushright}
			Consider $T \in \bmesh_H$:
		\end{flushright}
	\end{column}%
	\begin{column}{.35\textwidth}
		\begin{empheq}[left = \empheqlbrace]{alignat=2}
		\vect K^{-1}\,\vect u &+ \nabla\,p\,    &= 0       &\quad\text{in } T, \nonumber \\
		\nabla\cdot\vect u    &+ c\,p           &= f       &\quad\text{in } T, \nonumber \\
		&\phantom{+cc\,}p &= \textcolor{Red}{\lambda} &\quad\text{on } \partial T \nonumber
		\end{empheq}
	\end{column}
	\begin{column}{.25\textwidth}
	\end{column}
\end{columns}
$$\Downarrow$$
		\vskip -3cm
		\begin{figure}
			\begin{subfigure}{.3\linewidth}\centering
				\includegraphicsw[.9]{ring_mini_voronoi_cell.png}
				Minimesh~$\mmesh_h$ of $T$
			\end{subfigure}%
			\begin{subfigure}{.1\linewidth}\centering
				\vskip -1.65cm
				$\Rightarrow\:\,$
			\end{subfigure}%
			\begin{subfigure}{.6\linewidth}\centering
				\begin{exampleblock}{Discretization:}\centering
					Apply Mimetic Finite Difference\\Method\textsuperscript{*}
				\end{exampleblock}
				$\Downarrow$
				\begin{equation*}
				\begin{pmatrix}
				\phantom{-}\vect M_\mmesh & \vect B^T_\mmesh \\
				-\vect B_\mmesh & \vect \Sigma_\mmesh            
				\end{pmatrix} 
				\begin{pmatrix}
				\vect u_\mmesh \\
				\vect p_\mmesh        
				\end{pmatrix}
				= 
				\begin{pmatrix}
				\vect E_\mmesh\,\vect C_\mmesh\,\textcolor{Red}{\vect \lambda_\mmesh} \\
				\vect f_\mmesh        
				\end{pmatrix}
				\end{equation*}		
			\end{subfigure}%
		\end{figure}
		\setul{1pt}{.4pt} % https://tex.stackexchange.com/questions/50637/closer-underline
		\tiny{
			\textsuperscript{*}L.\,Beirao da Veiga, K.\,Lipnikov, G.\,Manzini\\
			$\:$\href{https://www.springer.com/us/book/9783319026626}{\ul{The Mimetic Finite Difference Method for Elliptic Problems}}\\
			$\:$Springer 2014
		}
\end{block}

\begin{block}{Description of the Method}

		If one knows the \textcolor{Red}{pressure trace~$\lambda$} for each~$T \in \bmesh$, one can recover the solution in~$\bmesh$. The idea is \textbf{(i)} to express external flux DOFs in terms of \textcolor{Red}{trace DOFs} (\textit{static condensation}),
$$
\vect u^\text{ext}_\mmesh \coloneqq \vect E_\mmesh^T\,\vect u_\mmesh = \vect A_\mmesh\,\vect C_\mmesh\,\textcolor{Red}{\vect \lambda_\mmesh} - \vect a_\mmesh,
$$
and \textbf{(ii)} to get the system for \textcolor{Red}{trace DOFs} by requiring weak continuity of fluxes. \textbf{Problem}: we may have different number of \textcolor{Red}{trace DOFs} from~$T^+$ and~$T^-$.	
%\begin{figure}
%	\centering
%	%\caption{MMCs: $3 = \#\,\mfaces^+_F \ne \#\,\mfaces^-_F = 2$, $\nu_F = 3$}
%	\svginputw[.6\linewidth]{e_plus_e_minus.pdf_tex}
%\end{figure}
		\textbf{Solution}: approximate a pressure trace on~$F$ with a polynomial~$\lambda_F \in \PnSpace{n}{F}$ described in terms of its~$(n+1)$ moments
\begin{equation*}
\lambda^{(i)}_F=\frac{\int_F  \lambda\,s_i \diff l}{|F|}, \quad i = 0, \dots, n.
%\frac{\int_F \hat \lambda\,s_i \diff l}{|F|}, \quad i = 0, \dots, n.
\end{equation*}
Here~$s_i \in \PnSpace{i}{F}$ is a fixed polynomial of degree~$i$ such that~$s_i \perp_\LTwo s_j$, $j < i$
\end{block}

%----------------------------------------------------------------------------------------

\end{column} % End of the first column

\begin{column}{\sepwid}\end{column} % Empty spacer column

\begin{column}{\onecolwid} % Begin (column 2)

%----------------------------------------------------------------------------------------
%	METHODS
%----------------------------------------------------------------------------------------

\begin{block}{Description of the Method (cont.)}
\begin{figure}
	\begin{subfigure}{.05\textwidth}
		\rotatebox{90}{\textcolor{Red}{DOFs}}
	\end{subfigure}%
	\begin{subfigure}{.95\textwidth}
		\begin{braced}
			Now we express trace DOFs on mini\,faces of~$\mmesh$ via coarse trace DOFs~$\coloneqq (n+1)$~moments on each base\,face of~$T$,
			\begin{align*}
			\vect \lambda_\mmesh &= \vect R_\mmesh\,\vect \lambda_T \quad \Rightarrow \\
			\vect u^\text{ext}_\mmesh &= \vect A_\mmesh\,\vect C_\mmesh\,\vect R_\mmesh\,\vect \lambda_T - \vect a_\mmesh,
			\end{align*}  
		\end{braced}
	\end{subfigure}
	\begin{subfigure}{.05\textwidth}
		\rotatebox{90}{\textcolor{Red}{Constraints}}
	\end{subfigure}%
	\begin{subfigure}{.95\textwidth}
		\begin{braced}
			and close the system by requiring weak continuity of normal fluxes on each base face
			\begin{equation*}
			\int_F \vect u|_{T^+}\cdot\hat{\vect n}\,s_i \diff l = \int_F \vect u|_{T^-}\cdot\hat{\vect n}\,s_i \diff l, \: i = 0, \dots, n, F \in \bfaces[int]
			\end{equation*}	
		\end{braced}
	\end{subfigure}
\end{figure}
Express fluxes in terms of traces $\Rightarrow$ get SLAE for coarse trace DOFs

\begin{equation*}
\int_F \vect u|_{T^+}\cdot\hat{\vect n}\,s_i \diff l = \int_F \vect u|_{T^-}\cdot\hat{\vect n}\,s_i \diff l, \: i = 0, \dots, n \text{ for } F \in \bfaces[int]
\end{equation*}
$$\Downarrow$$
\begin{align*}
n = 0: \quad& \sum_{f\in \mfaces_F(T^+)} u^{\text{ext}}_{\mmesh^+}(f)\,|f| + \sum_{f\in \mfaces_F(T^-)} u^{\text{ext}}_{\mmesh^-}(f)\,|f| = 0, \\
n = 1: \quad& \sum_{f\in \mfaces_F(T^+)} u^{\text{ext}}_{\mmesh^+}(f)\,\int_{f} s_1 \diff{l} + \sum_{f\in \mfaces_F(T^-)} u^{\text{ext}}_{\mmesh^-}(f)\,\int_{f} s_1 \diff{l} = 0
\end{align*}
$$\Downarrow$$
\begin{equation*}
\left( \vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,\vect u^{\text{ext}}_{\mmesh^+} \right)_{i+m} + \left( \vect R^T_{\mmesh^-}\,\vect C_{\mmesh^-}\,\vect u^{\text{ext}}_{\mmesh^-} \right)_{j+m} = 0, \quad m \in \{0, 1\}
\end{equation*}
$$\Downarrow$$
\begin{align*}\small
		\begin{split}
		\Big( \underbrace{\left( \vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,\vect A_{\mmesh^+}\,\vect C_{\mmesh^+}\,\vect R_{\mmesh^+} \right)}_{\vect S_{T^+} \coloneqq} \vect \lambda_{T^+} \Big)_{i+m} 
		&+ 
		\Big( \underbrace{\left( \vect R^T_{\mmesh^-}\,\vect C_{\mmesh^-}\,\vect A_{\mmesh^-}\,\vect C_{\mmesh^-}\,\vect R_{\mmesh^-} \right)}_{\vect S_{T^-} \coloneqq} \vect \lambda_{T^-} \Big)_{j+m} = \\
		\big( \underbrace{\vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,\vect a_{\mmesh^+}}_{\vect s_{T^+}} \big)_{i+m}
		&+
		\big( \underbrace{\vect R^T_{\mmesh^-}\,\vect C_{\mmesh^-}\,\vect a_{\mmesh^-}}_{\vect s_{T^-}} \big)_{j+m}
		\end{split}
\end{align*}
$$\Downarrow$$
\begin{empheq}[box=\widefbox]{align*}
\vect S_\bmesh &= \sum_{T \in \bmesh} \vect N^T_T\,\vect S_T\,\vect N_T, & \normalsize{\text{Global system:}} \\
\vect s_\bmesh &= \sum_{T \in \bmesh} \vect N^T_T\,\vect s_T, & \normalsize{\textcolor{Red}{\vect S_\bmesh\,\vect \lambda_\bmesh = \vect s_\bmesh}}
\end{empheq}\normalsize
\begin{itemize}
	\item \textbf{Theorem}: system matrix~$\vect S_\bmesh$ is sparse and SPD for ASC(0) and ASC(1)
	\item Hence efficient solvers and preconditioners are available (e.\,g. CG + Algebraic Multigrid)
	\item Once we obtain~$\vect \lambda_\bmesh$, we recover pressure and flux DOFs in each cell~$T \in \bmesh$ (this may be done in parallel) 
\end{itemize}
\end{block}

\begin{block}{Numerical Experiments}

\textbf{Algebraic Robustness}. We solve the diffusion problem w/ $\vect K = k\,\vect I$, $k = 1$ on the left part and .1 on the right. Exact solution is piecewise linear
\begin{figure}
	\centering
	\caption{$w \coloneqq$ width of the left minimesh cells}
	\begin{subfigure}{.33\linewidth}
		\centering
		\includegraphicsw{skew1.png}
		\caption{$w = .1$}
	\end{subfigure}%
	\hfill
	\begin{subfigure}{.33\linewidth}
		\centering
		\includegraphicsw{skew01.png}
		\caption{$w = .01$}
	\end{subfigure}%
	\hfill
	\begin{subfigure}{.33\linewidth}
		\centering
		\includegraphicsw{skew001.png}
		\caption{$w = .001$}
	\end{subfigure}
\end{figure}
$\kappa_{\text{ASC(0)}}$ does not depend on $w$, and $\kappa_{\text{ASC(1)}}$ is proportional to $w^{-1}$. However, if we remove 3 smallest eig values (corresponding to 3 int MM faces),

\end{block}

\end{column} % End of the second column

\begin{column}{\onecolwid} % The third column

%----------------------------------------------------------------------------------------
%	CONCLUSION
%----------------------------------------------------------------------------------------

\begin{block}{Numerical Experiments (cont.)}

\textbf{we will have $\tilde{\vect\kappa}_{\text{ASC(1)}} \approx \vect\kappa_{\text{ASC(0)}}$}.
Starting from some iteration CG behaves like extreme eig values are not present; that is, several small eig values is not a problem
\begin{figure}
	\centering
	\caption{Condition Numbers of ASC(0)\,/\,ASC(1) Matrices} 
	\begin{subfigure}{.45\linewidth}
		\centering\tiny
		\begin{tabular}[1.2]{ | c | c | c | c |}
			\hline
			$w$ & $\kappa_{\text{ASC(0)}}$ & $\kappa_{\text{ASC(1)}}$ & $\widetilde\kappa_{\text{ASC(1)}}$\\
			\hline
			$10^{-1}$ & 41.0 & 1\,730       & 41.0  \\
			\hline
			$10^{-2}$ & 45.2 & 2\,817       & 45.1  \\
			\hline
			$10^{-3}$ & 48.3 & 16\,391      & 48.3   \\
			\hline
			$10^{-4}$ & 49.0 & 152\,325     & 49.0    \\
			\hline
			$10^{-5}$ & 49.1 & $1.5\times10^6$&49.1  \\
			\hline
		\end{tabular}%
		%			\begin{tabular}[1.2]{ | c | c | c | }
		%				\hline
		%				$w$ & $\kappa_{\text{ASC(0)}}$ & $\kappa_{\text{ASC(1)}}$ \\
		%				\hline
		%				$10^{-1}$ & 41 & 1\,730 \\ 
		%				\hline
		%				$10^{-2}$ & 45 & 2\,817 \\
		%				\hline
		%				$10^{-3}$ & 48 & 16\,391 \\
		%				\hline
		%				$10^{-4}$ & 49 & 152\,325 \\
		%				\hline
		%				$10^{-5}$ & 49 & $1.5\times10^6$ \\
		%				\hline
		%			\end{tabular}
	\end{subfigure}%
	\hfill
	\begin{subfigure}{.55\linewidth}
		\centering
		\includegraphicsw{logplot.png}
	\end{subfigure}
\end{figure}
If the base mesh consists of triangles + we have no material interfaces, ASC($n$) boils down to Mixed-Hybrid Raviart\,--\,Thomas FEM:
\begin{align*}
\|\vect u - \vect u_h\|_{\LTwoSpace} &\le c\,h\,\|\vect u\|_{\HSpace{1}},\\
\|p - p_h\|_{\LTwoSpace} &\le c \left( h\,\|p\|_{\HSpace{1}} + h^2\,\|p\|_{\HSpace{2}} \right).
\end{align*}
That is, we cannot expect ASC($n$) convergence to be better than linear. We define \textbf{discrete $\LTwo$-norm}
\begin{equation*}
\| v \|_{\lTwoSpace} \coloneqq \| P_h\,v \|_{\LTwoSpace} \le \| v \|_{\LTwoSpace},
\end{equation*} 
where $P_h \coloneqq$ $\LTwo$-projection operator on the space of piecewise constant functions on each cell~$T \in \bmesh$ (or on each~$\tau \in \mmesh$ if $T$ is a MMC)
\vskip 1cm
\textbf{ASC(0) $\rightarrow$ ASC(1): Motivation}. If $\vect K_i \equiv \vect K_j$ and the exact soln is linear, ASC(0) produces errors due to const trace approximation, and ACS(1) recovers the exact soln
\vskip 1cm
\textbf{Piecewise $P_1$ Solution}. We solve the diffusion problem on the sequence of square meshes w/ $\vect K = k\,\vect I$, $k = 1$ on the left part and .1 on the right. Exact solution is piecewise linear
\begin{figure}
	\centering
	\begin{subfigure}{.45\linewidth}
		\centering
		\includegraphicsw{skew_ref.png}
		\caption{Exact soln, $p$}
	\end{subfigure}%
	\hfill
	\begin{subfigure}{.45\linewidth}
		\centering
		\includegraphicsw{skew_geometry_square.png}
		\caption{Materials}
	\end{subfigure}
\end{figure}
{\centering\small
\begin{tabular}[1.2]{| c | c || c | c | c || c | c |}
	\hline
	\multirow{5}{*}{\rotatebox{90}{ASC(0)}} & $h$ & $\errlTwo{p}$ & $\rho_p$ & $\errInf{p}$ & $\errlTwo{u}$ & $\rho_u$ \\
	\cline{2-7}
	& $3.5\times10^{-1}$ & $7.3\times10^{-1}$ &     & 4.8               & $ 6.6\times10^{-1}$ &  \\
	\cline{2-7}
	& $8.8\times10^{-2}$ & $1.6\times10^{-1}$ & 1.1 & 1.2               & $ 3.5\times10^{-1}$ & 0.46 \\ 
	\cline{2-7}
	& $2.2\times10^{-2}$ & $3.7\times10^{-2}$ & 1.1 & $3.4\times10^{-1}$ & $ 1.3\times10^{-1}$ & 0.71 \\ 
	\cline{2-7}
	& $5.5\times10^{-3}$ & $8.9\times10^{-3}$ & 1.0 & $7.9\times10^{-2}$ & $ 4.1\times10^{-2}$ & 0.83 \\
	\hline
	\hline
	\multirow{5}{*}{\rotatebox{90}{ASC(1)}} & $h$ & $\errlTwo{p}$ & $\rho_p$ & $\errInf{p}$ & $\errlTwo{u}$ & $\rho_u$ \\
	\cline{2-7}
	& $3.5\times10^{-1}$ & $2.5\times10^{-2}$ & & $2.9\times10^{-1}$      & $ 4.6\times10^{-2}$ &   \\
	\cline{2-7}
	& $8.8\times10^{-2}$ & $1.9\times10^{-3}$ & 1.84 & $6.6\times10^{-2}$ & $ 2.0\times10^{-2}$ & 0.6 \\
	\cline{2-7}
	& $2.2\times10^{-2}$ & $1.6\times10^{-4}$ & 1.79 & $4.3\times10^{-2}$ & $ 5.5\times10^{-3}$ & 0.93 \\
	\cline{2-7}
	& $5.5\times10^{-3}$ & $1.3\times10^{-5}$ & 1.80 & $2.0\times10^{-2}$ & $ 1.3\times10^{-3}$ & 1.   \\
	\hline
\end{tabular}}
\vskip 1cm
\textbf{Piecewise $P_2$ Solution w/ 3 Materials}. We solve the diffusion problem on triangular meshes w/ $\vect K = k\,\vect I$, $k = 1$ outside the ring and .001 inside. Exact solution is piecewise quadratic
\begin{figure}
	\centering
	\begin{subfigure}{.45\linewidth}
		\centering
		\includegraphicsw{ring_ref_mesh.png}
		\caption{Exact soln, $p$}
	\end{subfigure}%
	\hfill
	\begin{subfigure}{.45\linewidth}
		\centering
		\includegraphicsw{ring_ref_slice.png}
		\caption{$p(x,\frac{1}{2})$}
	\end{subfigure}
\end{figure}

\end{block}

\end{column} % End of the third column

\begin{column}{\sepwid}\end{column} % Empty spacer column

\begin{column}{\onecolwid} % Begin (column 2)

\begin{block}{Numerical Experiments (cont.)}

{\footnotesize
\begin{table}
	\begin{subtable}{.6\linewidth}
		\begin{tabular}[1.1]{| c | c || c | c || c |}
			\hline
			\multirow{7}{*}{\rotatebox{90}{ASC(0)}} & $h$ & $\errlTwo{p}$ & $\rho_p$ & $\errInf{p}$ \\
			\cline{2-5}
			& $3.0\times10^{-1}$ & 4.5 & & 17 \\
			\cline{2-5}
			& $2.5\times10^{-1}$ & 4.5 & & 17 \\
			\cline{2-5}
			& $1.3\times10^{-1}$ & 4.0 & & 17 \\
			\cline{2-5}
			& $8.3\times10^{-2}$ & 4.4 & & 17 \\
			\cline{2-5}
			& \hl{$6.7\times10^{-2}$} & $7.1\times10^{-1}$ & & 4.9 \\
			\cline{2-5}
			& $4.3\times10^{-2}$ & $4.5\times10^{-1}$ & 1.2 & 5.0 \\
			\hline
			\hline
			\multirow{7}{*}{\rotatebox{90}{ASC(1)}} & $h$ & $\errlTwo{p}$ & $\rho_p$ & $\errInf{p}$ \\
			\cline{2-5}
			& $3.0\times10^{-1}$ & $4.5\times10^{-1}$ & & 3.5 \\
			\cline{2-5}
			& $2.5\times10^{-1}$ & $2.6\times10^{-1}$ & 3 & 2.7 \\
			\cline{2-5}
			& $1.3\times10^{-1}$ & $9.2\times10^{-2}$ & 1.5 & $6.2\times10^{-1}$ \\
			\cline{2-5}
			& $8.3\times10^{-2}$ & $4.8\times10^{-2}$ & 1.6 & $8.3\times10^{-1}$ \\
			\cline{2-5}
			& $6.7\times10^{-2}$ & $2.8\times10^{-2}$ & 2.5 & $2.3\times10^{-1}$ \\
			\cline{2-5}
			& $4.3\times10^{-2}$ & $1.0\times10^{-2}$ & 2.3 & $6.3\times10^{-2}$ \\
			\hline
		\end{tabular}%
	\end{subtable}%
	\begin{subtable}{.4\linewidth}
		\begin{tabular}[1.1]{| c | c || c | c || c |}
			\hline
			\multirow{7}{*}{\rotatebox{90}{Arithmetic homo.}} & $h$ & $\errlTwo{\text{p}}$ & $\rho_p$ & $\errInf{p}$ \\
			\cline{2-5}
			& $3.0\times10^{-1}$ & 4.9 & & 17 \\
			\cline{2-5}
			& $2.5\times10^{-1}$ & 5.0 & & 17 \\
			\cline{2-5}
			& $1.3\times10^{-1}$ & 4.9 & & 17 \\
			\cline{2-5}
			& $8.3\times10^{-2}$ & 4.7 & & 17 \\
			\cline{2-5}
			& {$6.7\times10^{-2}$} & 4.4 & & 16 \\
			\cline{2-5}
			& $4.3\times10^{-2}$ & $9.7\times10^{-1}$ & 3.5 & 5.7 \\
			\hline
			\hline
			\multirow{7}{*}{\rotatebox{90}{Harmonic homo.}} & $h$ & $\errlTwo{p}$ & $\rho_p$ & $\errInf{p}$ \\
			\cline{2-5}
			& $3.0\times10^{-1}$ & 2.3 & & 15 \\
			\cline{2-5}
			& $2.5\times10^{-1}$ & 1.7 & 1.6 & 16 \\
			\cline{2-5}
			& $1.3\times10^{-1}$ & $7.3\times10^{-1}$ & 1.2 & 12 \\
			\cline{2-5}
			& $8.3\times10^{-2}$ & $4.8\times10^{-1}$ & 1.0 & 12 \\
			\cline{2-5}
			& $6.7\times10^{-2}$ & $3.4\times10^{-1}$ & 1.6 & 9.4 \\
			\cline{2-5}
			& $4.3\times10^{-2}$ & $1.6\times10^{-1}$ & 1.7 & 8.2 \\
			\hline
		\end{tabular}
	\end{subtable}
\end{table}}
\vskip .45cm
Before \hl{$h = 6.7\times10^{-2}$} we have cells\,/\,faces with 3 materials, and after this mesh level we have only 2 material MMCs
\vskip 1cm
\textbf{Unsteady Problem}. We solve the unsteady diffusion problem on Voronoi meshes w/ $\vect K = k\,\vect I$, $k = .002$ inside the ring, 10 in the inner disk, and 1 elsewhere. We set~$g_D = 1$ on the left bndry and 0 on the right; top and bottom bndries are insulated. Equilibrium state is $p \equiv 1$
\begin{figure}
	\centering
	\begin{subfigure}{.4\linewidth}
		\centering
		\includegraphicsw{transient2/supermesh.png}
		\caption{Conforming mesh}
	\end{subfigure}%
	\hfill
	\begin{subfigure}{.58\linewidth}
		\centering
		\includegraphicsw{transient2/ref_slices.png}
		\caption{Cuts~$p_*\big((x,0.5), t\big)$ of the ref soln}	
	\end{subfigure}
\end{figure}
\begin{figure}
	\centering
	\begin{subfigure}{.25\linewidth}
		\centering
		\includegraphicsw{transient2/movie_frames/ref/frame_1s34.png}
		\caption{\tiny Reference}
	\end{subfigure}%
	\hfill
	\begin{subfigure}{.25\linewidth}
		\centering
		\includegraphicsw{transient2-1/movie_frames/arithmetic_homo/frame_1s43.png}
		\caption{\tiny Arithmetic homo.}	
	\end{subfigure}%
	\hfill
	\begin{subfigure}{.25\linewidth}
		\centering
		\includegraphicsw{transient2-1/movie_frames/harmonic_homo/frame_1s43.png}
		\caption{\tiny Harmonic homo.}	
	\end{subfigure}%
	\par
	\begin{subfigure}{.25\linewidth}
		\centering
		\includegraphicsw{transient2-1/movie_frames/asc0/frame_1s43.png}
		\caption{\tiny ASC(0)}
	\end{subfigure}%
	\hfill
	\begin{subfigure}{.25\linewidth}
		\centering
		\includegraphicsw{transient2-1/movie_frames/asc1/frame_1s43.png}
		\caption{\tiny ASC(1)}	
	\end{subfigure}%
	\hfill
	\begin{subfigure}{.25\linewidth}
		\centering
		\includegraphicsw{transient2-1/movie_frames/asc_diff/frame_1s43.png}
		\caption{\tiny ASC(0,\,1) difference}	
	\end{subfigure}%
\end{figure}\centering
{\small Comparison of the discrete solutions~$p_h$, $h = 1.5 \times 10^{-1}$, $t = 1.25$}

\end{block}

\begin{block}{Summary}

\begin{itemize}
	\item ASC($n$) is able to efficiently handle unfitted material interfaces 
	\item 2\textsuperscript{nd} order $\lTwo$-convergence for ASC(1) 
	\item Effective condition number seems to be uniformly bounded w.r.t. an interface position
	\item The underline matrix is SPD and sparse; its pattern does not depend on mini\,meshes
	\item A.\,Zhiliakov et al. \href{https://www.researchgate.net/publication/330912268_A_higher_order_approximate_static_condensation_method_for_multi-material_diffusion_problems}{\ul{A higher order approximate static condensation method for multi-material diffusion problems}}, 2019 (JCP preprint)
	\item \textbf{TODO List}: Anisotropic diffusion: homogenization is not applicable; what about ASC($n$)? Extension to 3D? 
\end{itemize}
\vskip .45cm 
\small This work was performed under the auspices of the US Department of Energy at Los Alamos National Laboratory under contract DE-AC52-06NA25396; LA-UR-19-20919
\end{block}

\end{column} % End of the second column

\end{columns} % End of all the columns in the poster
\end{frame} % End of the enclosing frame

\end{document}

### 2019-06-06 answer_to_reviewers.tex
Add the answer to reviewers

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[dvips]{epsfig}
\usepackage{graphicx}%,amsmath,amsthm,amsfonts,cite}
\usepackage{showkeys}
\usepackage{subfigure}
\usepackage{epsfig}
\usepackage{color}
\usepackage{hyperref}
%\usepackage{nath}

\newcommand{\anna}[2][cyan]{\emph{\textcolor{#1}{#2}}}
\definecolor{blueg}{rgb}{0.2, 0.2, 0.6}
\newcommand{\gp}[2][blueg]{\emph{\textcolor{#1}{#2}}}
\newcommand{\stef}[2][red]{\emph{\textcolor{#1}{#2}}}
\textwidth=15.5cm
\textheight=22.0cm
\hoffset=-1.2cm
\voffset=-2.3cm
\parskip=10pt
\parindent=0pt
\def\rc#1{\textcolor{red}{#1}}

\usepackage{soul} % https://tex.stackexchange.com/a/260567/135296
\DeclareRobustCommand{\hlcyan}[1]{{\sethlcolor{cyan}\hl{#1}}}

%\include{commands.tex}

\usepackage{dutchcal}
\newcommand{\vect}[1]{\boldsymbol{\mathbf{#1}}}
\newcommand{\mfaces}[1][]{{\vect{\mathcal f}_{\text{#1}}}}
\newcommand{\bfaces}[1][]{{\vect{\mathcal F}_{\text{#1}}}}

%\pagestyle{empty}
\begin{document}

\centerline{
{\Large {A. Zhiliakov, D. Svyatskiy, M.Olshanskii, E. Kikinzon, M. Shashkov}}}

%\centerline{
%{\Large {SISC manuscript \#M116618}}
%}

Reviewer 1 requested no modifications to the manuscript. Thus, in this documents we are  addressing the points raised by Reviewer 2.

\textbf{Answer to Reviewer 2}

The authors would like to thank the Reviewer for his comments and
suggestions which we think improved the manuscript.
Our revised article has been modified accordingly, with the changes \hlcyan{highlighted in blue}.
%We have modified the manuscript accordingly. The changes in the manuscript are highlighted in red.
%We hope that the manuscript is now acceptable for publication in SISC.

%With this revision we also supply  supplementary material with the full animation of experiments 7.2 and 7.3.

A summary of the modifications is presented below.  In the following
we use italic font to quote the Reviewer.

\emph{(1) Page 1, paragraph 2: ``growth in developing of efficient computational techniques," change to ``growth in the development of efficient computational techniques."}

Fixed.

\emph{(2) Page 5, paragraph 1: ``We shall distinct between the subset of internal and external faces." Should change ``distinct" to ``distinguish."}

Fixed.

\emph{(3) Page 6, right above equation (7): ``we need to distinct the vector" should be changed to ``we need to distinguish the vector"}

Fixed.

\emph{(4) Page 7: ``However, we cannot do this in a straightforward way, since the discontinuity of material interfaces across the macro-mesh faces may lead to a mismatch of discrete fluxes... including different space dimensions." This sentence can be written more clearly. In particular, the phrase ``including different space dimensions" is a bit confusing. I think you are alluding to the fact that neighboring macro cells $T^{+}$ and $T^{-}$ that share a macro-face in $\bfaces_{\text{int}}$ can have different numbers of (mini) faces that make up the macro-face (i.e., $\#\mfaces[ext](T^+) \neq \#\mfaces[ext](T^-)$), and therefore the concentration vectors~$\vect \lambda_{\boldsymbol{\tau}}$, restricted to each macro-face, can be of different sizes (and, even if the sizes are the same, the location of the faces will be different and so matching these values is not trivial). You might want to put in a sentence or two spelling this out more, and perhaps point to Figure 2 in the description. Introducing the phrase ``micro-face" and the notation $\mfaces[ext](T^+)$, etc., earlier, as done on page 7, will help with the clarity.}

We elaborated on this (page 7, paragraph 3) and added Figure 3 to illustrate d.o.f. mismatch.

\emph{(5) Page 7, just below equation (11): ``... is the set of $L_{2}\left(\Omega\right)$-orthogonal polynomials on $F$ of degree $n$." Since $\Omega$ is the entire spatial domain and the functions $s_{i}$ are polynomials defined only on each macro-face $F$ (and not on $\Omega$), shouldn't this be $L_{2}\left(F\right)$ instead of $L_{2}\left(\Omega\right)$?}

Indeed, it should be~$L_{2}\left(F\right)$. Fixed.

\emph{(6) On Page 7, you refer (I think) for the first time to faces in $\bfaces[int]$ as macro-faces and faces in $\mfaces(T)$ as mini-faces. Although it is pretty clear what you mean, if this is indeed the first time you define these terms, then they should be defined earlier in Section 3. In particular, in Section 3 you refer to mini-faces as faces. Making this distinction early on would actually make the descriptions in Section 3 more clear.}

We added the explanation for what we mean by ``mini-faces" and ``macro-faces" to the beginning of Section 3 (page 6, paragraph 1).

\emph{(7) Page 10, going from (18) to (19): you introduce $\mathbf{C}_{\boldsymbol{\tau}}$ on page 6 only as ``the mass matrix for $\vect \lambda_{\boldsymbol{\tau}}$ unknowns." It is hard for me, from this minimal description, to see that equation (18) is the equation (19) written in matrix form. Can you add more detail in the description of $\mathbf{C}_{\boldsymbol{\tau}}$ to help clarify this? In particular, an extra few sentences of detail would be very helpful here, to make the exposition more self-contained.}

We made the definition of~$\vect C_{\boldsymbol{\tau}}$ more precise (page 6, below equation (6)). We also added equation~(18) on page 9 where we precisely defined ``signed distances" to make the flux continuity condition written in the matrix form more transparent. Hence ``equation (18) is the equation (19) written in matrix form" now reads as ``equation (19) is the equation (20) written in matrix form."

We simplified the second continuity condition in (19), page 10, by integrating the first moment~$s_1$. This makes it easy to see the matrix form in the equation~(20).

\emph{(8) Page 11: ``Clearly, matrix $\mathbf{R}_{\boldsymbol{\tau}}$ has a non-trivial kernel iff $s_{ki}=s_{kj}, \quad i,j=1,\ldots,m_{k}$. Shouldn't it be: iff there is a $k$ such that $s_{ki}=s_{kj}$ for some $i$ and $j$? For example, $\mathbf{R}_{\boldsymbol{\tau}}$ just below equation (17) shares two rows and so is singular if, e.g., $s_{21}=s_{22}$.}

After the previous correction, ``$\mathbf{R}_{\boldsymbol{\tau}}$ just below equation (17) shares two rows and so is singular if, e.g., $s_{21}=s_{22}$" reads as ``$\mathbf{R}_{\boldsymbol{\tau}}$ just below equation (18) shares two rows and so is singular if, e.g., $s_{21}=s_{22}$."

Matrix~$\mathbf{R}_{\boldsymbol{\tau}}$ is not singular for it is not square. We only prove that it has a trivial kernel, i.e. its columns are linearly independent. So no changes are needed here.

\emph{``It is important to take into accont", page 15, accont => account"}

\textbf{Other minor changes}

The changes are \hl{highlighted in yellow}.

(1) Page 2, paragraph 2: ``standard discretization thechniques" changed to ``standard discretization techniques."

\end{document}

### 2019-06-06 asc.tex
Add the answer to reviewers

@@
 \usepackage[dvipsnames, table]{xcolor}{\rm }
+\usepackage{soul} % https://tex.stackexchange.com/a/260567/135296
+\DeclareRobustCommand{\hlcyan}[1]{{\sethlcolor{cyan}\hl{#1}}}
 
@@
 
-	Past decades evidenced an explosive growth in developing of efficient computational techniques for problems with evolving interfaces, which involve interaction between many materials or different phases of matter.
+	Past decades evidenced an explosive \hlcyan{growth in the development of efficient computational techniques} for problems with evolving interfaces, which involve interaction between many materials or different phases of matter.
 These developments include immersed boundary method~\cite{peskin2002immersed}, immersed interface method~\cite{leveque1994immersed}, and unfitted finite element methods \cite{belytschko2009review,burman2015cutfem}, to name several popular numerical approaches.
@@
 In this approach, one assigns to the cells  artificial homogeneous  material properties, which are calculated based on the volumetric shares of different materials in each of the multi-material cells.
-This enables one to apply standard discretization thechniques.
+This enables one to apply standard discretization \hl{techniques}.
 %if one needs to solve for other physics, such as the heat transfer, on every time step of the simulation.
@@
 	Denote by $\bfaces$ the collection of all faces of the macro-mesh $\bmesh$.
-We shall distinct between the subset of internal and external faces,  $\bfaces = \bfaces[int] \cup \bfaces[ext]$\footnote{For the sake of  notation, we shall use~$\bfaces$ to denote both the set of elements and the corresponding domain formed by their union~$\cup_{F\in \bfaces} \bar{F}$; same for $\bfaces[int]$, $\bfaces[ext]$ and other collections of mesh elements introduced later in the text.
+\hlcyan{We shall distinguish between the subset of internal and external faces},  $\bfaces = \bfaces[int] \cup \bfaces[ext]$\footnote{For the sake of  notation, we shall use~$\bfaces$ to denote both the set of elements and the corresponding domain formed by their union~$\cup_{F\in \bfaces} \bar{F}$; same for $\bfaces[int]$, $\bfaces[ext]$ and other collections of mesh elements introduced later in the text.
 The meaning should be clear from a context.}.
@@
 We denote by $\mfaces(T)$ the set of all faces in $\mmesh(T)$, which collects both   internal and boundary (external) faces with respect to $T$,  $\mfaces(T) = \mfaces[int](T) \cup \mfaces[ext](T)$.
-Thus for the example of local mesh drafted in Figure~\ref{fig:mmesh}, we have three elements in $\mmesh(T)$, two internal faces from $\mfaces[int](T)$ and eleven external faces from $\mfaces[ext](T)$.
+\hlcyan{If the meaning is not clear from the context, we will refer to elements of~$\mfaces(T)$ as ``mini-faces," and to elements of~$\bfaces$ as ``macro-faces."} Thus for the example of local mesh drafted in Figure~\ref{fig:mmesh}, we have three elements in $\mmesh(T)$, two internal faces from $\mfaces[int](T)$ and eleven external faces from $\mfaces[ext](T)$.
 It is clear that this local mesh is fitted to the material interfaces.
@@
 	\end{equation}
-	Here $\vect M_\mmesh$, $\vect\Sigma_\mmesh$, $\vect B^T_\mmesh$, $-\vect B_\mmesh$ are vector-mass, mass, gradient and divergence matrices, respectively; $-\vect C_\mmesh$ is a diagonal scaling matrix, i.e.
-the mass matrix for ${\vect \lambda}_\mmesh$ unknowns;
+	Here $\vect M_\mmesh$, $\vect\Sigma_\mmesh$, $\vect B^T_\mmesh$, $-\vect B_\mmesh$ are vector-mass, mass, gradient and divergence matrices, respectively; \hlcyan{$-\vect C_\mmesh$ is a diagonal scaling matrix that has mini-faces' measures~$|f|$ on the diagonal, $f \in \mfaces[ext](T)$, i.e.
+the mass matrix for ${\vect \lambda}_\mmesh$ unknowns};
 	$\vect E_\mmesh \in \mathbb{R}^{n_f \times n_\lambda}$ is a rectangular matrix with 0 and 1 entries which sparsifies a vector from  $\mathbb{R}^{n_{\lambda}}$
@@
 
-	Since the continuity of flux condition \eqref{flux_cond} and boundary conditions are enforced on  the \emph{external} edges of $T$, we need to distinct the vector ${\vect u}^\text{ext}_\mmesh$ of fluxes on $\mfaces[ext](T)$, which is just a trivial restriction of ${\vect u}_\mmesh$ on the edges  from $\mfaces[ext](T)$,
+	Since the continuity of flux condition \eqref{flux_cond} and boundary conditions are enforced on  the \emph{external} edges of $T$, \hlcyan{we need to distinguish the vector} ${\vect u}^\text{ext}_\mmesh$ of fluxes on $\mfaces[ext](T)$, which is just a trivial restriction of ${\vect u}_\mmesh$ on the edges  from $\mfaces[ext](T)$,
 	\begin{equation}\label{system_mini}
@@
 	Next, we should use the continuity of flux condition \eqref{flux_cond} and boundary conditions to obtain a complete system for ${\vect u}^\text{ext}_\mmesh$ and ${\vect \lambda}_\mmesh$.
-However, we cannot do this in a straightforward way, since the discontinuity of material interfaces across the macro-mesh faces may lead to a mismatch of discrete fluxes from two sides of $F\in\bfaces[int]$, including different space dimensions.
-	Therefore, we shall enforce the flux continuity condition in the spirit of the mortar finite element method~\cite{mortar} using the space of functions defined on $\bfaces[int]$, which are polynomials of degree at most $n$ on every $F\in\bfaces[int]$, an analog of the Lagrange multiplier space in the mortar method:
+However, we cannot do this in a straightforward way, since the discontinuity of material interfaces across the macro-mesh faces may lead to a mismatch of discrete fluxes from two sides of $F\in\bfaces[int]$.
+\hlcyan{We elaborate on this below.}
+
+	\hlcyan{For $F \in \bfaces[int]$ shared by two polygonal cells~$\bcell^\pm\in \bmesh$ denote by~$\mfaces_F(T^\pm) \subset \mfaces_{\text{ext}}(T^\pm)$ the subsets of mini-faces that belong to the macro-face~$F$ from each side.
+In general, $\mfaces_F(T^+)$ and $\mfaces_F(T^-)$ can have different numbers of mini-faces that make up the macro-face~$F$, i.e.
+$\#\,\mfaces_F(T^+) \ne \#\,\mfaces_F(T^+)$, and hence the restrictions of concentration vectors~${\vect \lambda}_\mmesh$ and fluxes vectors~${\vect u}^\text{ext}_\mmesh$ can be of different sizes.
+Moreover, even if~$\#\,\mfaces_F(T^+) = \#\,\mfaces_F(T^+)$, locations of the mini-faces may be different due to volume- or moment-of-fluid interface reconstruction.
+See an example on Figure~{\ref{fig:mismatch}}.}
+
+	\begin{figure}[h]
+		\begin{subfigure}{.49\linewidth}
+			\svginputw{e_plus_e_minus.pdf_tex}
+		\end{subfigure}%
+		\quad
+		\begin{subfigure}{.49\linewidth}
+			\hlcyan{We have $3 = \#\,\mfaces_F(T^+) \ne \#\,\mfaces_F(T^+) = 2$. Note also that locations of mini-faces corresponding to the same material are different from each side of~$F$}
+		\end{subfigure}
+		\caption{\hlcyan{Example of the mismatch of discrete fluxes from two sides of $F\in\bfaces[int]$}}
+		\label{fig:mismatch}
+	\end{figure}
+
+	\hlcyan{This makes matching concentration and fluxes values not trivial.} Therefore, we shall enforce the flux continuity condition in the spirit of the mortar finite element method~\cite{mortar} using the space of functions defined on $\bfaces[int]$, which are polynomials of degree at most $n$ on every $F\in\bfaces[int]$, an analog of the Lagrange multiplier space in the mortar method:
 	\[
@@
 	\]
-
-	%	Let $F \coloneqq {\bcell^+} \cap {\bcell^-}$, $F \in \bfaces[int]$, be a face shared by base\,cells~$\bcell^+$ and~${\bcell^- \in \bmesh}$ with mini\,meshes~$\mmesh^\pm$ and mini\,faces~$\mfaces^\pm$, respectively.
-We denote by~$\mfaces^\pm_F \subset \mfaces^\pm_{\text{ext}}$ mini\,faces that belong to the face~$F$.
-In general measures of mini\,faces of~$\mfaces^\pm_F$ corresponding to one material may be different, and, moreover, it may be the case that $\#\,\mfaces^+_F \ne \#\,\mfaces^-_F$ (see figure~\ref{fig:e_plus_e_minus}).
-That is, one may have different trace DOFs~\eqref{dual_mini:trace} from~$\mmesh^+$ and~$\mmesh^-$.
-	%%	Let us set~$\nu_{F_{\bcell^\pm}} \coloneqq \#\,\mfaces^\pm_F$
-	%	We set~$\nu_F \coloneqq \max\,\{ \#\,\mfaces^+_F,\,\#\,\mfaces^-_F \}$.
-	%	
-	%	\begin{figure}[h]
-	%		\centering
-	%		\caption{MMCs: $3 = \#\,\mfaces^+_F \ne \#\,\mfaces^-_F = 2$, $\nu_F = 3$}
-	%		\label{fig:e_plus_e_minus}
-	%		\svginputw[.7\linewidth]{e_plus_e_minus.pdf_tex}
-	%	\end{figure}
 
@@
 	\end{equation}
-	Here~$\{\,s_i\,\}_{i=0,\dots,n}$ is the set of $\LTwoSpace$-orthogonal polynomials on $F$ of degree~$n$.
+	Here~$\{\,s_i\,\}_{i=0,\dots,n}$ is the set of \hlcyan{$\LTwoSpace[F]$-orthogonal} polynomials on $F$ of degree~$n$.
 
-	For $F \in \bfaces[int]$ shared by two polygonal cells~$\bcell^\pm\in \bmesh$  denote by~$\mfaces_F(T^\pm) \subset \mfaces_{\text{ext}}(T^\pm)$ the subsets of mini-faces that belong to the macro-face~$F$ from each side.
 	Let $\nu_F \coloneqq \max\,\{ \#\,\mfaces_F(T^+),\,\#\,\mfaces_F(T^-) \}$.
@@
 	\end{equation}
-	where $s_{j\,i} $ is a signed distance between centroids of~$f$  and~$F$.
-For the corresponding vectors of unknowns  ${\vect \lambda}_\mmesh = \{ \lambda_{j\,i}(\mmesh) \}$ and ${\vect \lambda}_\bcell = \{ \lambda^{(0)}_{j}(\bcell) \} \cup \{ \lambda^{(1)}_{j}(\bcell) \}$ this defines
+	\hlcyan{where $s_{j\,i} \equiv s_f$ is a signed distance between centroids of~$f$  and~$F$, i.e.
+if $\vect a_F$, $\vect b_F$ and $\vect a_f$, $\vect b_f$ are vertices forming macro-face~$F$ and mini-face~$f$, respectively, then we have}
+	\begin{equation}\label{sdist}
+		s_f \coloneqq \left\| \frac{\vect a_f + \vect b_f}{2} - \vect a_F \right\|_2 - \left\| \frac{\vect a_F + \vect b_F}{2} - \vect a_F\right\|_2.
+	\end{equation}
+
+	For the corresponding vectors of unknowns  ${\vect \lambda}_\mmesh = \{ \lambda_{j\,i}(\mmesh) \}$ and ${\vect \lambda}_\bcell = \{ \lambda^{(0)}_{j}(\bcell) \} \cup \{ \lambda^{(1)}_{j}(\bcell) \}$~\eqref{asc1_interp} defines
 	the matrix $\vect R_\mmesh$ through~\eqref{asc_lambda}. For the example in Figure~\ref{fig:asc_dofs:asc1:mmc} (left and right) we have
@@
 			\sum_{f\in \mfaces_F(T^+)} u^{\text{ext}}_{\mmesh^+}(f)\,|f| &+ \sum_{f\in \mfaces_F(T^-)} u^{\text{ext}}_{\mmesh^-}(f)\,|f| &= 0, \\
-			\sum_{f\in \mfaces_F(T^+)} u^{\text{ext}}_{\mmesh^+}(f)\,\int_{f} s_1 \diff{l} &+ \sum_{f\in \mfaces_F(T^-)} u^{\text{ext}}_{\mmesh^-}(f)\,\int_{f} s_1 \diff{l} &= 0
+			\sum_{f\in \mfaces_F(T^+)} u^{\text{ext}}_{\mmesh^+}(f)\,\int_{f} s_1 \diff{l} &+ \sum_{f\in \mfaces_F(T^-)} u^{\text{ext}}_{\mmesh^-}(f)\,\int_{f} s_1 \diff{l} &= 0.
 		\end{split}\right.
@@
 	\end{equation}
-	or in the matrix form
+	\hlcyan{Integrating the first moments in the second equation of~{\eqref{eq:aux1pre}}, one gets}
+	\begin{equation*}
+		\sum_{f\in \mfaces_F(T^+)} u^{\text{ext}}_{\mmesh^+}(f)\,s_f\,|f| + 
+		\sum_{f\in \mfaces_F(T^-)} u^{\text{ext}}_{\mmesh^-}(f)\,s_f\,|f| = 0,
+	\end{equation*}
+	\hlcyan{where~$s_f$ is defined in~{\eqref{sdist}}.
+Noting that matrix~$\vect C_\mmesh$ from~{\eqref{local}} has mini-faces' measures on its diagonal, and interpolation matrix~$\vect R_\mmesh$ defined via~{\eqref{asc1_interp}} has signed distances and ones as its elements, one can rewrite~{\eqref{eq:aux1pre}} in the matrix form}
 	\begin{equation}\label{eq:aux1}

### 2019-06-06 num_sec.tex
Add index 'p' for pressure rate of conv
Fix l2 (semi-) norm descr
Add the answer to reviewers

@@
 Let $h$ be a maximum cell diameter for the macro-mesh~$\bmesh_h$, and $\mathbb V_h \subset \LTwoSpace$ be a space of piecewise constant
-functions on each cell~$\mcell \in \mmesh(\bcell)$, $\bcell \in \bmesh_h$. We define \textit{discrete} $\LTwo$-norm of $v \in \LTwoSpace$ as
+functions on each cell~$\mcell \in \mmesh(\bcell)$, $\bcell \in \bmesh_h$. For $v \in \LTwoSpace$ we define
 \begin{equation}\label{l2}
@@
 where $P_h\;:\;\LTwoSpace\rightarrow\mathbb V_h$ is $\LTwo$-projection operator.
+Note that~$\| \cdot \|_{\lTwoSpace}$ defines a norm in~$\mathbb V_h$; we will refer to it as \textit{discrete} $\LTwo$-norm.
 
@@
         $$
-        \varepsilon_h^{l_2} =  \left[\sum\limits_{\bface \in \bmesh_h}
+        \varepsilon_h^{l_2} =  \left[\sum\limits_{\bface \in \bfaces}
           A_\bface\left(
@@
 		\hline
-		\multirow{5}{*}{\rotatebox{90}{ASC(1)}} & $h$ & $\errlTwo{1}$ & $\rho$ & $\errInf{1}$
+		\multirow{5}{*}{\rotatebox{90}{ASC(1)}} & $h$ & $\errlTwo{1}$ & $\rho_p$ & $\errInf{1}$
                 & $\varepsilon^{l_2}_1$ & $\rho_u$ \\              %& $\varepsilon^\infty_1$\\
@@
 		\hline
-		\multirow{7}{*}{\rotatebox{90}{ASC(1)}} & $h$ & $\errlTwo{1}$ & ${\rho}$ & $\errInf{1}$
+		\multirow{7}{*}{\rotatebox{90}{ASC(1)}} & $h$ & $\errlTwo{1}$ & ${\rho_p}$ & $\errInf{1}$
                 & $\varepsilon^{l_2}_1$ & $\rho_u$ \\ %& $\varepsilon^\infty_1$ \\
@@
 The norms of the errors are shown in Table~\ref{tab:conv:pwquad2}. ASC(1) demonstrates convergence with the rate in the $\lTwo$-norm close to quadratic for scalar unknowns and
-even higher than linear for flux errors. It is important to take into accont that approximation errors in the interface reconstruction
+even higher than linear for flux errors. \hlcyan{It is important to take into account} that approximation errors in the interface reconstruction
 may  effect the convergence of discretization methods. For example, in these set of tests ASC(0) convergence rate fluctuates significantly for both scalar and flux errors.
@@
 
-%\clearpage
+From the figures it is easy to appreciate  that among all the methods only  ASC(1)  provides a reasonable approximation for the coarse mesh, cf. Figures~\ref{fig:transient:comp}.
+Numerical solution computed with ASC(0) overestimates incoming fluxes for the ring.
+This solution converges to the equilibrium state~$p_h \approx 1$ at approximately $t = 3.75$, which is significantly earlier than the time when the same state is achieved by the reference solution.
+Note that the coarse mesh contains faces with three materials, and we saw already that ASC(0) may fail to converge for this case even for stationary examples.
 
-\begin{figure}[h]
+We tried replacing Voronoi mesh with a triangulation such that the number of triangles is close to the number of the polygonal cells in the fine Voronoi mesh (456 elements for the triangular mesh v.s.
+465 for the Voronoi mesh); the achieved difference is that the triangular mesh has faces with three materials, and Voronoi mesh does not.
+Nevertheless, ASC(0) performed poorly for this example converging to the steady-state at approximately $t = 3$.
+
+Arithmetic homogenization performs poorly for both mesh levels (even finer mesh near the inclusions is required to provide reasonably accurate solution).
+Harmonic homogenization shows reasonable results only for the fine mesh.
+
+In Figure~\ref{fig:transient:err} we present the $\lTwo$-norm of the error $p_* - p_h$ computed for the inclusion~$\Omega_1 \cup \Omega_2$ as a function of time.
+Since all numerical solutions eventually converge to the same steady state, numerical errors for any method decrease for large enough time.
+On earlier stages ASC(1) outperforms all methods on the coarse mesh and provides comparable results with ASC(0) scheme and the harmonic homogenization approach on the fine mesh.
+
+\clearpage
+
+\begin{figure}
 	\centering
@@
 \end{figure}
-\begin{figure}[h]
+\begin{figure}
  	\centering
@@
 \end{figure}
+\clearpage
 
@@
 \end{figure}
-
-From the figures it is easy to appreciate  that among all the methods only  ASC(1)  provides a reasonable approximation for the coarse mesh, cf. Figures~\ref{fig:transient:comp}.
-Numerical solution computed with ASC(0) overestimates incoming fluxes for the ring.
-This solution converges to the equilibrium state~$p_h \approx 1$ at approximately $t = 3.75$, which is significantly earlier than the time when the same state is achieved by the reference solution.
-Note that the coarse mesh contains faces with three materials, and we saw already that ASC(0) may fail to converge for this case even for stationary examples.
-
-We tried replacing Voronoi mesh with a triangulation such that the number of triangles is close to the number of the polygonal cells in the fine Voronoi mesh (456 elements for the triangular mesh v.s.
-465 for the Voronoi mesh); the achieved difference is that the triangular mesh has faces with three materials, and Voronoi mesh does not.
-Nevertheless, ASC(0) performed poorly for this example converging to the steady-state at approximately $t = 3$.
-
-Arithmetic homogenization performs poorly for both mesh levels (even finer mesh near the inclusions is required to provide reasonably accurate solution).
-Harmonic homogenization shows reasonable results only for the fine mesh.
-
-In Figure~\ref{fig:transient:err} we present the $\lTwo$-norm of the error $p_* - p_h$ computed for the inclusion~$\Omega_1 \cup \Omega_2$ as a function of time.
-Since all numerical solutions eventually converge to the same steady state, numerical errors for any method decrease for large enough time.
-On earlier stages ASC(1) outperforms all methods on the coarse mesh and provides comparable results with ASC(0) scheme and the harmonic homogenization approach on the fine mesh.

### 2019-06-10 answer_to_reviewers.tex
Add Maxim's iteration

@@
 
-\centerline{
-{\Large {A. Zhiliakov, D. Svyatskiy, M.Olshanskii, E. Kikinzon, M. Shashkov}}}
+\begin{center}A list of changes  and responses to reviewers for ``A higher order approximate static condensation method for multi-material diffusion problems'' by A.
+Zhiliakov, D.
+Svyatskiy, M.
+Olshanskii, E.
+Kikinzon, M.
+Shashkov.
+\end{center}
+\bigskip
+
+%We are grateful to the reviewers for a careful read of the manuscript and constructive suggestions, which lead to an improved paper.
+%We addressed all points raised by the reviewers as outlined below.  \\
 
@@
 
-Reviewer 1 requested no modifications to the manuscript. Thus, in this documents we are  addressing the points raised by Reviewer 2.
+Reviewer 1 requested no modifications to the manuscript. Thus, in this document we are  addressing the points raised by Reviewer 2.
 
-\textbf{Answer to Reviewer 2}
+\textbf{Answers to Reviewer 2}
 
-The authors would like to thank the Reviewer for his comments and
-suggestions which we think improved the manuscript.
-Our revised article has been modified accordingly, with the changes \hlcyan{highlighted in blue}.
-%We have modified the manuscript accordingly. The changes in the manuscript are highlighted in red.
-%We hope that the manuscript is now acceptable for publication in SISC.
-
-%With this revision we also supply  supplementary material with the full animation of experiments 7.2 and 7.3.
-
-A summary of the modifications is presented below.  In the following
+The authors would like to thank the Reviewer for a careful read of the manuscript and his/her comments and
+constructive suggestions, which led to an improved paper. We addressed all points raised by the reviewers as outlined below.
+In the following
 we use italic font to quote the Reviewer.
+Our revised article has been modified accordingly, with the changes {highlighted in blue}.\\
 
@@
 
-We elaborated on this (page 7, paragraph 3) and added Figure 3 to illustrate d.o.f. mismatch.
+We elaborated on this (page 7, paragraph 3) and added Figure 3 to illustrate the d.o.f. mismatch.
 
@@
 
-After the previous correction, ``$\mathbf{R}_{\boldsymbol{\tau}}$ just below equation (17) shares two rows and so is singular if, e.g., $s_{21}=s_{22}$" reads as ``$\mathbf{R}_{\boldsymbol{\tau}}$ just below equation (18) shares two rows and so is singular if, e.g., $s_{21}=s_{22}$."
+%After the previous correction, ``$\mathbf{R}_{\boldsymbol{\tau}}$ just below equation (17) shares two rows and so is singular if, e.g., $s_{21}=s_{22}$" reads as ``$\mathbf{R}_{\boldsymbol{\tau}}$ just below equation (18) shares two rows and so is singular if, e.g., $s_{21}=s_{22}$."
 
-Matrix~$\mathbf{R}_{\boldsymbol{\tau}}$ is not singular for it is not square. We only prove that it has a trivial kernel, i.e. its columns are linearly independent. So no changes are needed here.
+Matrix~$\mathbf{R}_{\boldsymbol{\tau}}$ is not singular for it is not a square matrix if the corresponding cell has a multi-material face.
+We only prove that it has a trivial kernel, i.e.
+its columns are linearly independent, which is indeed the case if $s_{ki}\neq s_{kj}$ for some $i\neq j$.
+So no changes are needed here.
 
-\emph{``It is important to take into accont", page 15, accont => account"}
+\emph{(9) ``It is important to take into accont", page 15, accont $=>$ account"}
 
-\textbf{Other minor changes}
+Fixed.
 
-The changes are \hl{highlighted in yellow}.
-
-(1) Page 2, paragraph 2: ``standard discretization thechniques" changed to ``standard discretization techniques."
+%
+%\textbf{Other minor changes}
+%
+%The changes are \hl{highlighted in yellow}.
+%
+%(1) Page 2, paragraph 2: ``standard discretization thechniques" changed to ``standard discretization techniques."
 

### 2019-06-10 asc.tex
Add Maxim's iteration

@@
 	\and
-	Maxim Olshanskii\thanks{Department of Mathematics, University of Houston, Houston, Texas 77204 (molshan@math.uh.edu); Partially supported by NSF through grant  DMS-1717516.}
+	Maxim Olshanskii\thanks{Department of Mathematics, University of Houston, Houston, Texas 77204 and Sechenov University, Moscow  (molshan@math.uh.edu); Partially supported by NSF through grant  DMS-1717516.}
 	\and Evgeny Kikinzon \thanks{Los Alamos National Laboratory, Los Alamos,
@@
 
-	Past decades evidenced an explosive \hlcyan{growth in the development of efficient computational techniques} for problems with evolving interfaces, which involve interaction between many materials or different phases of matter.
+	Past decades evidenced an explosive {\color{blue}growth in the development of efficient computational techniques} for problems with evolving interfaces, which involve interaction between many materials or different phases of matter.
 These developments include immersed boundary method~\cite{peskin2002immersed}, immersed interface method~\cite{leveque1994immersed}, and unfitted finite element methods \cite{belytschko2009review,burman2015cutfem}, to name several popular numerical approaches.
@@
 In this approach, one assigns to the cells  artificial homogeneous  material properties, which are calculated based on the volumetric shares of different materials in each of the multi-material cells.
-This enables one to apply standard discretization \hl{techniques}.
+This enables one to apply standard discretization {techniques}.
 %if one needs to solve for other physics, such as the heat transfer, on every time step of the simulation.
@@
 	Denote by $\bfaces$ the collection of all faces of the macro-mesh $\bmesh$.
-\hlcyan{We shall distinguish between the subset of internal and external faces},  $\bfaces = \bfaces[int] \cup \bfaces[ext]$\footnote{For the sake of  notation, we shall use~$\bfaces$ to denote both the set of elements and the corresponding domain formed by their union~$\cup_{F\in \bfaces} \bar{F}$; same for $\bfaces[int]$, $\bfaces[ext]$ and other collections of mesh elements introduced later in the text.
+{\color{blue}We shall distinguish between the subset of internal and external faces},  $\bfaces = \bfaces[int] \cup \bfaces[ext]$\footnote{For the sake of  notation, we shall use~$\bfaces$ to denote both the set of elements and the corresponding domain formed by their union~$\cup_{F\in \bfaces} \bar{F}$; same for $\bfaces[int]$, $\bfaces[ext]$ and other collections of mesh elements introduced later in the text.
 The meaning should be clear from a context.}.
@@
 We denote by $\mfaces(T)$ the set of all faces in $\mmesh(T)$, which collects both   internal and boundary (external) faces with respect to $T$,  $\mfaces(T) = \mfaces[int](T) \cup \mfaces[ext](T)$.
-\hlcyan{If the meaning is not clear from the context, we will refer to elements of~$\mfaces(T)$ as ``mini-faces," and to elements of~$\bfaces$ as ``macro-faces."} Thus for the example of local mesh drafted in Figure~\ref{fig:mmesh}, we have three elements in $\mmesh(T)$, two internal faces from $\mfaces[int](T)$ and eleven external faces from $\mfaces[ext](T)$.
+{\color{blue}If the meaning is not obvious from the context, we will refer to elements of~$\mfaces(T)$ as ``mini-faces," and to elements of~$\bfaces$ as ``macro-faces."} Thus for the example of local mesh drafted in Figure~\ref{fig:mmesh}, we have three elements in $\mmesh(T)$, two internal faces from $\mfaces[int](T)$ and eleven external faces from $\mfaces[ext](T)$.
 It is clear that this local mesh is fitted to the material interfaces.
@@
 	\end{equation}
-	Here $\vect M_\mmesh$, $\vect\Sigma_\mmesh$, $\vect B^T_\mmesh$, $-\vect B_\mmesh$ are vector-mass, mass, gradient and divergence matrices, respectively; \hlcyan{$-\vect C_\mmesh$ is a diagonal scaling matrix that has mini-faces' measures~$|f|$ on the diagonal, $f \in \mfaces[ext](T)$, i.e.
-the mass matrix for ${\vect \lambda}_\mmesh$ unknowns};
+	Here $\vect M_\mmesh$, $\vect\Sigma_\mmesh$, $\vect B^T_\mmesh$, $-\vect B_\mmesh$ are vector-mass, mass, gradient and divergence matrices, respectively; {\color{blue}$-\vect C_\mmesh$ is a diagonal scaling matrix  with diagonal elements equal to the measures $|f|$ of mini-faces $f \in \mfaces[ext](T)$, i.e.
+$-\vect C_\mmesh$ is the mass matrix for ${\vect \lambda}_\mmesh$ unknowns};
 	$\vect E_\mmesh \in \mathbb{R}^{n_f \times n_\lambda}$ is a rectangular matrix with 0 and 1 entries which sparsifies a vector from  $\mathbb{R}^{n_{\lambda}}$
@@
 
-	Since the continuity of flux condition \eqref{flux_cond} and boundary conditions are enforced on  the \emph{external} edges of $T$, \hlcyan{we need to distinguish the vector} ${\vect u}^\text{ext}_\mmesh$ of fluxes on $\mfaces[ext](T)$, which is just a trivial restriction of ${\vect u}_\mmesh$ on the edges  from $\mfaces[ext](T)$,
+	Since the continuity of flux condition \eqref{flux_cond} and boundary conditions are enforced on  the \emph{external} edges of $T$, {\color{blue}we need to distinguish the vector} ${\vect u}^\text{ext}_\mmesh$ of fluxes on $\mfaces[ext](T)$, which is just a trivial restriction of ${\vect u}_\mmesh$ on the edges  from $\mfaces[ext](T)$,
 	\begin{equation}\label{system_mini}
@@
 However, we cannot do this in a straightforward way, since the discontinuity of material interfaces across the macro-mesh faces may lead to a mismatch of discrete fluxes from two sides of $F\in\bfaces[int]$.
-\hlcyan{We elaborate on this below.}
+{\color{blue}We elaborate on this below.}
 
-	\hlcyan{For $F \in \bfaces[int]$ shared by two polygonal cells~$\bcell^\pm\in \bmesh$ denote by~$\mfaces_F(T^\pm) \subset \mfaces_{\text{ext}}(T^\pm)$ the subsets of mini-faces that belong to the macro-face~$F$ from each side.
-In general, $\mfaces_F(T^+)$ and $\mfaces_F(T^-)$ can have different numbers of mini-faces that make up the macro-face~$F$, i.e.
-$\#\,\mfaces_F(T^+) \ne \#\,\mfaces_F(T^+)$, and hence the restrictions of concentration vectors~${\vect \lambda}_\mmesh$ and fluxes vectors~${\vect u}^\text{ext}_\mmesh$ can be of different sizes.
-Moreover, even if~$\#\,\mfaces_F(T^+) = \#\,\mfaces_F(T^+)$, locations of the mini-faces may be different due to volume- or moment-of-fluid interface reconstruction.
-See an example on Figure~{\ref{fig:mismatch}}.}
-
-	\begin{figure}[h]
-		\begin{subfigure}{.49\linewidth}
+	{\color{blue}For $F \in \bfaces[int]$ shared by two polygonal cells~$\bcell^\pm\in \bmesh$ denote by~$\mfaces_F(T^\pm) \subset \mfaces_{\text{ext}}(T^\pm)$ the subsets of mini-faces that belong to the macro-face~$F$ from each side.
+In general, $\mfaces_F(T^+)$ and $\mfaces_F(T^-)$ may have a different number of mini-faces that make up the macro-face~$F$, i.e.
+$\#\,\mfaces_F(T^+) \ne \#\,\mfaces_F(T^-)$, and hence the restrictions of concentration vectors~${\vect \lambda}_\mmesh$ and fluxes vectors~${\vect u}^\text{ext}_\mmesh$ can be of different sizes.
+Even if~$\#\,\mfaces_F(T^+) = \#\,\mfaces_F(T^-)$, the locations of the mini-faces may be different due to volume- or moment-of-fluid interface reconstruction.}
+	\begin{wrapfigure}{l}{0.5\linewidth}
+		\begin{subfigure}{1\linewidth}
 			\svginputw{e_plus_e_minus.pdf_tex}
 		\end{subfigure}%
-		\quad
-		\begin{subfigure}{.49\linewidth}
-			\hlcyan{We have $3 = \#\,\mfaces_F(T^+) \ne \#\,\mfaces_F(T^+) = 2$. Note also that locations of mini-faces corresponding to the same material are different from each side of~$F$}
-		\end{subfigure}
-		\caption{\hlcyan{Example of the mismatch of discrete fluxes from two sides of $F\in\bfaces[int]$}}
+%		\quad
+%		\begin{subfigure}{.49\linewidth}
+%			
+%		\end{subfigure}
+		\caption{{\color{blue}Example of the mismatch of discrete fluxes from two sides of $F\in\bfaces[int]$}}
 		\label{fig:mismatch}
-	\end{figure}
-
-	\hlcyan{This makes matching concentration and fluxes values not trivial.} Therefore, we shall enforce the flux continuity condition in the spirit of the mortar finite element method~\cite{mortar} using the space of functions defined on $\bfaces[int]$, which are polynomials of degree at most $n$ on every $F\in\bfaces[int]$, an analog of the Lagrange multiplier space in the mortar method:
+	\end{wrapfigure}
+{\color{blue}See an example in Figure~\ref{fig:mismatch}.
+We have $3 = \#\,\mfaces_F(T^+) \ne \#\,\mfaces_F(T^-) = 2$.
+Note also that locations of mini-faces corresponding to the same material are different from each side of~$F$}.
+	{\color{blue}This makes matching concentration and fluxes values not straightforward.} Therefore, we shall enforce the flux continuity condition in the spirit of the mortar finite element method~\cite{mortar} using the space of functions defined on $\bfaces[int]$, which are polynomials of degree at most $n$ on every $F\in\bfaces[int]$, an analog of the Lagrange multiplier space in the mortar method:
 	\[
@@
 	\end{equation}
-	Here~$\{\,s_i\,\}_{i=0,\dots,n}$ is the set of \hlcyan{$\LTwoSpace[F]$-orthogonal} polynomials on $F$ of degree~$n$.
+	Here~$\{\,s_i\,\}_{i=0,\dots,n}$ is the set of {\color{blue}$\LTwoSpace[F]$-orthogonal} polynomials on $F$ of degree~$n$.
 
@@
 	\end{equation}
-	\hlcyan{where $s_{j\,i} \equiv s_f$ is a signed distance between centroids of~$f$  and~$F$, i.e.
+	{\color{blue}where $s_{j\,i} \equiv s_f$ is a signed distance between centroids of~$f$  and~$F$, i.e.
 if $\vect a_F$, $\vect b_F$ and $\vect a_f$, $\vect b_f$ are vertices forming macro-face~$F$ and mini-face~$f$, respectively, then we have}
@@
 
-	For the corresponding vectors of unknowns  ${\vect \lambda}_\mmesh = \{ \lambda_{j\,i}(\mmesh) \}$ and ${\vect \lambda}_\bcell = \{ \lambda^{(0)}_{j}(\bcell) \} \cup \{ \lambda^{(1)}_{j}(\bcell) \}$~\eqref{asc1_interp} defines
+	For the corresponding vectors of unknowns  ${\vect \lambda}_\mmesh = \{ \lambda_{j\,i}(\mmesh) \}$ and ${\vect \lambda}_\bcell = \{ \lambda^{(0)}_{j}(\bcell) \} \cup \{ \lambda^{(1)}_{j}(\bcell) \}$ equation \eqref{asc1_interp} defines
 	the matrix $\vect R_\mmesh$ through~\eqref{asc_lambda}. For the example in Figure~\ref{fig:asc_dofs:asc1:mmc} (left and right) we have
@@
 	\end{equation}
-	\hlcyan{Integrating the first moments in the second equation of~{\eqref{eq:aux1pre}}, one gets}
+	{\color{blue}Integrating the first moments in the second equation of~{\eqref{eq:aux1pre}}, one gets}
 	\begin{equation*}
@@
 	\end{equation*}
-	\hlcyan{where~$s_f$ is defined in~{\eqref{sdist}}.
+	{\color{blue}where~$s_f$ is defined in~{\eqref{sdist}}.
 Noting that matrix~$\vect C_\mmesh$ from~{\eqref{local}} has mini-faces' measures on its diagonal, and interpolation matrix~$\vect R_\mmesh$ defined via~{\eqref{asc1_interp}} has signed distances and ones as its elements, one can rewrite~{\eqref{eq:aux1pre}} in the matrix form}

### 2019-07-30 3d/asc3d.tex
Add ASC 3D draft description

\input{style.tex}

\title{Extension of the approximate static condensation method for multi-material diffusion problems to 3D}
\author{
	Alexander Zhiliakov\thanks{Department of Mathematics, University of Houston, Houston, Texas 77204 (alex@math.uh.edu).}
}

\begin{document}

\maketitle

\tableofcontents
\vfill
\clearpage
\let\oldtabular\tabular
\renewcommand{\tabular}[1][1.5]{\def\arraystretch{#1}\oldtabular}

\section{Introduction}

In this technical report we present the extension of the approximate static condensation method (ASC) from 2D to 3D. The ASC method was first introduced in~\cite{kikinzon2017approximate}, and then was further studied in~\cite{ZHILIAKOV2019333}.

\AZ{TBA: What was done in~\cite{kikinzon2017approximate} and~\cite{ZHILIAKOV2019333}; outline of the report.}

In a polyhedral bounded domain $\Omega \subset \Rn{3}$ we consider the diffusion problem in the mixed form
\begin{equation}\label{dual}
	\arraycolsep=2pt\def\arraystretch{1.5}
	\left\{\begin{array}{rcrccl}
	\vect K^{-1}\,\vect u & + & \nabla\,p & = & 0 &\quad\text{in } \Omega , \\
	\nabla\cdot\vect u    & + & c\,p      & = & f &\quad\text{in } \Omega
	\end{array}\right.
\end{equation}
with boundary data
\begin{equation}
	p = g_D \text{ on } \partial\Omega_D,\quad
	\vect u \cdot \hat{\vect n} = g_N \text{ on } \partial\Omega_N. \label{dual:bc}
\end{equation}

\subsection{Notations and problem description}

\AZ{TBA: basic notations and quick problem setting.}
\begin{eqnarray}
	\arraycolsep=2pt\def\arraystretch{1.5}
	\left\{\begin{array}{rcrccl}
	\vect K^{-1}\,\vect u                   & + & \nabla\,p & = & 0       &\quad\text{in } \bcell, \\
	\nabla\cdot\vect u                      & + & c\,p      & = & f       &\quad\text{in } \bcell, \\
											&   & p         & = & \lambda &\quad\text{on } \partial\bcell, %\label{dual_mini:trace}
	\end{array}\right.
	& \qquad \forall~\bcell\in\bmesh, \label{dual_mini} \\
		\llbracket\vect u \cdot \hat{\vect n}\rrbracket = 0\quad\:\:\text{on } F,\:\:\:\:
	& \qquad\quad \forall~F\in\bfaces[int]. \label{flux_cond}
\end{eqnarray}
\begin{equation}\label{local}
	\begin{pmatrix}
		\phantom{-}\vect M_\mmesh & \vect B^T_\mmesh \\
		-\vect B_\mmesh & \vect \Sigma_\mmesh
	\end{pmatrix}
	\begin{pmatrix} {\vect u}_\mmesh \\ {\vect p}_\mmesh \end{pmatrix}
	=
	\begin{pmatrix} \vect E_\mmesh\,\vect C_\mmesh\,{\vect \lambda}_\mmesh \\ {\vect f}_\mmesh \end{pmatrix}.
\end{equation}

\subsection{Higher order method}

\AZ{I would much appreciate if somebody adds the description. Daniil, could you do this? :)}

\section{Implementation details}

ASC algorithm may be seen as a high-level approach: Once disctretizations~\eqref{local} of local systems~\eqref{dual_mini} are available, one can perform the approximate static condensation procedure, assemble and solve the global linear system for concentrations etc. If one works with simple mesh cells, e.g. hexahedrons or tetrahedrons, then the usual finite element, finite volume, or finite difference approaches may be used for the discretization of local matrices in~\eqref{local}.

However, we would like to be more flexible w.r.t. cells' geometry, and thus we stick to mimetic finite difference method~\cite{MFDbook}. As we did for 2D case, we use Amanzi multi-process HPC simulator software~\cite{amanzi} for this purpose.

\subsection{Mesh requirements}

We would like to allow for general polyhedral cells for both macro- and mini-meshes. Faces may not be necessarily flat. In order to generate a macro-mesh~$\mmesh$, we use ShaPo software package~\cite{shapo2d, shapo3d} developed in Los Alamos National Laboratory. Meshes are exported to the binary Exodus~II format~\cite{exo}, and then efficiently imported to Amanzi. Examples of meshes generated with ShaPo are demonstrated in Figure~\ref{fig:shapo}.

\begin{figure}[H]
	\centering
	\begin{subfigure}{.1\linewidth}\end{subfigure}%
	\begin{subfigure}{.4\linewidth}
		\centering
		\includegraphicsw[.8]{{shapo1.cropped}.png}
	\end{subfigure}%
	\begin{subfigure}{.4\linewidth}
		\centering
		\includegraphicsw[.8]{{shapo2.cropped}.png}
	\end{subfigure}%
	\begin{subfigure}{.1\linewidth}\end{subfigure}%
	\caption{Meshes generated with Shapo. Left: prismatic Voronoi mesh generated from 2D mesh. Right: pure Voronoi mesh}
	\label{fig:shapo}		
\end{figure}

As in 2D case, we assemble the global matrix via iterating over macro-cells~$\bcell \in \bmesh$ of the macro-mesh~$\bmesh$. Thus we need the following interface for the mesh~$\bmesh$.

\textit{Local matrix assembly:}
\begin{enumerate}
	\item Given the index of the macro-cell~$\bcell$, one needs to iterate over mini-cells~$\mcell \in \mmesh(\bcell) \equiv \mmesh$ of its mini-mesh;
	\item Given the mini-mesh~$\mmesh$, one needs to be able to get the indices of its mini-faces~$\mfaces(\bcell)$;
	\item One also needs to be able to differ internal and boundary mini-faces: $\mface \in \mfaces[int](\bcell)$ or $\mface \in \mfaces[ext](\bcell)$;
	\item Given the index of the boundary mini-face~$\mface \in \mfaces[ext](\bcell)$, one needs to be able to get the global index of the macro-face~$\bface \in \bfaces$ that the mini-face belongs to, $\mface \subset \bface$;  
	\item The crucial aspect is assembly of the mass matrix~$\vect M_{\mmesh} = \sum_{\mcell \in \mmesh} \vect N^T_{\mcell}\,\vect M_{\mcell}\,\vect N_{\mcell}$ stemmed from MFD. $\vect M_{\mmesh}$ is global w.r.t. the mini-mesh~$\mmesh$, and local w.r.t. the macro-mesh~$\bmesh$. It is associated with flux d.o.f., so one needs the following mappings:
	\begin{itemize}
		\item Index of $\mcell \in \mmesh \mapsto$ indices of mini-faces~$\mface \in \mfaces$ that form mini-cell~$\mcell$. This is needed for mapping of local (associated with faces of~$\mcell$) flux d.o.f. to global (associated with faces of~$\mmesh$), i.e. implicitly representing the assembly matrix~$\vect N_\mcell$,
		\item Index of~$\mcell \in \mmesh \mapsto$ vector of areas of mini-faces~$\mface \in \mfaces$ that form mini-cell~$\mcell$,
		\item Index of~$\mcell \in \mmesh \mapsto$ its centroid,
		\item Index of~$\mcell \in \mmesh \mapsto$ its volume;
	\end{itemize} 
	\item Index of mini-face~$f \in \mfaces$ of~$\mmesh \mapsto$ local index of the macro-face~$\bface \in \bfaces$ in~$\bcell$ that~$f$ belongs to. This is needed for the interpolation matrix~$\vect R_{\mmesh}$.
\end{enumerate}

The bullets~(3) and~(4) above are the most challenging one: Typically VOF or MOF interface reconstruction software does not provide one with such topology information. The \textit{extended} MOF (XMOF) software package~\cite{kikinzon2018xmof} that we used in~\cite{kikinzon2017approximate, ZHILIAKOV2019333} is capable of recovering full macro- and mini-mesh connectivity, however, the implementation only exists for 2D case as for now.

\textit{Global matrix assembly:}
\begin{enumerate}
	\item The global system for coarse (moment) concentrations~$\vect \lambda_{\bmesh}$, $\vect S_{\bmesh}\,\vect \lambda_{\bmesh} = \vect b_{\bmesh}$, is assembled cell-wised: $\vect S_{\bmesh} = \sum_{\bcell \in \bmesh} \vect N_\bcell^T\,\vect S_\bcell\,\vect N_\bcell$.
	\item Thus one needs the following routine: index of~$\bcell \in \bmesh \mapsto$ global indices of macro-faces~$\bface \in \bfaces$ that form macro-cell~$\bcell$. This is needed for mapping local (associated with faces of~$T$) concentration d.o.f. to global (associated with faces of~$\bmesh$) ones, i.e. implicitly representing the assembly matrix~$\vect N_T$;
	\item The condensation process\,---\,i.e. computation of~$\vect S_\bcell$\,---\,is essentially the same as for 2D, so we refer to~\cite[p.~7]{ZHILIAKOV2019333}.
\end{enumerate}

\subsection{Interface reconstruction}

In order to perform MOF interface reconstruction, we use Tangram software framework~\cite{tangram}. We refer to Figure~\ref{fig:tangram} for an example. Note that ASC method allows for discontinuous material\,/\,phases configuration.

\begin{figure}[H]
	\centering
	\begin{subfigure}{.1\linewidth}\end{subfigure}%
	\begin{subfigure}{.4\linewidth}
		\centering
		\includegraphicsw[.8]{{mof_tjunction.cropped}.png}
	\end{subfigure}%
	\begin{subfigure}{.4\linewidth}
		\centering
		\includegraphicsw[.8]{{mof_tjunction_noise.cropped}.png}
	\end{subfigure}%
	\begin{subfigure}{.1\linewidth}\end{subfigure}%
	\caption{MOF interface reconstruction with Tangram. Left: T-junction materials\,/\,phases configuration (different colors correspond to different materials\,/\,phases). Right: the same as in Left picture, but with some ``noise'' added to simulate discontinuous interfaces}
	\label{fig:tangram}		
\end{figure}

\begin{remark}
As we mentioned above, recovering macro- and mini-mesh connectivity has to be implemented separately, for currently it is not a part of Tangram software. This by itself is a non-trivial problem of computational geometry if one works in floating point arithmetic, and making it robust may be challenging. This goes beyond of what we present in the current report.
\end{remark}

Since Tangram is not a part of Amanzi, we have to link it to Amanzi and provide a mesh wrapper so that Tangram is able to work with the Amanzi mesh data structure. One can find building \& running instructions here: \url{https://github.com/56th/amanzi/blob/56th/ASC/src/operators/README.md}.

\section{Numerical experiments}

\subsection{Mixed--hybrid mimetic finite difference method}

We first test our implementation on the problem where \textit{no} multi-material cells are present. Note that in this case the interpolation matrix boils down to identity,
\begin{equation}
	\vect R_{\mmesh} = \vect I, \quad \forall \mmesh = \mmesh(\bcell \in \bmesh).
\end{equation}
In this case the ASC($n$) method is equivalent to the ordinary mixed-hybrid mimetic finite difference\footnotemark{} approach.

We choose~$\vect K = \vect I$, $c = 2$, $f = 0$, and $\partial\Omega = \partial\Omega_D$ in~\eqref{dual} and~\eqref{dual:bc}. The exact solution is set as
\begin{equation}\label{exact1}
	p(\vect x) = (1,\,2,\,3)\,\vect x + 4.
\end{equation}

\begin{figure}[H]
	\centering
	\begin{subfigure}{.33\linewidth}
		\centering
		\includegraphicsw{{exact1_brick.cropped}.png}
	\end{subfigure}%
	\begin{subfigure}{.33\linewidth}
		\centering
		\includegraphicsw{{exact1_poly.cropped}.png}
	\end{subfigure}%
	\begin{subfigure}{.33\linewidth}
		\centering
		\includegraphicsw{{exact1_tetra.cropped}.png}
	\end{subfigure}%	
	\caption{Computed solutions $p_h$. Left: Brick mesh for~$\Omega = (-1,\,1)^3$, $\|p - p_h\|_{\lTwoSpace} = 2.03\times 10^{-14}$. Middle: Polyhedral prismatic mesh for~$\Omega = (0,\,1)^3$, $\|p - p_h\|_{\lTwoSpace} = 2.24\times 10^{-15}$. Right: Tetrahedral mesh for~$\Omega = (-3000,\,3000)^2\times(-4000,\,0)$, $\|p - p_h\|_{\lTwoSpace} = 2.47\times 10^{-7}$}
	\label{fig:exact1}		
\end{figure}

Computed solutions~$p_h$ for three different domains and cell choices are shown in Figure~\ref{fig:exact1}. Note that the exact solution~$p$ in~\eqref{exact1} is an affine function, and the method recovers it exactly (up to the machine precision) w.r.t. mean values over the cells~$\bcell \in \bmesh$.

\footnotetext{Or to whatever method that was used to discretize local problems~\eqref{dual_mini}.}

\subsection{Interface without multi-material faces}

\AZ{TBA\dots}

\subsection{Interface with multi-material faces}

\AZ{TBA\dots}

\section*{Acknowledgments}

\AZ{Mikhail, please correct the details.}
Funded by the Department of Energy at Los Alamos National Laboratory
under contracts DE-AC52-06NA25396 and the DOE Office of Science
Advanced Computing Research (ASCR) program in Applied Mathematical
Sciences. Alexander Zhiliakov acknowledges the internship opportunity in the Los Alamos National Laboratory.

\bibliographystyle{plain}
\bibliography{bibl}

\end{document}

### 2019-08-07 3d/asc3d.tex
Add more comments

@@
 
-\subsection{Interface without multi-material faces}
+\subsection{Constant concentration on multi-material faces}
 
-\AZ{TBA\dots}
+\AZ{TBA: $p = 1$ (voronoi sandwich mesh) and $p = 2\,z + 1$ (square)}
 
-\subsection{Interface with multi-material faces}
+\subsection{General example: planar sandwich}
 
-\AZ{TBA\dots}
+\AZ{TBA: high-contrast $k$, sequence of voronoi and brick meshes (skewed parallel interfaces), compare with homo, plot fluxes}
 
@@
 
+\AZ{Add building / running instructions as an appendix}
+
 \bibliographystyle{plain}

### 2019-08-08 3d/asc3d.tex
High order algorithm

@@
 \end{eqnarray}
+
+In the weak form this problem is formulated as follows:
+find $\vect u \in \bigotimes\limits_{\bcell\in\bmesh}\HDivSpace[\bcell]$ s.t.
+$\vect u \cdot \hat{\vect n} = g_N$ on $\partial\Omega_N$, $ p\in\LTwoSpace$, $\lambda\in\HHalfSpace[{\bfaces[int]}]$ such that
+	\begin{equation}\label{weak_form}
+		\begin{split}
+			\int_{\Omega} \vect K^{-1}\,\vect u\cdot\vect v \diff \vect x - \sum_{\bcell\in\bmesh}\int_\bcell p\,\nabla\cdot\vect v \diff \vect x + \sum_{\bface\in\bfaces[int]}\int_{\bface} \lambda\,\llbracket\vect v\cdot\hat{\vect n}\rrbracket \diff l &= -\int_{\partial\Omega_D} g_D\,\vect v\cdot\hat{\vect n} \diff l, \\
+			\sum_{\bcell\in\bmesh}\int_\bcell \nabla\cdot\vect u\,q \diff \vect x + \int_\Omega c\,p\,q \diff \vect x &= \int_\Omega f\,q \diff \vect x, \\
+			\sum_{\bface\in\bfaces[int]}\int_{\bface} \llbracket\vect u\cdot\hat{\vect n}\rrbracket\,\mu \diff l &= 0
+		\end{split}
+	\end{equation}
+	for all $\vect v \in \bigotimes\limits_{\bcell\in\bmesh}\HDivSpace[\bcell]$ s.t.
+$\vect v \cdot \hat{\vect n} = 0$ on $\partial\Omega_N$, $q \in \LTwoSpace[\Omega]$, and $\mu \in \HHalfSpace[{\bfaces[int]}]$.
+
+        We shall discretize problem \eqref{weak_form} on a particular cell $T$ in terms of average fluxes assigned to each face from $\mfaces(T)$,
+        we denote the corresponding vector by ${\vect u}_\mmesh\in\mathbb{R}^{n_f}$, $n_f=\#\mfaces(T)$,  and concentration values assigned to each cell ${\tau \in \mmesh(T)}$, we denote the corresponding vector by ${\vect p}_\mmesh\in\mathbb{R}^{n_p}$, $n_p=\#\mmesh(T)$.
+The given data is the source term vector ${\vect f}_\mmesh\in \mathbb{R}^{n_p}$ and the concentration values $\lambda$ on the boundary of $T$.
+	To approximate this boundary data \emph{for the local problem}, we introduce the vector
+	${\vect \lambda}_\mmesh\in\mathbb{R}^{n_\lambda}$, $n_\lambda=\#\mfaces[ext](T)$,
+	where we assign one averaged concentration value for each $f\in\mfaces[ext](T)$, so that ${\vect \lambda}_\mmesh$ can be seen as a piecewise-constant approximation of $\lambda$ with respect to the subdivision of $\partial T$ into the faces of the local mesh $\mmesh$.
+
+%Before we go into details of the method, we note that $\lambda$ can also  be observed as the Lagrange multiplier corresponding to the normal flux condition~\eqref{flux_cond}.
+%The problem \eqref{dual_mini}--\eqref{flux_cond} can be formulated in the weak form:
+
 \begin{equation}\label{local}
@@
 
+\subsection{Lowest order method}
+
 \subsection{Higher order method}
 
-\AZ{I would much appreciate if somebody adds the description. Daniil, could you do this? :)}
+%\AZ{I would much appreciate if somebody adds the description. Daniil, could you do this? :)}
+Let $\vect s_{ji}$ are the vectors which connects the centoroid of macroface $F_j$ and
+mini-faces $f_i$.
+The matrix $S_j=\{ \vect s_{j1}, \vect s_{j2} \dots \vect s_{jn}\}$ for macroface $F_j$
+is formed using $\vect s_{ji}$ as columns, $S_j \in {\mathbb R}^{3\times n}$. Since we assume
+that all macrofaces are planar then $rank(S_j) \le 2$. For better readability of the formulas we droppped the subscript $j$ bellow.
+Let consider $QR$ decomposition of matrix $S$. Since it is possible that $S$ has incomplete rank then:
+
+$$ S P = QR=(\vect q_1, \vect q_2, \vect q_3)
+\left(
+\begin{array}{cc}
+R_{11} & R_{12}\\
+0 & 0
+\end{array}
+\right),$$
+
+\noindent where $P$ is a permutation matrix, $Q \in \mathbb R^{3\times 3}$ is orthogonal matrix,
+$R_{11}\in \mathbb R^{2\times 2}$ is uppper triangular matrix and $R_{12} \in \mathbb R^{2\times(n-2)}$.
+For the sake of simplicity we assume that $P$ is identity matrix. This can be achieved by
+the corresponding ordering of mini-faces $f_i$. Now we impose the continuity condition for the inteface fluxes we need to introduce the discrete space on macrofaces and establish
+the relationship between degrees of freedom on mini and macrofaces. The degrees of freedom for $\lambda$ on minifaces are defined as :
+
+$$\lambda(f_i) = \frac{1}{|f_i|}\int_{f_i} \lambda dx$$
+
+If we introduce the average concentration on a macroface as one macroface degrees of freedom:
+
+$$\lambda^{(0)}(F) = \frac{1}{|F|}\int_{F} \lambda dx$$
+
+then $\lambda(f_i)$ can be expressed in terms of $\lambda(F)$ as follows:
+
+$$\lambda(f_i) = \lambda^{(0)}(F) + \nabla^T \lambda \cdot \vect s_i$$
+or
+$$\lambda_f^T =  \lambda^{(0)}(F) \vect e^T + \nabla^T \lambda S =
+\lambda^{(0)}(F) \vect e^T + \nabla^T \lambda (\vect q_1, \vect q_2, \vect q_3)
+\left(
+\begin{array}{cc}
+R_{11} & R_{12}\\
+0 & 0
+\end{array}
+\right) = $$
+$$\lambda^{(0)}(F) \vect e^T  + (\nabla^T \lambda  \cdot  \vect q_1, \nabla^T \lambda  \cdot  \vect q_2) \left(
+\begin{array}{cc}
+R_{11} & R_{12}
+\end{array}
+\right) = \lambda^{(0)}(F) \vect e^T + (\lambda^{(1)}(F),\lambda^{(2)}(F)) \left(
+\begin{array}{cc}
+R_{11} & R_{12}
+\end{array}
+\right).$$
+
+Here, the additional degrees of freedom $\lambda^{(k)}(F) = \nabla^T \lambda  \cdot  \vect q_k, k=1,2$
+are introduced and $\vect e$ is the vector of ones.
+
+To close the global linear system we neeed to impose the interface conditions for the fluxes $\vect u^{\text{ext}}_\mmesh$.
+
+\begin{equation}\label{flux_cont1}
+\int_F \vect u|_{\bcell^+}\cdot\hat{\vect n}\, \diff s =
+\int_F \vect u|_{\bcell^-}\cdot\hat{\vect n}\, \diff s, \text{for each } F \in \bfaces[int],
+\end{equation}
+
+\begin{equation}\label{flux_cont2}
+\int_F \vect u|_{\bcell^+}\cdot\hat{\vect n}\,({\vect r} \cdot \vect q_k^{\bcell^+}) \diff s =
+\int_F \vect u|_{\bcell^-}\cdot\hat{\vect n}\,({\vect r} \cdot \vect q_k^{\bcell^-}) \diff s,
+\quad k=1,2,  \quad \text{for each } F \in \bfaces[int],
+\end{equation}
+
+where ${\vect r}^T = (x-x_F, y-y_F, z-z_F).$
 

### 2019-08-08 3d/asc3d.tex
Update on high order dof

@@
 are introduced and $\vect e$ is the vector of ones.
+
+{\it Another interpretation of degrees of freedom could be somewhat similar to 2D version.The Lagrange multiplier space in can be defined as}:
+
+$$\Lambda=\left\{\lambda\in \LTwoSpace[{\bfaces[int]}]\,:\, \lambda\in {\widetilde P}_n~\text{for any}~F\in\bfaces[int]\right\}.
+$$
+\noindent {\it where ${\widetilde P}_n~$ is the polynomial space defined in a
+local coordinate system $\{\vect q_1, \vect q_2\}$.
+It is convenient to define degrees of freedom for $\lambda\in\Lambda$ in terms
+of its~$(n+1)$ moments $\lambda^{(i)}_F$ on every internal face $F\in\bfaces[int]$:
+
+\begin{equation}\label{asc_dofs}
+\lambda^{(i)}_F=\frac{\int_F  \lambda\,\phi_i \diff s}{|F|}, \quad i = 0, \dots, n.	\end{equation}
+Here~$\{\,\phi_i\,\}_{i=0,\dots,n}$ is the set of {\color{blue}$\LTwoSpace[F]$-orthogonal} polynomials on $F$ of degree~$n$ in a local coordinate system .
+}
 

### 2019-08-12 3d/asc3d.tex
Add constant concentration on multi-material faces example

@@
 
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{.33\linewidth}
+		\centering
+		\includegraphicsw[.9]{{skewed_exact_k.cropped}.png}
+	\end{subfigure}%
+	\begin{subfigure}{.33\linewidth}
+		\centering
+		\includegraphicsw[.9]{{skewed_k.cropped}.png}
+	\end{subfigure}%
+	\begin{subfigure}{.33\linewidth}
+		\centering
+		\includegraphicsw[.9]{{skewed_vor_k.cropped}.png}
+	\end{subfigure}%
+	\vskip .3cm
+	\begin{subfigure}{.33\linewidth}
+		\centering
+		\includegraphicsw[.9]{{skewed_exact.cropped}.png}
+	\end{subfigure}%
+	\begin{subfigure}{.33\linewidth}
+		\centering
+		\includegraphicsw[.9]{{skewed.cropped}.png}
+	\end{subfigure}%
+	\begin{subfigure}{.33\linewidth}
+		\centering
+		\includegraphicsw[.9]{{skewed_vor.cropped}.png}
+	\end{subfigure}%	
+	\caption{Computed solutions $p_h$.
+Left: Multi-material faces lie only in $xy$-plane, $\|p - p_h\|_{\lTwoSpace} = 1.08\times 10^{-14}$.
+Middle and right: Slightly perturbed interface so we have that $p$ is not constant on all multi-material faces, $\|p - p_h\|_{\lTwoSpace} = 3.10\times 10^{-10}$ (Middle) and $\|p - p_h\|_{\lTwoSpace} = 3.17\times 10^{-3}$ (Right)}
+	\label{fig:skewed}		
+\end{figure}
+
 \subsection{General example: planar sandwich}
@@
 \AZ{TBA: high-contrast $k$, sequence of voronoi and brick meshes (skewed parallel interfaces), compare with homo, plot fluxes}
+
+Pic: $p_h$ + fluxes and error for cyl
 

### 2019-10-26 3d/asc3d.tex
Add cyl example images
Add conv table for cylinder
Add spherical inclusion example

@@
 
-\subsection{General example: planar sandwich}
+\subsection{Planar sandwich}
 
-\AZ{TBA: high-contrast $k$, sequence of voronoi and brick meshes (skewed parallel interfaces), compare with homo, plot fluxes}
+We choose~$\vect K = k\,\vect I$ with $k = 10^4$ in the middle part of the domain, and $k = 1$ in the left and right parts; $c = 2$, $f = 0$, and $\partial\Omega = \partial\Omega_D$ in~\eqref{dual} and~\eqref{dual:bc}.
+The exact solution is continuous piecewise linear s.t.
+its normal flux is also continuous.
 
-Pic: $p_h$ + fluxes and error for cyl
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[t]{.5\linewidth}
+		\centering
+		\includegraphicsw[.9]{{cyl_sol.cropped}.png}
+	\end{subfigure}%
+	\begin{subfigure}[t]{.5\linewidth}
+		\centering
+		\includegraphicsw[.9]{{cyl_err.cropped}.png}
+	\end{subfigure}%
+	\caption{Left: Computed solution $p_h$ and the flux. Right: error $(p - p_h)$. Here~$\|p - p_h\|_{\lTwoSpace} = 1.77\times 10^{-4}$}
+	\label{fig:cyl}		
+\end{figure}
+
+\begin{table}[H]
+	\centering\footnotesize
+	\caption{Convergence results for the cylinder example. $\bar q$ denotes the mean value of a function~$q$} 
+	\label{tab:cyl}
+	\begin{subtable}{1.\linewidth}
+		\centering
+		\begin{tabular}[1.2]{|c||c|c||c||c|}
+			\hline
+			$h$ & $\| p - p_h \|_{\lTwoSpace}$ & Order & $| \bar p - \bar p_h |$ & $\| p - p_h \|_{\infty}$ \\ 
+			\hline
+			\input{cyl_table.tex}
+		\end{tabular}
+	\end{subtable}%
+\end{table}
+
+\AZ{TBA: compare with homo. methods}
+
+\subsection{Spherical inclusion}
+
+We choose~$\vect K = k\,\vect I$ with $k = 1$ inside the sphere and $k = 100$ outside; $c = 1$ and $\partial\Omega = \partial\Omega_D$ in~\eqref{dual} and~\eqref{dual:bc}.
+The exact solution is set to be continuous piecewise quadratic s.t.
+its normal flux is also continuous across the interface.
+Load data~$f$ is computed from the exact solution.
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{.33\linewidth}
+		\centering
+		\includegraphicsw[.9]{{incl100.cropped}.png}
+	\end{subfigure}%
+	\begin{subfigure}{.33\linewidth}
+		\centering
+		\includegraphicsw[.9]{{incl1000.cropped}.png}
+	\end{subfigure}%
+	\begin{subfigure}{.33\linewidth}
+		\centering
+		\includegraphicsw[.9]{{incl10000.cropped}.png}
+	\end{subfigure}%
+	\vskip .3cm
+	\begin{subfigure}{.33\linewidth}
+		\centering
+		\includegraphicsw[.9]{{incl100_k.cropped}.png}
+	\end{subfigure}%
+	\begin{subfigure}{.33\linewidth}
+		\centering
+		\includegraphicsw[.9]{{incl1000_k.cropped}.png}
+	\end{subfigure}%
+	\begin{subfigure}{.33\linewidth}
+		\centering
+		\includegraphicsw[.9]{{incl10000_k.cropped}.png}
+	\end{subfigure}
+	\caption{Spherical material inclusion for $h \in \{ 6.44\times 10^{-1}, 2.97\times 10^{-1}, 1.53\times 10^{-1}\}$ resulting from Tangram moment-of-fluid interface reconstruction.
+Note that the interface is discontinuous}
+	\label{fig:incl}		
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{.5\linewidth}
+		\centering
+		\includegraphicsw[.9]{{sph_p_1000.cropped}.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\linewidth}
+		\centering
+		\includegraphicsw[.9]{{sph_e_1000.cropped}.png}
+	\end{subfigure}%
+	\vskip .3cm
+	\begin{subfigure}{.5\linewidth}
+		\centering
+		\includegraphicsw[.9]{{sph_p_10000.cropped}.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\linewidth}
+		\centering
+		\includegraphicsw[.9]{{sph_e_10000.cropped}.png}
+	\end{subfigure}%	
+	\caption{Computed solution $p_h$ and corresponding error~$(p - p_h)$, $h = 2.97\times 10^{-1}$ (Top) and $h = 1.53\times 10^{-1}$ (Bottom)}
+	\label{fig:sph}		
+\end{figure}
+
+\begin{table}[H]
+	\centering\footnotesize
+	\caption{Convergence results for the spherical inclusion example. $\bar q$ denotes the mean value of a function~$q$} 
+	\label{tab:cube}
+	\begin{subtable}{1.\linewidth}
+		\centering
+		\begin{tabular}[1.2]{|c||c|c||c||c|}
+			\hline
+			$h$ & $\| p - p_h \|_{\lTwoSpace}$ & Order & $| \bar p - \bar p_h |$ & $\| p - p_h \|_{\infty}$ \\ 
+			\hline
+			\input{cube_table.tex}
+		\end{tabular}
+	\end{subtable}%
+\end{table}
+
+We see that for this example the reconstructed interface is actually discontinuous, and the convergence rate for pressure $\lTwoSpace$-error is worse than for piecewise linear case (where the interface is reconstructed exactly), cf.
+Tables~$\ref{tab:cyl}$ and \ref{tab:cube}.
+However, in both cases convergence rate is close to one.
+We see that $\ell^\infty(\Omega)$-error is sensitive to small isolated material volumes that appear to have ``wrong'' material ID after the interface reconstruction (similar to what we observe for 2D case, cf.~\cite[Section~4.3.1]{ZHILIAKOV2019333}); however, this does not affect the $\lTwoSpace$-error.
 
@@
 
-\AZ{Mikhail, please correct the details.}
-Funded by the Department of Energy at Los Alamos National Laboratory
-under contracts DE-AC52-06NA25396 and the DOE Office of Science
-Advanced Computing Research (ASCR) program in Applied Mathematical
-Sciences. Alexander Zhiliakov acknowledges the internship opportunity in the Los Alamos National Laboratory.
+This work was performed under the auspices of the National Nuclear Security Administration of the US Department of Energy at Los Alamos National Laboratory under Contract No.~89233218CNA000001.
+The authors gratefully acknowledge the support of the NNSA Advanced Simulation and Computing ASC) Program.
 
